### 2019-10-10 categorical-zero-one.tex
initial commit

\documentclass{article}
\usepackage{eigilscmds}
\usepackage{tikzit}
\input{/home/eigil/Downloads/tikzit/styles/foo.tikzstyles}
\usepackage{todonotes}
\author{Eigil Fjeldgren Rischel}
\title{A Kolmogorov zero to one law for Markov Categories}
\date{}
\renewcommand{\sf}{\mathsf}
\DeclareMathOperator{\del}{del}
\begin{document}
\maketitle
\section{Introduction}
This is a treatment of Kolmogorov's zero to one law in the setting of Markov categories.
Throughout, $J$ is a possibly infinite set and $F \subset J$ is a finite subset.

\section{Definitions and preliminaries}
Suppose $\cC$ is a Markov category.
To make sense of infinite families of random variables,
we will want to have a notion of infinite tensor product.
Of course, there is no reason such a thing should exist - for instance, it would be very strange for $\sf{FinStoch}$ to have infinite tensor products.
But in cases where the subcategory $\cC_{det}$ of deterministic maps has infinite products as well as finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
We introduce the following notion
\begin{definition}
    Let $\{X_i\}_{i \in J}$ be a collection of objects in $\cC$.
    Then we may form the diagram \[F \mapsto \bigotimes_{i \in F} X_i\]
    indexed over the poset of finite subsets $F \subset J$, ordered by reverse inclusion, where the structure maps are induced by $\del_{X_i}: X_i \to I$ and the coherence isomorphisms.

    We define $\bigotimes_{i \in J}X_i$ to be the limit of this (cofiltered) diagram in $\cC$, if it exists.
\end{definition}
\begin{remark}
    If $J$ is finite, this coincides with the normal tensor product indexed over $J$.
\end{remark}
\begin{remark}
    It is easily verified that 
    \[\bigotimes_{i \in J} X_i \tensor \bigotimes_{i' \in J'} X_{i'} \cong \bigotimes_{i \in J \sqcup J'} X_i\]
    i.e tensor products of infinite tensor products can be written as single infinite tensor products in the obvious way.

    Probably the similar theorem about infinite tensor products of infinite tensor products is true as well, although I have not verified it. 
\end{remark}
\begin{remark}
    Supposing $\bigotimes_{i\in J}X_i$ exists, the structure morphisms $\pi_j: \bigotimes_{i \in J} X_i \to X_j$ are deterministic and exhibit it as the product in $\cC_{det}$ of $\{X_i\}$.
\end{remark}
\begin{remark}
    If we take as input certain maps $I \to X_i$ as well, so that we have an infinite system of probability distributions, we can also try to define the infinite tensor product as a colimit, which will then be a space with a probability distribution, corresponding to an infinite system of random variables.
    It would also be possible to formulate the zero-to-one law in this setting, but I have not explored this.
\end{remark}

To actually use this idea to reproduce the usual Kolmogorov zero-one law, we need to do a bit of work:
\begin{example}
Let $\{(X_i,\Sigma_i)\}_{i\in J}$ be a set of measurable spaces in $\sf{Stoch}$.
Then consider their product $X = \prod_i X_i$ with the $\sigma$-algebra generated by the projections $\pi_i: X \to X_i$, which we denote $\Sigma$.
Let us write in general $X_F = \prod_{i\in F}X_F$, $\Sigma_F$ for the corresponding $\sigma$-algebra, and $\pi_F: X \to X_F$ for the projection.

Let $\{p_F: A \times \Sigma_F \to [0,1]\}_{F \subset J}$ be a collection of Markov kernels $A \to \prod_{i \in F}X_i$ for each $F$, compatible in the suitable sense.
Consider a point $a \in A$ and a generator $\pi_F\inv(B)$ for $\Sigma$, where $B \in \Sigma_F$.
Then we define $p(a,\pi_F\inv(B)) = p_F(a,B)$.
Note that the collection of such $\pi_F\inv(B)$ is a ring of sets on $X$ which generates $\Sigma$ - hence by Caratheodory extension, there is a unique probability measure
$p(a,-)$ on $X$ extending it. This is how we define $p(a,A)$ for general subsets $A \subset X$.

Now consider the class of subsets $A \in \Sigma$ such that $p(-,A):A \to X$ is measurable.
This class is a $\sigma$-algebra, which contains $\pi_F\inv(B)$, since $p(-,\pi_F\inv(B)) = p_F(-,B)$, which is measurable by assumption.
Since these generate $\Sigma$, the map is always measurable.
Hence $p$ is a Markov kernel.

This argument also shows that this Markov kernel is determined uniquely by the fact that $p(a,\pi_F\inv(B)) = p_F(a,B) = \pi_F \circ p$.
This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
\end{example}

We will refer to the structure maps $\bigotimes_{i\in J} X_i \to \bigotimes_{i\in F} X_i$ as \emph{finite marginalizations}.

This notion of infinite tensor product describes a notion of infinite collection of random variable where all dependence must be witnessed on some finite subset of the variables.

We can codify this in the following definition
\begin{definition}
    Let $p: A \to \bigotimes_{i\in J}X_i$ be a map in $\cC$.
    We say it exhibits the independence of $\{X_i\}$ given $A$ if each finite marginalization $A \to \bigotimes_{i \in F}X_i$ exhibits the independence of $\{X_i\}_{i \in F}$ given $A$.
\end{definition}

\section{Theorem}
\begin{theorem}
    Suppose we are given $p: A \to T \tensor \bigotimes_{i \in J} X_i$ satisfying the following conditions:
    \begin{enumerate}
        \item $T$ is a deterministic function of $\bigotimes_{i \in J} X_i$.
        \item For each finite subset $F \subset J$, the marginal $A \to T \tensor \bigotimes_{i \in F}X_i$ displays the independence of $T$ and $\bigotimes_{i \in F} X_i$.
    \end{enumerate}
    Then the marginal $A \to T$ is deterministic as well.
\end{theorem}

This theorem is a consequence of two lemmas.
\begin{lemma}[The infinite independence lemma]
    Suppose $p: A \to \bigotimes X_i$ exhibits the independence of $\{X_i\}$.
    Then for each $j$, the map $A \to X_j \tensor \bigotimes_{i \neq j}X_i$ exhibits the independence $X_j \bot \tensor_{i\neq j} X_i \mid \mid A$.
\end{lemma}
\begin{proof}[Sketch of proof]
    To prove this, we must compare two maps $A \to X_j \tensor \bigotimes_{i\neq j} X_i \cong \bigotimes_i X_i$.
    To show that these maps are equal, it suffices to show that all finite marginalizations of them are equal.
    But this is an immediate consequence of the assumption.
\end{proof}

\begin{lemma}[The determinism lemma]
    Suppose $p: A \to T \tensor X$ is such that $T$ is a deterministic function of $X$, and $p$ exhibits the independence $T \bot X \mid \mid A$.
    Then the marginal $A \to T$ is deterministic.
\end{lemma}
\begin{proof}
The proof is a string diagram chase:
First, the assumption that $T$ is a deterministic function of $X$ means precisely that we can find $f$ deterministic so that.

\tikzfig{determinismlemma1}.

Now we can use the independence of $X$ and $T$, and the axioms, to rewrite this as

\tikzfig{determinismlemma2}

Applying the map $1_T \tensor f$ to the second and fourth diagram now gives an equality

\tikzfig{determinismlemma3}

Where we have also applied the determinism of $f$.
This is precisely the statement that $A \to T \tensor X \to X \labelto{f} T$ is deterministic.

Lastly, we use the equality

\tikzfig{determinismlemma4}

To see that the marginal $A \to T \tensor X \to T$ is deterministic as desired.

\end{proof}

\begin{proof}[Proof of the theorem]
    It's clear from the definition that $A \to T \tensor \bigotimes X_i$ exhibits the independence of $\{T, X_1, \dots\}$.
    By the infinite independence lemma, this means that it also exhibits the independence $T \bot \bigotimes X_i \mid \mid A$.
    Now the determinism lemma implies exactly what we want, that the marginal $A \to T$ is deterministic.
\end{proof}

\begin{corollary}[Kolmogorov zero to one law]
    Suppose $\Omega$ is a measure space with a probability measure $P$, $\{f_i: \Omega \to X_i\}$ is a collection of independent random variables,
    and $T \subset \Omega$ is a subset in the $\sigma$-algebra generated by the $f_i$, such that $1_T$ is independent of any finite subset of the $f_i$.
    Then $P(T)$ is $0$ or $1$.
\end{corollary}
\begin{proof}
    Consider the composite $I \labelto{P} \Omega \labelto{1_T, \{f_i\}} \{0,1\} \tensor \bigotimes_i X_i$.
    Then independence of the $f_i$ means precisely that this map exhibits the independence of $\{X_i\}$ given $I$ in the above sense.
    Moreover, $T(\omega)$ is determined by the values of $f_i(\omega)$, so $T$ factors as a map $\prod_i X_i \to \{0,1\}$, and
    this map is measurable.
    Hence we can apply the theorem, and conclude that the map $I \labelto{P} \Omega \labelto{T} \{0,1\}$ is deterministic - but this means it's just a constant map,
    which precisely means that $T$ is true or false with probability $1$.
\end{proof}

\section{Speculation}
It would good to have a way of using this theorem without assuming that the category in question has these infinite tensor products.
We can always make sense of the notion of an infinite independent collection of random variables (just a collection of maps $I \to X_i$).
Of course to talk about an outcome or a function which depends on the outcome of all the $X_i$, we need a map $\prod_i X_i \to T$ of some type.
But since this map is deterministic, we may want to talk about it without admitting it to our category of Markov kernels.

As an example, the probability theory of finite or countable sets is much simpler than the probability theory of infinite sets, since the whole edifice of $\sigma$-algebras can be done away with.
This is a reason to prefer $\sf{FinStoch}$ over the full $\sf{Stoch}$.
In this case, it would be desirable to be able to apply this theorem, given a collection of finite variables $I \to X_i$ and a function $\prod_i X_i \to Y$
(which may be required to satisfy some condition like continuity in the product topology), without begin required to invent the larger category $\sf{Stoch}$.

For instance, maybe there is a Markov category with objects the profinite sets, which can be obtained from $\sf{FinStoch}$ by some formal construction (maybe even simply as the pro-category), which admits infinite tensor products, and where one can profitably interpret this theorem.
\end{document}

### 2019-10-11 categorical-zero-one.tex
added sketch of hewitt-savage argument

@@
 
+We can also prove a version of the Hewitt-Savage theorem
+\begin{definition}
+    Let $\alpha: J \to J$ be any map.
+    Then it induces a map 
+    \[]\hat{\alpha}: \bigotimes_{i\in J}X_i \to \bigotimes_{i \in J}X_{\alpha(i)},\]
+    which we may suggestively write as $(x_i)_{i\in J} \mapsto (x_{\alpha(i)})_{i\in J}$.
+
+    It is clear that this map is always deterministic. Moreover, if $\alpha$ is a bijection, this map is an isomorphism.
+\end{definition}
+
+\begin{theorem}[Hewitt-Savage for Markov categories]
+    Let $\cC$ be a causal Markov category with infinite tensor products. Let $A \to \cC$ be a map in $\cC$, $J$ an infinite set, and let $f: \bigotimes_{i \in J}X \to T$ be a deterministic map.
+    Suppose for each finite permutation $\sigma: J \to J$, we have $f \circ \hat{\sigma} = f$ - in other words, $f$ is independent of finite permutations of the inputs.
+    Then the composite $A \to \tensor_J A \to \tensor_J X \to T$ is deterministic.
+\end{theorem}
+Again, we factor part of the proof into a lemma.
+\begin{lemma}
+    Let $\cC$ be a causal markov category, and let $f,g: B \to X$ be maps, $f$ deterministic.
+    Let $p: A \to B$ be any map.
+    Suppose the composites 
+    \[A \to B \to B \tensor B \labelto{f \tensor g} X \tensor X\]
+    and
+    \[A \to B \to B \tensor B \labelto{f \tensor f} X \tensor X\]
+    agree. Then $f = g$ $p$-almost everywhere.
+\end{lemma}
+\begin{proof}[Sketch of sketch of proof]
+    Consider the map
+    $A \labelto{p} B \to B \tensor B \labelto{f \tensor g} X \tensor X \labelto{copy_{X \tensor X}} X \tensor X \tensor X \tensor X$.
+    Whether we marginalize on the first or second factor of $X$, we get equal morphisms, because we may replace the first part of this with
+    $A \to B \labelto{f} B \to X \tensor X \tensor X \tensor X$ by using the assumptions and determinism.
+
+    Then applying causality, with $f = p$, $g= (f \tensor g) \circ copy_B$, $h_1 = (del_X \tensor 1_X)$, $h_2  = (1_X \tensor del_X)$.
+    Marginalizing the resulting (equal) diagrams, one of them is 
+    \[A \to B \to B \tensor B \labelto{f, 1_B} B \tensor B,\]
+    one of them is 
+    \[A \to B \to B \tensor B \labelto{g,1_B} B \tensor B,\]
+    and this is precisely what must hold for them to agree $p$-a.e.
+\end{proof}
+
+\begin{proof}[Proof of theorem]
+    Consider the map
+
+    \[e: A \to \tensor_J A \labelto{\tensor p} (\tensor_J X) \to (\tensor_J X) \tensor (\tensor_J X) \to T \tensor (\tensor_J X)\]
+
+    Denote by $e_\sigma$ the composite of $e$ with $1_T \tensor \hat{\sigma}$
+    Note that if $\sigma$ is a finite permutation, $e_\sigma = e$. To see this, note that we may add a $\hat{\sigma}$ before the $f$ as well, by assumption.
+    Now we can use the determinism of the $\hat{\sigma}$s, and the clear fact that 
+    \[A \to \tensor A \to \tensor B \labelto{\hat{\sigma}} \tensor B = A \to \tensor A \to \tensor B\]
+
+    Now let $\sigma$ instead be an injection. Then for each finite subset $F \subset J$, we can find a finite permutation of $J$, $\sigma_0$, such that $\sigma|_F = \sigma_0|_F$.
+    Then on this marginal, $e_\sigma = e_{\sigma_0} = e$, hence $e_\sigma = e$ in general.
+
+    Let $J = J_0 \sqcup J_1$ be a decomposition of $J$ into two disjoint subsets with the cardinality of $J$ (here we use $J$ infinite).
+    Let $\tau_0, \tau_1: J \to J$ be injections with image $J_0,J_1$ respectively.
+
+    Now consider the map $a_\sigma: A \to T \tensor T$ given by composing $e_\sigma$ with $t$.
+    By the above, they all agree.
+    By the lemma, we see that the maps $\tensor_J X \labelto{\hat{\sigma}} \tensor_J X \to T$ are all $\tensor_J p$ a.e. equal.
+    Applying this to $\tau_0,\tau_1$, we get that the map $A \to T$ must be deterministic.
+\end{proof}
+In the last step, the idea is that precomposing with $\hat{\tau_0}$ and $\hat{\tau_1}$ is essentially picking out two disjoint subsets and using them to determine $T$.
+Since all the variables are independent, these two are clearly independent, but also equal (by the preceding argument). Hence they are deterministic, but they also agree with the original map.
+
 \section{Speculation}

### 2019-10-12 categorical-zero-one.tex
started adding more text

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 \usepackage{eigilscmds}
 \usepackage{tikzit}
-\input{/home/eigil/Downloads/tikzit/styles/foo.tikzstyles}
+\usepackage{geometry}
+\input{foo.tikzstyles}
+
+% draft packages
 \usepackage{todonotes}
-\author{Eigil Fjeldgren Rischel}
-\title{A Kolmogorov zero to one law for Markov Categories}
-\date{}
+\usepackage{showkeys}
+
+\author{Tobias Fritz and Eigil Fjeldgren Rischel}
+\title{The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability}
+\date{\today}
+
 \renewcommand{\sf}{\mathsf}
@@
 \maketitle
+
+\begin{abstract}
+	We state and prove the zero--one laws of Kolmogorov and Hewitt--Savage within the setting of \emph{Markov categories}, a category-theoretic approach to the foundations of probability and statistics.
+This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones, but also in other contexts such as categories of closed relations between topological spaces,
+	\improve{T: this abstract states what we can hopefully achieve. To be adjusted}
+\end{abstract}
+
+\tableofcontents
+
 \section{Introduction}
-This is a treatment of Kolmogorov's zero to one law in the setting of Markov categories.
-Throughout, $J$ is a possibly infinite set and $F \subset J$ is a finite subset.
 
-\section{Definitions and preliminaries}
+This is a treatment of the zero--one laws of Kolmogorov and of Hewitt--Savage in the setting of Markov categories.
+
+\paragraph*{Notation.}
+
+Throughout, $\cC$ is a Markov category in the sense of \cite[Definition~2.1]{markov_cats} (see also the closely related earlier work of Golubtsov~\cite{golubtsov} and Cho and Jacobs~\cite{cho_jacobs}).
+$J$ is a possibly infinite set, used for indexing products of objects, and $F \subset J$ ranges over finite subsets.
+
+\section{Background on Markov categories}
+
+\todo[inline]{to be written}
+
+\section{Infinite tensor products}
+
 Suppose $\cC$ is a Markov category.
-To make sense of infinite families of random variables,
-we will want to have a notion of infinite tensor product.
-Of course, there is no reason such a thing should exist - for instance, it would be very strange for $\sf{FinStoch}$ to have infinite tensor products.
-But in cases where the subcategory $\cC_{det}$ of deterministic maps has infinite products as well as finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
+To make sense of infinite families of random variables within $\cC$,
+we will want to have a notion of infinite tensor product in $\cC$.
+By Kolmogorov's extension theorem, the joint distribution of infinitely many random variables is uniquely determined by the family of distributions of all finite subsets of these variables.
+This motivates a general definition of the infinite tensor product of a family of objects $(X_i)_{i \in J}$, based on the observation that if $F \subseteq F' \subseteq J$ are two finite subset, then the fact that $\cC$ is semicartesian monoidal gives us morphisms
+\[
+	\bigotimes_{i \in F'} X_i \longrightarrow \bigotimes_{i \in F} X_i
+\]
+to be interpreted as \emph{marginalization}.
+Via these maps, the finite tensor products $\bigotimes_{i \in F} X_i$ make up a cofiltered diagram in the form of a functor from the poset of finite subsets of $J$, ordered by reverse inclusion, to $\cC$.
+
+\begin{definition}
+    Let $(X_i)_{i \in J}$ be a family of objects in $\cC$.
+    Then the \emph{infinite tensor product} $\bigotimes_{i \in J} X_i$ is the limit of the diagram \[F \longmapsto \bigotimes_{i \in F} X_i,\]
+    indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists.
+\end{definition}
+
+Similar definitions of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products are well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
+Intuitively, our definition matches up with these under the categorical duality of algebra and geometry, where our definition is of a geometrical flavour.
+
+Of course, in a general Markov category the above limit need not exist, in which case the infinite tensor product does not exist either (\Cref{infprods_finstoch}).
+But in cases where the subcategory $\cC_{\det}$ of deterministic maps has infinite products as well as finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
 We introduce the following notion
-\begin{definition}
-    Let $\{X_i\}_{i \in J}$ be a collection of objects in $\cC$.
-    Then we may form the diagram \[F \mapsto \bigotimes_{i \in F} X_i\]
-    indexed over the poset of finite subsets $F \subset J$, ordered by reverse inclusion, where the structure maps are induced by $\del_{X_i}: X_i \to I$ and the coherence isomorphisms.
 
-    We define $\bigotimes_{i \in J}X_i$ to be the limit of this (cofiltered) diagram in $\cC$, if it exists.
-\end{definition}
 \begin{remark}
-    If $J$ is finite, this coincides with the normal tensor product indexed over $J$.
+	If $J$ is finite, the infinite tensor product coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
 \end{remark}
+
 \begin{remark}
@@
 \end{remark}
+
 \begin{remark}
-    Supposing $\bigotimes_{i\in J}X_i$ exists, the structure morphisms $\pi_j: \bigotimes_{i \in J} X_i \to X_j$ are deterministic and exhibit it as the product in $\cC_{det}$ of $\{X_i\}$.
+    Supposing $\bigotimes_{i\in J}X_i$ exists, the structure morphisms $\pi_j: \bigotimes_{i \in J} X_i \to X_j$ are deterministic and exhibit it as the product in $\cC_{\det}$ of $\{X_i\}$.
 \end{remark}
+
 \begin{remark}
@@
 To actually use this idea to reproduce the usual Kolmogorov zero-one law, we need to do a bit of work:
+
 \begin{example}
@@
 This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
+\end{example}
+
+\begin{example}
+	\label{infprods_finstoch}
+	$\sf{FinStoch}$ does not have infinite tensor products.
 \end{example}
@@
 For instance, maybe there is a Markov category with objects the profinite sets, which can be obtained from $\sf{FinStoch}$ by some formal construction (maybe even simply as the pro-category), which admits infinite tensor products, and where one can profitably interpret this theorem.
+
+\bibliographystyle{plain}
+\bibliography{categorical-zero-one}
+
 \end{document}

### 2019-10-14 categorical-zero-one.tex
some stuff on infinite tensor products

@@
 \usepackage{geometry}
-\input{foo.tikzstyles}
+\input{comonoids.tikzdefs}
+\input{comonoids.tikzstyles}
 
@@
 
-\section{Infinite tensor products}
+\section{Infinite tensor products in semicartesian monoidal categories}
 
-Suppose $\cC$ is a Markov category.
+Suppose $\cC$ is a semicartesian monoidal category.
 To make sense of infinite families of random variables within $\cC$,
@@
 
-Similar definitions of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products are well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
-Intuitively, our definition matches up with these under the categorical duality of algebra and geometry, where our definition is of a geometrical flavour.
+We will refer to the structure maps $\pi_F : \bigotimes_{i\in J} X_i \to \bigotimes_{i\in F} X_i$ as \emph{finite marginalizations}, and also write $\pi_j$ as shorthand for $\pi_{\{j\}}$.
 
-Of course, in a general Markov category the above limit need not exist, in which case the infinite tensor product does not exist either (\Cref{infprods_finstoch}).
-But in cases where the subcategory $\cC_{\det}$ of deterministic maps has infinite products as well as finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
-We introduce the following notion
+The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
+Intuitively, our definition matches up with these under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
 
 \begin{remark}
-	If $J$ is finite, the infinite tensor product coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
+	If $J$ is finite, the infinite tensor product exists and coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
 \end{remark}
 
+Of course, in a general Markov category the above cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
+
 \begin{remark}
+	\label{double_infinite_product}
     It is easily verified that 
@@
     i.e tensor products of infinite tensor products can be written as single infinite tensor products in the obvious way.
-
-    Probably the similar theorem about infinite tensor products of infinite tensor products is true as well, although I have not verified it. 
 \end{remark}
 
+\todo[inline]{Probably the similar theorem about infinite tensor products of infinite tensor products is true as well, although I have not verified it.}
+
+\section{Infinite tensor products in Markov categories}
+
+If a Markov category $\cC$ has infinite tensor products, then one should expect a suitable compatibility condition between these infinite tensor products and the comonoid structures on the objects to be satisfied.
+In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
+
+\begin{definition}
+	\label{defn_kolmogorov_ext}
+	A Markov category \emph{satisfies Kolmogorov extension} if it has infinite tensor products $\bigotimes_{i \in J} X_i$ such that 
+	\[
+		\tikzfig{infinite_product_copy}
+	\]
+\end{definition}
+
+\todo[inline]{Is this good terminology?}
+
+The idea is that this equation uniquely determines the comonoid structure: by \Cref{double_infinite_product}, the comultiplication
+\[
+	\mathsf{copy}_{\bigotimes_i X_i} \: : \: \bigotimes_i X_i \longrightarrow \left( \bigotimes_i X_i \right) \otimes \left( \bigotimes_i X_i \right)
+\]
+is uniquely determined by its composition with the maps $\pi_i \otimes \pi_j$ for all $i,j \in J$.
+
+\todo[inline]{Can we show that the comonoid laws automatically follow from \Cref{defn_kolmogorov_ext}?}
+
+In particular, the $i=j$ case of the equation above shows that the marginalizations $\pi_i$ are deterministic.
+
 \begin{remark}
-    Supposing $\bigotimes_{i\in J}X_i$ exists, the structure morphisms $\pi_j: \bigotimes_{i \in J} X_i \to X_j$ are deterministic and exhibit it as the product in $\cC_{\det}$ of $\{X_i\}$.
+	Isomorphic objects in a Markov category can have non-isomorphic comonoid structures~\cite[Remark~10.9]{markov_cats}.
+Therefore the condition of \Cref{defn_kolmogorov_ext} generally depends on the particular \emph{choice} of the infinite tensor product, rather than only on the mere existence of infinite tensor products in the underlying semicartesian monoidal category.
 \end{remark}
+
+But in case that the subcategory of deterministic maps $\cC_{\det}$ has infinite products in addition to finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
+
+\begin{lemma}
+	If $\cC$ satisfies Kolmogorov extension, then an infinite tensor product $\bigotimes_i X_i$ is a product $\prod_i X_i$ with projections $\pi_i$ in the subcategory of deterministic morphisms $\cC_\detc \subseteq \cC$.
+\end{lemma}
+
+\begin{proof}
+	\todo[inline]{We probably have to show that all finite marginalization maps $\pi_F$ are deterministic}
+\end{proof}
 
@@
 \end{example}
-
-We will refer to the structure maps $\bigotimes_{i\in J} X_i \to \bigotimes_{i\in F} X_i$ as \emph{finite marginalizations}.
 
@@
 
-\tikzfig{determinismlemma1}.
+%\tikzfig{determinismlemma1}.
 
@@
 
-\tikzfig{determinismlemma2}
+%\tikzfig{determinismlemma2}
 
@@
 
-\tikzfig{determinismlemma3}
+%\tikzfig{determinismlemma3}
 
@@
 
-\tikzfig{determinismlemma4}
+%\tikzfig{determinismlemma4}
 

### 2019-10-18 categorical-zero-one.tex
Add examples for Kl(H)

@@
     If we take as input certain maps $I \to X_i$ as well, so that we have an infinite system of probability distributions, we can also try to define the infinite tensor product as a colimit, which will then be a space with a probability distribution, corresponding to an infinite system of random variables.
-    It would also be possible to formulate the zero-to-one law in this setting, but I have not explored this.
+    It would also be possible to formulate the zero-to-one law in this setting, but we have not explored this.
 \end{remark}
@@
 \begin{theorem}
+    \label{thm:kolmog}
     Suppose we are given $p: A \to T \tensor \bigotimes_{i \in J} X_i$ satisfying the following conditions:
@@
     Then it induces a map 
-    \[]\hat{\alpha}: \bigotimes_{i\in J}X_i \to \bigotimes_{i \in J}X_{\alpha(i)},\]
+    \[\hat{\alpha}: \bigotimes_{i\in J}X_i \to \bigotimes_{i \in J}X_{\alpha(i)},\]
     which we may suggestively write as $(x_i)_{i\in J} \mapsto (x_{\alpha(i)})_{i\in J}$.
@@
 \begin{theorem}[Hewitt-Savage for Markov categories]
+    \label{thm:hewsav}
     Let $\cC$ be a causal Markov category with infinite tensor products. Let $A \to \cC$ be a map in $\cC$, $J$ an infinite set, and let $f: \bigotimes_{i \in J}X \to T$ be a deterministic map.
@@
 
+\section{Examples}
+As noted, theorems \cref{thm:kolmog} and \cref{thm:hewsav}, when intepreted in the Markov category $\mathsf{Stoch}$, recover the classical Kolmogorov and Hewitt-Savage zero to one laws.
+\improve{Maybe move those examples to here? Also figure out where to put proof that $Kl(H)$ has infinite tensor product and Kolmogorov extension. (And introduce $H$)}
+
+By intepreting them in other Markov categories, we obtain other nontrivial (although hardly particularly deep) statements:
+
+\begin{corollary}
+    Let $\{X_i\}_{i \in J}$ be a family of topological spaces, $Y$ a Hausdorff space, and let $f: \prod_i X_i \to Y$ be a continuous function
+    which is independent of any finite prefix of the input.
+    Then the map $f$ is constant.
+\end{corollary}
+\begin{corollary}
+    Let $X, Y$ be topological spaces, $Y$ Hausdorff, and let $f: \prod_{i\in J} X \to Y$ be a continuous function which is independent of any finite permutation of the input.
+    Then $f$ is constant.
+\end{corollary}
+\begin{proof}
+    The theorems follow from \cref{thm:kolmog} and \cref{thm:hevsav}, applied to the Kleisli category $Kl(H)$ of the hyperspace monad,
+    using the maps $* \to X_i$ and $* \to X$ given by the closed subsets $X_i \subseteq X_i, X \subset X$.
+    The conclusion is that the closure of the image, call it $A$, has the following property: $\overline{\{(a,a) \mid a \in A\}} = A \times A$ as subsets of $Y \times Y$.
+    But since the diagonal is closed in $Y$, this clearly implies that $A$ must be a singleton.
+\end{proof}
+
 \section{Speculation}
+\todo[inline]{not sure if this section is any good}
 It would good to have a way of using this theorem without assuming that the category in question has these infinite tensor products.

### 2019-10-18 categorical-zero-one.tex
Rewrite sections on infinite tensor products

@@
 \usepackage{geometry}
+\usepackage{enumerate}
 \input{comonoids.tikzdefs}
@@
 Of course, in a general Markov category the above cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
-
-\begin{remark}
-	\label{double_infinite_product}
-    It is easily verified that 
-    \[\bigotimes_{i \in J} X_i \tensor \bigotimes_{i' \in J'} X_{i'} \cong \bigotimes_{i \in J \sqcup J'} X_i\]
-    i.e tensor products of infinite tensor products can be written as single infinite tensor products in the obvious way.
-\end{remark}
-
-\todo[inline]{Probably the similar theorem about infinite tensor products of infinite tensor products is true as well, although I have not verified it.}
-
 \section{Infinite tensor products in Markov categories}
@@
     \label{defn_kolmogorov_ext}
-	A Markov category \emph{satisfies Kolmogorov extension} if it has infinite tensor products $\bigotimes_{i \in J} X_i$ such that 
-	\[
-		\tikzfig{infinite_product_copy}
-	\]
+    Let $\cC$ be a Markov category, let $\{X_i\}_{i\in J}$ be an infinite family of objects, and let $\bigotimes_i X_i$ be an infinite tensor product.
+    We say this product \emph{satisfies Kolmogorov extension} if the following two conditions hold:
+    \begin{enumerate}[(1)]
+        \item The finite marginals \[\pi_F: \bigotimes_{i\in J} X_i \to \bigotimes_{i \in F} X_i\] are deterministic
+        \item These maps exhibit $\bigotimes_{i\in J} X_i$ as the cofiltered limit of the diagram $F \mapsto \bigotimes_{i \in F} X_i$ \emph{in $\cC_{\rm det}$}.
+    \end{enumerate}
 \end{definition}
@@
 
-The idea is that this equation uniquely determines the comonoid structure: by \Cref{double_infinite_product}, the comultiplication
-\[
-	\mathsf{copy}_{\bigotimes_i X_i} \: : \: \bigotimes_i X_i \longrightarrow \left( \bigotimes_i X_i \right) \otimes \left( \bigotimes_i X_i \right)
-\]
-is uniquely determined by its composition with the maps $\pi_i \otimes \pi_j$ for all $i,j \in J$.
+\begin{remark}
+    Since the (finite) tensor product is the product in $\cC_{\rm det}$, condition (2) is equivalent to the statement that the marginals
+    \[\pi_j: \bigotimes_i X_i \to X_j\]
+    exhibit $\bigotimes_i X_i$ as the product of the $X_j$ in $\cC_{\rm det}$,
+    since in any category, \[\lim_{F \subset J} \prod_{i \in F}X_i \cong \prod_{i \in J}X_i\]
+\end{remark}
 
-\todo[inline]{Can we show that the comonoid laws automatically follow from \Cref{defn_kolmogorov_ext}?}
+\begin{remark}
+    Condition (2) is also equivalent to the statement that, given a compatible family of deterministic maps $a_F: A \to \bigotimes_{i \in F}$, the induced map $a: A \to \bigotimes_i X_i$ is deterministic.
+\end{remark}
 
-In particular, the $i=j$ case of the equation above shows that the marginalizations $\pi_i$ are deterministic.
+This determines the comonoid structure uniquely: $\mathsf{copy}_{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$,
+and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
 
@@
 
-But in case that the subcategory of deterministic maps $\cC_{\det}$ has infinite products in addition to finite ones, it seems natural to ask whether this is compatible with the structure of $\cC$ in a suitable sense.
-
 \begin{lemma}
-	If $\cC$ satisfies Kolmogorov extension, then an infinite tensor product $\bigotimes_i X_i$ is a product $\prod_i X_i$ with projections $\pi_i$ in the subcategory of deterministic morphisms $\cC_\detc \subseteq \cC$.
+    Let $J,J'$ be possibly infinite sets, and $\{X_i\}_{i\in J}, \{Y_i\}_{i\in J'}$ two families of objects in $\cC$, so that both have infinite tensor products with Kolmogorov extension.
+    Let $\{Z_i\}_{i\in J \sqcup J'}$ be a family of objects indexed by the disjoint union, where $Z_i = X_i$ for $i\in J$, $Z_i = Y_i$ for $i \in J'$,
+    and suppose $\{Z_i\}$ admits an infinite tensor product with Kolmogorov extension, too.
+    Consider the family of maps
+    \[\rho_F: \bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \labelto{\pi_{F \cap J} \tensor \pi_{F \cap J'}} \bigotimes_{i \in F \cap J}X_i \tensor \bigotimes_{i\in F \cap J'}Y_i\]
+    indexed by finite subsets $F \subset J \sqcup J'$ of the disjoint union.
+    The induced map
+    \[\bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \to \bigotimes_{i \in J \sqcup J'} Z_i\]
+    is a deterministic isomorphism.
 \end{lemma}
-
 \begin{proof}
-	\todo[inline]{We probably have to show that all finite marginalization maps $\pi_F$ are deterministic}
+    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
+    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
 \end{proof}
-
-\begin{remark}
-    If we take as input certain maps $I \to X_i$ as well, so that we have an infinite system of probability distributions, we can also try to define the infinite tensor product as a colimit, which will then be a space with a probability distribution, corresponding to an infinite system of random variables.
-    It would also be possible to formulate the zero-to-one law in this setting, but we have not explored this.
-\end{remark}
 
@@
 This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
+It is simple to verify that it also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
 \end{example}
@@
 \end{example}
+\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
+
+From this point, the term \emph{infinite tensor product} will refer always to an infinite tensor product with Kolmogorov extension.
 
@@
 \begin{proof}
-    The theorems follow from \cref{thm:kolmog} and \cref{thm:hevsav}, applied to the Kleisli category $Kl(H)$ of the hyperspace monad,
+    The theorems follow from \cref{thm:kolmog} and \cref{thm:hewsav}, applied to the Kleisli category $Kl(H)$ of the hyperspace monad,
     using the maps $* \to X_i$ and $* \to X$ given by the closed subsets $X_i \subseteq X_i, X \subset X$.

### 2019-10-23 categorical-zero-one.tex
some more introductory stuff

@@
 
-Throughout, $\cC$ is a Markov category in the sense of \cite[Definition~2.1]{markov_cats} (see also the closely related earlier work of Golubtsov~\cite{golubtsov} and Cho and Jacobs~\cite{cho_jacobs}).
-$J$ is a possibly infinite set, used for indexing products of objects, and $F \subset J$ ranges over finite subsets.
+For monoidal categories, we make frequent use of string diagram notation. We omit object labels whenever these are obvious from the context.
+
+In \Cref{infprod_semicartesian}, $\cC$ denotes a semicartesian monoidal category.
+In \Cref{infprod_markov} and after, $\cC$ denotes a Markov category in the sense of \Cref{markov_cat}.
+$J$ is a set used for indexing products of objects; the definitions and results of this paper are nontrivial only when $J$ is infinite.
+$F$ denotes either an arbitrary finite set or more concretely a finite subset of $J$.
 
 \section{Background on Markov categories}
+
+A monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal. Equivalently, it is a monoidal category equipped with morphisms
+\[
+	X \otimes Y \longrightarrow X, \qquad X \otimes Y \longrightarrow Y,
+\]
+which are natural in $X$ and $Y$ and coincide with the monoidal structure isomorphisms whenever $X = I$ or $Y = I$. Here are the main examples that we will be considering.
+
+\begin{example}
+	$\FinStoch$ is the category of finite sets with \emph{stochastic maps}, where a stochastic map $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
+Stochastic maps compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
+We consider $\FinStoch$ as a monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic maps on morphisms.
+\end{example}
+
+\begin{example}
+	Let $\CRing_+$ be the category of commutative rings with maps which are merely additive and unit-preserving, considered as a monoidal category in the obvious way with respect to the tensor product of rings.
+Then since $\CRing_+$ has the monoidal unit $\Z$ as its initial object, we can conclude that $\CRing_+\op$ is semicartesian monoidal.
+\end{example}
+
+\begin{example}
+	$\Stoch$ is the category of measurable spaces $(X,\Sigma_X)$ as objects and Markov kernels as morphisms.
+We sketch the definition here and refer to~\cite[Section~4]{markov_cats} and references therein for the details.
+A \emph{Markov kernel} $(X,\Sigma_X) \to (Y,\Sigma_Y)$ is a function
+	\[
+		f \: : \: \Sigma_Y \times X \longrightarrow [0,1], \quad (S,x) \longmapsto f(S|x)
+	\]
+	assigning to every $x \in X$ a probability measure $f(-|x) : \Sigma_Y \to [0,1]$ in such a way that for every $S \in \Sigma_Y$, the function $x \mapsto f(S|x)$ is measurable.
+Intuitively, $f$ assigns to every $x \in X$ a random element of $Y$.
+Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the monoidal structure is defined in terms of the usual product of measurable spaces.
+\end{example}
+
+In the graphical calculus, the unique morphism $X \to I$ for an object $X \in \cC$ is denoted by
+\[
+	\tikzfig{terminal}
+\]
+The projection maps $X \otimes Y \to X$ and $X \otimes Y \to Y$ are correspondingly written as
+\[
+	\tikzfig{marginals}
+\]
+
+Our goal is to use semicartesian monoidal categories such as the above in order to develop aspects of probability theory in categorical terms.
+As it turns out, doing so requires a bit more structure, in a form which has been axiomatized in the notion of \emph{Markov category} \cite[Definition~2.1]{markov_cats}.
+
+\begin{definition}
+	A Markov category $\cC$ is a semicartesian monoidal category \ldots
+	\label{markov_cat}
+\end{definition}
+
+A closely related definition was also used in earlier work of Golubtsov~\cite{golubtsov}, who had proposed a closely related definition, and Cho and Jacobs~\cite{cho_jacobs}, where an equivalent definition was used under the term \emph{affine CD-category}.
 
@@
 \section{Infinite tensor products in semicartesian monoidal categories}
+\label{infprod_semicartesian}
 
-Suppose $\cC$ is a semicartesian monoidal category.
-To make sense of infinite families of random variables within $\cC$,
+\todo[inline]{Let's also simplify notation by writing $X_J$ and $X_F$ instead of writing $\bigotimes$ every time. This is quite standard}
+
+Suppose $\cC$ is a semicartesian monoidal category. In our
+
+In order to make sense of infinite families of random variables within $\cC$,
 we will want to have a notion of infinite tensor product in $\cC$.
@@
 Of course, in a general Markov category the above cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
-\section{Infinite tensor products in Markov categories}
-
-If a Markov category $\cC$ has infinite tensor products, then one should expect a suitable compatibility condition between these infinite tensor products and the comonoid structures on the objects to be satisfied.
-In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
-
-\begin{definition}
-    \label{defn_kolmogorov_ext}
-    Let $\cC$ be a Markov category, let $\{X_i\}_{i\in J}$ be an infinite family of objects, and let $\bigotimes_i X_i$ be an infinite tensor product.
-    We say this product \emph{satisfies Kolmogorov extension} if the following two conditions hold:
-    \begin{enumerate}[(1)]
-        \item The finite marginals \[\pi_F: \bigotimes_{i\in J} X_i \to \bigotimes_{i \in F} X_i\] are deterministic
-        \item These maps exhibit $\bigotimes_{i\in J} X_i$ as the cofiltered limit of the diagram $F \mapsto \bigotimes_{i \in F} X_i$ \emph{in $\cC_{\rm det}$}.
-    \end{enumerate}
-\end{definition}
-
-\todo[inline]{Is this good terminology?}
-
-\begin{remark}
-    Since the (finite) tensor product is the product in $\cC_{\rm det}$, condition (2) is equivalent to the statement that the marginals
-    \[\pi_j: \bigotimes_i X_i \to X_j\]
-    exhibit $\bigotimes_i X_i$ as the product of the $X_j$ in $\cC_{\rm det}$,
-    since in any category, \[\lim_{F \subset J} \prod_{i \in F}X_i \cong \prod_{i \in J}X_i\]
-\end{remark}
-
-\begin{remark}
-    Condition (2) is also equivalent to the statement that, given a compatible family of deterministic maps $a_F: A \to \bigotimes_{i \in F}$, the induced map $a: A \to \bigotimes_i X_i$ is deterministic.
-\end{remark}
-
-This determines the comonoid structure uniquely: $\mathsf{copy}_{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$,
-and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
-
-\begin{remark}
-    Isomorphic objects in a Markov category can have non-isomorphic comonoid structures~\cite[Remark~10.9]{markov_cats}.
-    Therefore the condition of \Cref{defn_kolmogorov_ext} generally depends on the particular \emph{choice} of the infinite tensor product, rather than only on the mere existence of infinite tensor products in the underlying semicartesian monoidal category.
-\end{remark}
 
@@
 \end{proof}
+
+\section{Infinite tensor products in Markov categories}
+\label{infprod_markov}
+
+If a Markov category $\cC$ has infinite tensor products, then one should expect a suitable compatibility condition between these infinite tensor products and the comonoid structures on the objects to be satisfied.
+In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
+
+\begin{definition}
+    \label{defn_kolmogorov_ext}
+    Let $\cC$ be a Markov category, let $\{X_i\}_{i\in J}$ be an infinite family of objects, and let $\bigotimes_i X_i$ be an infinite tensor product.
+    We say this product \emph{satisfies Kolmogorov extension} if the following two conditions hold:
+    \begin{enumerate}[(1)]
+        \item The finite marginals \[\pi_F: \bigotimes_{i\in J} X_i \to \bigotimes_{i \in F} X_i\] are deterministic
+        \item These maps exhibit $\bigotimes_{i\in J} X_i$ as the cofiltered limit of the diagram $F \mapsto \bigotimes_{i \in F} X_i$ \emph{in $\cC_{\rm det}$}.
+    \end{enumerate}
+\end{definition}
+
+\todo[inline]{Perhaps we could change the terminology to ``Kolmogorov product''. I'll tentatively use this in the following}
+
+\begin{remark}
+    Since the (finite) tensor product is the product in $\cC_{\rm det}$, condition (2) is equivalent to the statement that the marginals
+    \[\pi_j: \bigotimes_i X_i \to X_j\]
+    exhibit $\bigotimes_i X_i$ as the product of the $X_j$ in $\cC_{\rm det}$,
+    since in any category, \[\lim_{F \subset J} \prod_{i \in F}X_i \cong \prod_{i \in J}X_i\]
+\end{remark}
+
+\begin{remark}
+    Condition (2) is also equivalent to the statement that, given a compatible family of deterministic maps $a_F: A \to \bigotimes_{i \in F} X_i$, the induced map $a: A \to \bigotimes_i X_i$ is deterministic.
+\end{remark}
+
+This determines the comonoid structure uniquely: $\mathsf{copy}_{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$,
+and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
+
+\begin{remark}
+    Isomorphic objects in a Markov category can have non-isomorphic comonoid structures~\cite[Remark~10.9]{markov_cats}.
+    Therefore the condition of \Cref{defn_kolmogorov_ext} generally depends on the particular \emph{choice} of the infinite tensor product, rather than only on the mere existence of infinite tensor products in the underlying semicartesian monoidal category.
+\end{remark}
 

### 2019-10-24 categorical-zero-one.tex
added something on kleisli categories and infinite tensor prods

--- 2019-10-18 categorical-zero-one.tex
@@
 
+\begin{example}
+    Suppose $\cC$ is a Cartesian monoidal category. Then it has a unique Markov category structure given by the diagonal maps,
+    where every map is deterministic.
+    An infinite collection of objects $\{X_i\}$ has an infinite tensor product with Kolmogorov extension if and only if it has a categorical product in $\cC$.
+\end{example}
+
+\begin{proposition}
+    \todo[inline]{write proof once we've figured out the order of things. But this is one for the "wishlist"}
+    Let $\cC$ be a Markov category, and let $T$ be an affine symmetric monoidal monad on $\cC$, so that the Kleisli category $Kl(T)$ is a Markov category.
+    Let $\{X_i\}_{i\in J}$ be a possibly infinite family of objects in $\cC$, and suppose it has an infinite tensor product in $\cC$ with Kolmogorov extension, $\bigotimes X_i$.
+    Then the limit
+    \[\lim_{F \subset J} \prod_{i\in F}X_i\]
+    exists in $\cC$ (by assumption, it is $\bigotimes X_i$).
+    Suppose further that $T$ preserves this limit.
+    Then $\bigotimes X_i$ is also an infinite tensor product of $\{X_i\}$ in $Kl(T)$.
+\end{proposition}
 \begin{lemma}

### 2019-10-24 categorical-zero-one.tex

--- 2019-10-23 categorical-zero-one.tex
@@
 \end{remark}
+
+\begin{example}
+    Suppose $\cC$ is a Cartesian monoidal category. Then it has a unique Markov category structure given by the diagonal maps,
+    where every map is deterministic.
+    An infinite collection of objects $\{X_i\}$ has an infinite tensor product with Kolmogorov extension if and only if it has a categorical product in $\cC$.
+\end{example}
+
+\begin{proposition}
+    \todo[inline]{write proof once we've figured out the order of things. But this is one for the "wishlist"}
+    Let $\cC$ be a Markov category, and let $T$ be an affine symmetric monoidal monad on $\cC$, so that the Kleisli category $Kl(T)$ is a Markov category.
+    Let $\{X_i\}_{i\in J}$ be a possibly infinite family of objects in $\cC$, and suppose it has an infinite tensor product in $\cC$ with Kolmogorov extension, $\bigotimes X_i$.
+    Then the limit
+    \[\lim_{F \subset J} \prod_{i\in F}X_i\]
+    exists in $\cC$ (by assumption, it is $\bigotimes X_i$).
+    Suppose further that $T$ preserves this limit.
+    Then $\bigotimes X_i$ is also an infinite tensor product of $\{X_i\}$ in $Kl(T)$.
+\end{proposition}
+\begin{lemma}
+    Let $J,J'$ be possibly infinite sets, and $\{X_i\}_{i\in J}, \{Y_i\}_{i\in J'}$ two families of objects in $\cC$, so that both have infinite tensor products with Kolmogorov extension.
+    Let $\{Z_i\}_{i\in J \sqcup J'}$ be a family of objects indexed by the disjoint union, where $Z_i = X_i$ for $i\in J$, $Z_i = Y_i$ for $i \in J'$,
+    and suppose $\{Z_i\}$ admits an infinite tensor product with Kolmogorov extension, too.
+    Consider the family of maps
+    \[\rho_F: \bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \labelto{\pi_{F \cap J} \tensor \pi_{F \cap J'}} \bigotimes_{i \in F \cap J}X_i \tensor \bigotimes_{i\in F \cap J'}Y_i\]
+    indexed by finite subsets $F \subset J \sqcup J'$ of the disjoint union.
+    The induced map
+    \[\bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \to \bigotimes_{i \in J \sqcup J'} Z_i\]
+    is a deterministic isomorphism.
+\end{lemma}
+\begin{proof}
+    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
+    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
+\end{proof}
 

### 2019-10-24 categorical-zero-one.tex
more on Secs 2 and 3

--- 2019-10-23 categorical-zero-one.tex
@@
 \begin{example}
-	$\FinStoch$ is the category of finite sets with \emph{stochastic maps}, where a stochastic map $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
-Stochastic maps compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
-We consider $\FinStoch$ as a monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic maps on morphisms.
+	\label{finstoch}
+	$\FinStoch$ is the category of finite sets with \emph{stochastic matrices}, which means that $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
+Stochastic matrices compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
+We consider $\FinStoch$ as a monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic matrices on morphisms.
 \end{example}
@@
 \begin{example}
+	\label{cring}
 	Let $\CRing_+$ be the category of commutative rings with maps which are merely additive and unit-preserving, considered as a monoidal category in the obvious way with respect to the tensor product of rings.
@@
 \begin{example}
+	\label{stoch}
 	$\Stoch$ is the category of measurable spaces $(X,\Sigma_X)$ as objects and Markov kernels as morphisms.
@@
 Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the monoidal structure is defined in terms of the usual product of measurable spaces.
+
+	There is a subcategory that will be of relevance to us later on in this paper: we define $\perfStoch \subseteq \Stoch$ to be the subcategory of all measurable spaces and those Markov kernels $f : \Sigma_Y \times X \to [0,1]$ which have the following additional property \ldots
 \end{example}
@@
 Our goal is to use semicartesian monoidal categories such as the above in order to develop aspects of probability theory in categorical terms.
-As it turns out, doing so requires a bit more structure, in a form which has been axiomatized in the notion of \emph{Markov category} \cite[Definition~2.1]{markov_cats}.
+As it turns out, doing so requires a bit more structure, in a form which has been axiomatized first by Cho and Jacobs~\cite{cho_jacobs} as \emph{affine CD-categories}, although similar definitions occur in earlier work of Golubtsov~\cite{golubtsov}.
+We here follow the terminology of our own~\cite[Definition~2.1]{markov_cats}.
 
 \begin{definition}
-	A Markov category $\cC$ is a semicartesian monoidal category \ldots
+	A \emph{Markov category} $\cC$ is a semicartesian symmetric monoidal category where every object $X \in \cC$ is equipped with a morphism
+	\begin{equation}
+		\label{comultiplication}
+		\tikzfig{comultiplication}
+	\end{equation}
+	which, together with the unique $X \to I$, makes $X$ into a commutative comonoid, and such that
+	\begin{equation}
+		\label{multiplicativity}
+		\tikzfig{multiplicativity}
+	\end{equation}
 	\label{markov_cat}
@@
 
-\todo[inline]{to be written}
+We think of the comultiplication~\Cref{comultiplication} as a copying operation.
+The coassociativity and counitality conditions guarantee that copying with any number of output wires is well-defined, and we draw it likewise as a single black dot with any number of outgoing wires, as in
+\[
+	\tikzfig{triple_copy}
+\]
+
+\Cref{finstoch,cring,stoch} are all Markov categories in a canonical way.
+In $\FinStoch$ and $\Stoch$, the comultiplication morphisms are given indeed by copying, i.e.~by those stochastic matrices or Markov kernels which map an $x \in X$ to the Dirac delta measure at $(x,x) \in X \times X$.
+We refer to~\cite[Example~2.5 and Section~4]{markov_cats} for the technical details.
+In $\CRing_+\op$, we define the comultiplication of an object $R \in \CRing_+\op$ to be represented by the multiplication map $R \otimes R \to R$.
+The multiplicativity condition~\eqref{multiplicativity} then amounts to the fact that the multiplication on a tensor product of commutative rings $R \otimes S$ is given by the defining equation
+\[
+	(r_1 \otimes s_1) (r_2 \otimes s_2) \, = \, r_1 r_2 \otimes s_1 s_2.
+\]
+
+\begin{definition}[{\cite[Definition~10.1]{markov_cats}}]
+	Let $\cC$ be a Markov category. A morphism $f : X \to Y$ in $\cC$ is \emph{deterministic} if it is a comonoid homomorphism,
+	\[
+		\tikzfig{multiplication_natural}	
+	\]
+\end{definition}
+
+As per~\cite[Remark~10.12]{markov_cats}, the deterministic morphisms form a symmetric monoidal cartesian subcategory $\cC_\detc \subseteq \cC$ which contains all structure morphisms of $\cC$, including the comultiplications themselves.
+The fact that all morphisms are comonoid homomorphisms implies that $\cC_\detc$ is cartesian monoidal.
+
+In $\FinStoch$, the deterministic morphisms $X \to Y$ are exactly the $\{0,1\}$-valued stochastic matrices.
+Since these can be identified with honest functions $X \to Y$, we conclude that $\FinStoch_\detc$ is equivalent to the category of finite sets.
+In $\Stoch$, the deterministic morphisms $f : X \to Y$ are exactly those Markov kernels for which $f(S|x) \in \{0,1\}$ for every $S \in \Sigma_Y$ and $x \in X$.
+In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness.
+In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive unital maps $S \to R$, i.e.~the ring homomorphisms.
+Thus the subcategory of deterministic morphisms is exactly the opposite of the usual category of commutative rings.
 
@@
 
-\todo[inline]{Let's also simplify notation by writing $X_J$ and $X_F$ instead of writing $\bigotimes$ every time. This is quite standard}
+\todo[inline]{Let's simplify notation by writing $X_J$ and $X_F$ instead of writing $\bigotimes$ every time, as you've already partly done}
 
-Suppose $\cC$ is a semicartesian monoidal category. In our
+Zero--one laws involve infinitely many random variables.
+In the setting of Markov categories, this means that we need to consider morphisms whose codomain is an ``infinite tensor product'' in a suitable sense.
+We start in this section by considering infinite tensor products in semicartesian symmetric monoidal categories.
 
-In order to make sense of infinite families of random variables within $\cC$,
-we will want to have a notion of infinite tensor product in $\cC$.
+Suppose that $(X_i)_{i \in J}$ is any family of objects, where the indexing set $J$ is typically infinite.
+For any finite subset $F \subseteq J$, we also write $X_F := \bigotimes_{i \in F} X_i$ for simplicity of notation.
 By Kolmogorov's extension theorem, the joint distribution of infinitely many random variables is uniquely determined by the family of distributions of all finite subsets of these variables.
-This motivates a general definition of the infinite tensor product of a family of objects $(X_i)_{i \in J}$, based on the observation that if $F \subseteq F' \subseteq J$ are two finite subset, then the fact that $\cC$ is semicartesian monoidal gives us morphisms
+This motivates our general definition of the infinite tensor product: if $F \subseteq F' \subseteq J$ are two finite subsets, then the fact that $\cC$ is semicartesian monoidal gives us \emph{marginalization morphisms}
 \[
-	\bigotimes_{i \in F'} X_i \longrightarrow \bigotimes_{i \in F} X_i
+	X_{F'} \longrightarrow X_F.
 \]
-to be interpreted as \emph{marginalization}.
-Via these maps, the finite tensor products $\bigotimes_{i \in F} X_i$ make up a cofiltered diagram in the form of a functor from the poset of finite subsets of $J$, ordered by reverse inclusion, to $\cC$.
+Via these maps, the finite tensor products $(X_F)_{F \subseteq J}$ make up a cofiltered diagram in the form of a functor from the poset of finite subsets of $J$, ordered by reverse inclusion, to $\cC$.
 
 \begin{definition}
-    Let $(X_i)_{i \in J}$ be a family of objects in $\cC$.
-    Then the \emph{infinite tensor product} $\bigotimes_{i \in J} X_i$ is the limit of the diagram \[F \longmapsto \bigotimes_{i \in F} X_i,\]
-    indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists.
+	\label{semicartesian_infproduct}
+	Let $(X_i)_{i \in J}$ be a family of objects in $\cC$. Then the \emph{infinite tensor product}
+	\[
+		X_J \: := \: \bigotimes_{i \in J} X_i
+	\]
+	is the limit of the diagram $F \mapsto X_F$, indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists.
 \end{definition}
 
-We will refer to the structure maps $\pi_F : \bigotimes_{i\in J} X_i \to \bigotimes_{i\in F} X_i$ as \emph{finite marginalizations}, and also write $\pi_j$ as shorthand for $\pi_{\{j\}}$.
-
-The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
-Intuitively, our definition matches up with these under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
+We will refer to the structure maps $\pi_F : X_J \to X_F$ as \emph{finite marginalizations}. % We also write $\pi_j$ as shorthand for $\pi_{\{j\}}$.
 
 \begin{remark}
-	If $J$ is finite, the infinite tensor product exists and coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
+	If $J$ is finite, then the infinite tensor product exists and coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
 \end{remark}
 
+\begin{remark}
+	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
+Thus in the case where our Markov category is $\CRing_+\op$, we recover the usual folklore definition of an infinite tensor product of rings $\bigotimes_{i \in J} R_i$ in terms of formal sums of elementary tensors, where an elementary tensor is a family of elements $(r_i)_{i \in J}$ such that all but finitely many are equal to the respective unit.
+Note that we do not yet consider the multiplication on $\bigotimes_{i \in J} R_i$, since \Cref{semicartesian_infproduct} is not yet concerned with the comonoid structures on the objects.
+We will get to this in the next section.
+
+	Intuitively, our definition matches up with these algebraic ones under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
+\end{remark}
+
+\begin{example}
+	To consider infinite tensor products in $\Stoch$, let $\left((X_i,\Sigma_i)\right)_{i\in J}$ be a family of measurable spaces.
+Then consider their cartesian product $X_J = \prod_{i \in J} X_i$ with the $\sigma$-algebra generated by the projections $\pi_i: X_J \to X_i$, which we denote $\Sigma_J$.
+Let us write in general $\Sigma_F$ for the product $\sigma$-algebra on finite products $X_F = \prod_{i\in F}X_F$, and $\pi_F: X_J \to X_F$ for the corresponding measurable projection.
+
+	In order to prove that this defines an infinite tensor product in $\Stoch$, let $(A,\Sigma_A)$ be another measurable space and let
+	\[
+		\left(g_F: A \times \Sigma_F \to [0,1]\right)_{F \subseteq J}
+	\]
+	be a collection of Markov kernels $A \to X_F$, one for each finite $F$, compatible with the marginalization morphisms.
+Consider an element $a \in A$ and a generating measurable set $\pi_F\inv(B) \in \Sigma_J$, where $B \in \Sigma_F$.
+Then we define a Markov kernel $h : A \to X_J$ by putting
+	\[
+		h(a,\pi_F\inv(B)) := g_F(a,B).
+	\]
+	The assumed compatibility condition guarantees that this is well-defined with respect to changing the choice of $F$.
+Since the collection of such $\pi_F\inv(B)$ is a ring of sets on $X$ which generates $\Sigma$ - hence by Carath\'eodory extension, there is a unique probability measure
+$p(a,-)$ on $X$ extending it. This is how we define $p(a,A)$ for general subsets $A \subset X$.
+
+Now consider the class of subsets $A \in \Sigma$ such that $p(-,A):A \to X$ is measurable.
+This class is a $\sigma$-algebra, which contains $\pi_F\inv(B)$, since $p(-,\pi_F\inv(B)) = p_F(-,B)$, which is measurable by assumption.
+Since these generate $\Sigma$, the map is always measurable.
+Hence $p$ is a Markov kernel.
+
+This argument also shows that this Markov kernel is determined uniquely by the fact that $p(a,\pi_F\inv(B)) = p_F(a,B) = \pi_F \circ p$.
+This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
+It is simple to verify that it also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
+\end{example}
+
 Of course, in a general Markov category the above cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
+
+\begin{example}
+	\label{infprods_finstoch}
+	$\FinStoch$ does not have infinite tensor products: if the family $(X_i)$ is such that no $X_i$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_i X_i$ does not exist.
+One way to see this is to use the fact that the hom-sets of $\FinStoch$ are convex sets in the space of matrices, and that composition distributes over these convex combinations, making $\FinStoch$ into a category enriched in convex sets.
+Since these hom-sets are finite-dimensional, for every $Y$ and $Z$ there is $n \in \bN$ such that among every $n$ morphism $Y \to Z$, one of them can be written as a convex combination of the others.
+Now suppose that the product $\bigotimes_i X_i$ existed.
+Then by choosing varying elements of each $X_i$, we can construct uncountably many morphisms $1 \to \bigotimes_i X_i$ whose marginalizations $1 \to X_F$ are all deterministic.
+Per the above, one of these hypothetical morphisms can be written as a convex combination of finitely many others.
+By choosing $F \subseteq J$ suitably, we can achieve that the finite marginalizations $1 \to X_F$ are all distinct.
+Since they are deterministic by construction, and no deterministic morphism in $\FinStoch$ can be written as a convex combination of other deterministic morphisms, we have arrived at a contradiction.
+\end{example}
+
+\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
+
+\todo[inline]{T: sounds good to me, can you put it in?}
 
@@
 To actually use this idea to reproduce the usual Kolmogorov zero-one law, we need to do a bit of work:
-
-\begin{example}
-Let $\{(X_i,\Sigma_i)\}_{i\in J}$ be a set of measurable spaces in $\sf{Stoch}$.
-Then consider their product $X = \prod_i X_i$ with the $\sigma$-algebra generated by the projections $\pi_i: X \to X_i$, which we denote $\Sigma$.
-Let us write in general $X_F = \prod_{i\in F}X_F$, $\Sigma_F$ for the corresponding $\sigma$-algebra, and $\pi_F: X \to X_F$ for the projection.
-
-Let $\{p_F: A \times \Sigma_F \to [0,1]\}_{F \subset J}$ be a collection of Markov kernels $A \to \prod_{i \in F}X_i$ for each $F$, compatible in the suitable sense.
-Consider a point $a \in A$ and a generator $\pi_F\inv(B)$ for $\Sigma$, where $B \in \Sigma_F$.
-Then we define $p(a,\pi_F\inv(B)) = p_F(a,B)$.
-Note that the collection of such $\pi_F\inv(B)$ is a ring of sets on $X$ which generates $\Sigma$ - hence by Caratheodory extension, there is a unique probability measure
-$p(a,-)$ on $X$ extending it. This is how we define $p(a,A)$ for general subsets $A \subset X$.
-
-Now consider the class of subsets $A \in \Sigma$ such that $p(-,A):A \to X$ is measurable.
-This class is a $\sigma$-algebra, which contains $\pi_F\inv(B)$, since $p(-,\pi_F\inv(B)) = p_F(-,B)$, which is measurable by assumption.
-Since these generate $\Sigma$, the map is always measurable.
-Hence $p$ is a Markov kernel.
-
-This argument also shows that this Markov kernel is determined uniquely by the fact that $p(a,\pi_F\inv(B)) = p_F(a,B) = \pi_F \circ p$.
-This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
-It is simple to verify that it also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
-\end{example}
-
-\begin{example}
-	\label{infprods_finstoch}
-	$\sf{FinStoch}$ does not have infinite tensor products.
-\end{example}
-\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
 

### 2019-10-25 categorical-zero-one.tex
through Sec 3 for now

@@
 Stochastic matrices compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
-We consider $\FinStoch$ as a monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic matrices on morphisms.
+We consider $\FinStoch$ as a symmetric monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic matrices on morphisms.
 \end{example}
@@
 	\label{cring}
-	Let $\CRing_+$ be the category of commutative rings with maps which are merely additive and unit-preserving, considered as a monoidal category in the obvious way with respect to the tensor product of rings.
+	Let $\CRing_+$ be the category of commutative rings with maps which are merely additive and unit-preserving, considered as a symmetric monoidal category in the obvious way with respect to the tensor product of rings.
 Then since $\CRing_+$ has the monoidal unit $\Z$ as its initial object, we can conclude that $\CRing_+\op$ is semicartesian monoidal.
@@
 Intuitively, $f$ assigns to every $x \in X$ a random element of $Y$.
-Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the monoidal structure is defined in terms of the usual product of measurable spaces.
+Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the symmetric monoidal structure is defined in terms of the usual product of measurable spaces.
+The monoidal unit $I$ is given by any one-element set with its unique $\sigma$-algebra.
+As a special case, morphisms $I \to (X,\Sigma_X)$ can be identified with probability measures $\sigma_X \to [0,1]$.
 
-	There is a subcategory that will be of relevance to us later on in this paper: we define $\perfStoch \subseteq \Stoch$ to be the subcategory of all measurable spaces and those Markov kernels $f : \Sigma_Y \times X \to [0,1]$ which have the following additional property \ldots
+	There is a well-known subclass of particularly well-behaved measurable spaces, the \emph{standard Borel spaces} or equivalently Polish spaces equipped with their Borel $\sigma$-algebras.
+We write $\BorelStoch \subseteq \Stoch$ for the full subcategory of standard Borel spaces with Markov kernels.
+Since finite products of standard Borel spaces are again standard Borel, $\BorelStoch$ is again semicartesian symmetric monoidal.
 \end{example}
 
-In the graphical calculus, the unique morphism $X \to I$ for an object $X \in \cC$ is denoted by
+Returning to the general theory, in string diagrams the unique morphism $X \to I$ for an object $X \in \cC$ is denoted by
 \[
@@
 \[
-	X_{F'} \longrightarrow X_F.
+	\pi_{F',F} \: : \: X_{F'} \longrightarrow X_F.
 \]
@@
 	If $J$ is finite, then the infinite tensor product exists and coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
+In a general Markov category, the relevant cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
 \end{remark}
 
-\begin{remark}
+\begin{example}
 	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
@@
 	Intuitively, our definition matches up with these algebraic ones under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
+\end{example}
+
+\begin{remark}
+	In those semicartesian monoidal categories $\cC$ that are of interest to us, morphisms $I \to X$ play the role of \emph{probability measures} on $X$.
+Thus applying the universal property with respect to maps out of $I$ amounts to requiring the \emph{Kolmogorov extension theorem} to hold in $\cC$: probability measures on an infinite product $X_J$ are in bijection with consistent families of probability measures on the finite products $X_F$ for $F \subseteq J$.
 \end{remark}
@@
 \begin{example}
-	To consider infinite tensor products in $\Stoch$, let $\left((X_i,\Sigma_i)\right)_{i\in J}$ be a family of measurable spaces.
-Then consider their cartesian product $X_J = \prod_{i \in J} X_i$ with the $\sigma$-algebra generated by the projections $\pi_i: X_J \to X_i$, which we denote $\Sigma_J$.
-Let us write in general $\Sigma_F$ for the product $\sigma$-algebra on finite products $X_F = \prod_{i\in F}X_F$, and $\pi_F: X_J \to X_F$ for the corresponding measurable projection.
+	We now consider infinite tensor products in $\Stoch$, where we would like infinite tensor products to be given by the corresponding infinite products of measurable spaces in the usual sense.
+Since the Kolmogorov extension theorem does not hold for general (even merely countable) products of measurable spaces~\cite{AJ}, this is not the case without further additional assumptions on the measurable spaces involved.
+Thus we do not know whether $\Stoch$ has infinite tensor products, although we suspect that it does not; but even if it does, they are in general not the ones that one would like to have for the purposes of probability theory.
 
-	In order to prove that this defines an infinite tensor product in $\Stoch$, let $(A,\Sigma_A)$ be another measurable space and let
+	However, the situation improves for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem holds~\cite[Theorem~14.35]{klenke}.
+In other words, if $\left( (X_i, \Sigma_i) \right)_{i \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{i \in \bN} X_i$ carrying the product $\sigma$-algebra $\Sigma_\bN$ satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
+In the following, we show that this implies the universal property in general.
+
+	Suppose that
 	\[
-		\left(g_F: A \times \Sigma_F \to [0,1]\right)_{F \subseteq J}
+		\Big( g_F : (A,\Sigma_A) \longrightarrow (X_F, \Sigma_F) \Big)_{F \subseteq J \text{ finite}}
 	\]
-	be a collection of Markov kernels $A \to X_F$, one for each finite $F$, compatible with the marginalization morphisms.
-Consider an element $a \in A$ and a generating measurable set $\pi_F\inv(B) \in \Sigma_J$, where $B \in \Sigma_F$.
-Then we define a Markov kernel $h : A \to X_J$ by putting
-	\[
-		h(a,\pi_F\inv(B)) := g_F(a,B).
-	\]
-	The assumed compatibility condition guarantees that this is well-defined with respect to changing the choice of $F$.
-Since the collection of such $\pi_F\inv(B)$ is a ring of sets on $X$ which generates $\Sigma$ - hence by Carath\'eodory extension, there is a unique probability measure
-$p(a,-)$ on $X$ extending it. This is how we define $p(a,A)$ for general subsets $A \subset X$.
+	is a family of Markov kernels satisfying the compatibility condition $\pi_{F',F} \circ g_{F'} = g_F$ for all finite $F \subseteq F' \subseteq J$.
+Then for every $a \in A$, the probability measures $g_F(-|a) : \Sigma_F \to [0,1]$ are a compatible family to which the Kolmogorov extension theorem in the form~\cite[Theorem~14.35]{klenke} applies, and we obtain a unique probability measure $g_J(-|a) : \Sigma_J \to [0,1]$ which has the $g_F(-|a)$ as its finite marginals.
+It remains to be shown that for every $S \in \Sigma_J$, the map $a \mapsto g_J(S|a)$ is measurable.
+Since limits of pointwise convergent sequences of measurable real-valued functions are again measurable, the set of $S$ for which this measurability holds is closed under countable disjoint union, and it is clearly closed under complements.
+We therefore have a $\lambda$-system.
+Since the map is measurable by assumption whenever $S$ is a measurable cylinder set, and the cylinder sets form a $\pi$-system, the $\pi$-$\lambda$-theorem implies that $a \mapsto g_J(S|a)$ is measurable for all $S$ in the $\sigma$-algebra generated by the measurable cylinder sets, which is exactly the product $\sigma$-algebra $\Sigma_J$.
 
-Now consider the class of subsets $A \in \Sigma$ such that $p(-,A):A \to X$ is measurable.
-This class is a $\sigma$-algebra, which contains $\pi_F\inv(B)$, since $p(-,\pi_F\inv(B)) = p_F(-,B)$, which is measurable by assumption.
-Since these generate $\Sigma$, the map is always measurable.
-Hence $p$ is a Markov kernel.
-
-This argument also shows that this Markov kernel is determined uniquely by the fact that $p(a,\pi_F\inv(B)) = p_F(a,B) = \pi_F \circ p$.
-This proves that $(X,\Sigma)$ is the limit of $(X_F,\Sigma_F)$, so that it is the tensor product $\bigotimes_{i\in J} X_i$.
-It is simple to verify that it also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
+	In conclusion, $\BorelStoch$ indeed has countable tensor products.
+It is plausible that there is is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
+However, we have so far not been able to find a suitable condition on Markov kernels which would be closed under composition, due to problems of perfect measures under mixtures~\cite{ramachandran}.
 \end{example}
-
-Of course, in a general Markov category the above cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
 
@@
 \todo[inline]{T: sounds good to me, can you put it in?}
-
-\begin{lemma}
-    Let $J,J'$ be possibly infinite sets, and $\{X_i\}_{i\in J}, \{Y_i\}_{i\in J'}$ two families of objects in $\cC$, so that both have infinite tensor products with Kolmogorov extension.
-    Let $\{Z_i\}_{i\in J \sqcup J'}$ be a family of objects indexed by the disjoint union, where $Z_i = X_i$ for $i\in J$, $Z_i = Y_i$ for $i \in J'$,
-    and suppose $\{Z_i\}$ admits an infinite tensor product with Kolmogorov extension, too.
-    Consider the family of maps
-    \[\rho_F: \bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \labelto{\pi_{F \cap J} \tensor \pi_{F \cap J'}} \bigotimes_{i \in F \cap J}X_i \tensor \bigotimes_{i\in F \cap J'}Y_i\]
-    indexed by finite subsets $F \subset J \sqcup J'$ of the disjoint union.
-    The induced map
-    \[\bigotimes_{i\in J}X_i \tensor \bigotimes_{i\in J'} Y_i \to \bigotimes_{i \in J \sqcup J'} Z_i\]
-    is a deterministic isomorphism.
-\end{lemma}
-\begin{proof}
-    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
-    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
-\end{proof}
 
@@
 
+\begin{example}
+	It is simple to verify that $\BorelStoch$ also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
+\end{example}
+
 This determines the comonoid structure uniquely: $\mathsf{copy}_{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$,
@@
 
-\section{Theorem}
+\begin{lemma}
+	Let $J = J_1 \sqcup J_2$ be a disjoint union, and $(X_i)_{i \in J}$ a family of objects in a semicartesian monoidal category $\cC$.
+Suppose that the infinite tensor products $X_{J_1}$ and $X_{J_2}$ exist.
+Then the object
+	\[
+		X_{J_1} \otimes X_{J_2} 
+	\]
+	is an infinite tensor product $X_J$ with respect to the finite marginalizations morphisms given by, for $F \subseteq J$,
+	\[
+		\begin{tikzcd}[column sep=huge]
+			X_{J_1} \otimes X_{J_2} \ar{r}{\pi_{F\cap J_1} \otimes \pi_{F\cap J_2}} & X_{F \cap J_1} \otimes X_{F \cap J_2}
+		\end{tikzcd}
+	\]
+\end{lemma}
+\begin{proof}
+    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
+    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
+\end{proof}
+
+\section{The zero--one laws}
+
 \begin{theorem}

### 2019-10-26 categorical-zero-one.tex
Secs 3 and 4 should be more or less solid now

@@
 
-For monoidal categories, we make frequent use of string diagram notation. We omit object labels whenever these are obvious from the context.
+Throughout, $\cC$ is a symmetric monoidal category.
+To simplify notation, we generally omit mention of the structure isomorphisms by assuming that $\cC$ is strict without loss of generality.
+We make frequent use of string diagram notation, and in doing so we omit object labels whenever these are obvious from the context.
 
-In \Cref{infprod_semicartesian}, $\cC$ denotes a semicartesian monoidal category.
+In \Cref{infprod_semicartesian}, $\cC$ denotes more concretely a semicartesian strict symmetric monoidal category.
 In \Cref{infprod_markov} and after, $\cC$ denotes a Markov category in the sense of \Cref{markov_cat}.
@@
 
-A monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal. Equivalently, it is a monoidal category equipped with morphisms
+A symmetric monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal. Equivalently, it is a monoidal category equipped with morphisms
 \[
@@
 
-Returning to the general theory, in string diagrams the unique morphism $X \to I$ for an object $X \in \cC$ is denoted by
+Returning to the general theory, in string diagrams the unique morphism $\discard{X} : X \to I$ for an object $X \in \cC$ is denoted by
 \[
@@
 \]
-The projection maps $X \otimes Y \to X$ and $X \otimes Y \to Y$ are correspondingly written as
+The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $X \otimes Y \to Y$ are correspondingly written as
 \[
@@
 \end{definition}
+
+There is a strictification result~\cite[Theorem~10.16]{markov_cats} which guarantees that $\cC$ can be assumed to be strict monoidal, as we do throughout.
 
@@
 \begin{example}
+	\label{infprods_cring}
 	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
@@
 \begin{example}
+	\label{infprods_stoch}
 	We now consider infinite tensor products in $\Stoch$, where we would like infinite tensor products to be given by the corresponding infinite products of measurable spaces in the usual sense.
@@
 	\label{infprods_finstoch}
-	$\FinStoch$ does not have infinite tensor products: if the family $(X_i)$ is such that no $X_i$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_i X_i$ does not exist.
+	Infinite tensor products never exist in $\FinStoch$, in the following sense: if the family $(X_i)$ is such that no $X_i$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_i X_i$ does not exist.
 One way to see this is to use the fact that the hom-sets of $\FinStoch$ are convex sets in the space of matrices, and that composition distributes over these convex combinations, making $\FinStoch$ into a category enriched in convex sets.
@@
 
-\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
-
-\todo[inline]{T: sounds good to me, can you put it in?}
-
-\section{Infinite tensor products in Markov categories}
-\label{infprod_markov}
-
-If a Markov category $\cC$ has infinite tensor products, then one should expect a suitable compatibility condition between these infinite tensor products and the comonoid structures on the objects to be satisfied.
-In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
+It is natural to require different infinite tensor products to interact well with another.
+If $X_J$ is an infinite tensor product of a family $(X_i)_{i \in J}$ and we are given an additional object $X_\ast$ for $\ast \not \in J$, then one will want $X_J \otimes X_\ast$ to be the infinite tensor product $X_{J \sqcup \{\ast\}}$ of the original family together with $X_\ast$, with finite marginalization morphisms given by
+\[
+		\pi_{F \setminus \{\ast\}} \otimes \id \: : \: X_J \otimes X_\ast \longrightarrow X_{F \setminus \{\ast\}} \otimes X_\ast
+\]
+for $\ast \in F$, and simply
+\[
+		\pi_F \otimes \discard{X_\ast} : X_J \otimes X_\ast \longrightarrow X_F 
+\]
+in case $\ast \not \in F$.
+It is straightforward to check that these morphisms exhibit $X_J \otimes X_\ast$ as the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
+This motivates the following definition.
 
 \begin{definition}
-    \label{defn_kolmogorov_ext}
-    Let $\cC$ be a Markov category, let $\{X_i\}_{i\in J}$ be an infinite family of objects, and let $\bigotimes_i X_i$ be an infinite tensor product.
-    We say this product \emph{satisfies Kolmogorov extension} if the following two conditions hold:
-    \begin{enumerate}[(1)]
-        \item The finite marginals \[\pi_F: \bigotimes_{i\in J} X_i \to \bigotimes_{i \in F} X_i\] are deterministic
-        \item These maps exhibit $\bigotimes_{i\in J} X_i$ as the cofiltered limit of the diagram $F \mapsto \bigotimes_{i \in F} X_i$ \emph{in $\cC_{\rm det}$}.
-    \end{enumerate}
+	\label{has_infprods}
+	Let $\cC$ be a semicartesian symmetric monoidal category.
+We say that $\cC$ \emph{has infinite tensor products} if for every family of objects $(X_i)_{i \in J}$ with $|J| < \kappa$, the infinite tensor product $X_J$ exists, and its defining cofiltered limit is preserved by every functor $Y \otimes -$.
+
+	For $\kappa$ a regular cardinal, we say that $\cC$ \emph{has tensor products of size $<\kappa$} if these conditions hold as soon as $|J| < \kappa$.
+For $\kappa = \aleph_1$, we also simply say that $\cC$ \emph{has countable tensor products}.
 \end{definition}
 
-\todo[inline]{Perhaps we could change the terminology to ``Kolmogorov product''. I'll tentatively use this in the following}
+\todo[inline]{We could also make the preservation condition part of the definition of infinite tensor product. Thoughts?}
 
-\begin{remark}
-    Since the (finite) tensor product is the product in $\cC_{\rm det}$, condition (2) is equivalent to the statement that the marginals
-    \[\pi_j: \bigotimes_i X_i \to X_j\]
-    exhibit $\bigotimes_i X_i$ as the product of the $X_j$ in $\cC_{\rm det}$,
-    since in any category, \[\lim_{F \subset J} \prod_{i \in F}X_i \cong \prod_{i \in J}X_i\]
-\end{remark}
-
-\begin{remark}
-    Condition (2) is also equivalent to the statement that, given a compatible family of deterministic maps $a_F: A \to \bigotimes_{i \in F} X_i$, the induced map $a: A \to \bigotimes_i X_i$ is deterministic.
-\end{remark}
-
-\begin{example}
-	It is simple to verify that $\BorelStoch$ also has Kolmogorov extension, using e.g. \cite[Example~10.4]{markov_cats}
-\end{example}
-
-This determines the comonoid structure uniquely: $\mathsf{copy}_{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$,
-and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
-
-\begin{remark}
-    Isomorphic objects in a Markov category can have non-isomorphic comonoid structures~\cite[Remark~10.9]{markov_cats}.
-    Therefore the condition of \Cref{defn_kolmogorov_ext} generally depends on the particular \emph{choice} of the infinite tensor product, rather than only on the mere existence of infinite tensor products in the underlying semicartesian monoidal category.
-\end{remark}
-
-To actually use this idea to reproduce the usual Kolmogorov zero-one law, we need to do a bit of work:
-
-From this point, the term \emph{infinite tensor product} will refer always to an infinite tensor product with Kolmogorov extension.
-
-This notion of infinite tensor product describes a notion of infinite collection of random variable where all dependence must be witnessed on some finite subset of the variables.
-
-We can codify this in the following definition
-\begin{definition}
-    Let $p: A \to \bigotimes_{i\in J}X_i$ be a map in $\cC$.
-    We say it exhibits the independence of $\{X_i\}$ given $A$ if each finite marginalization $A \to \bigotimes_{i \in F}X_i$ exhibits the independence of $\{X_i\}_{i \in F}$ given $A$.
-\end{definition}
+As per the above, the preservation condition in this definition amounts to the requirement that the canonical comparison morphism
+\[
+	X_J \otimes X_\ast \longrightarrow X_{J \sqcup \{\ast\}}
+\]
+must be an isomorphism, as one would expect intuitively from a notion of infinite tensor product.
+The explicit constructions of \Cref{infprods_cring,infprods_stoch} show that $\CRing_+\op$ has infinite tensor products and that $\BorelStoch$ has countable tensor products, respectively.
 
 \begin{lemma}
-	Let $J = J_1 \sqcup J_2$ be a disjoint union, and $(X_i)_{i \in J}$ a family of objects in a semicartesian monoidal category $\cC$.
+	\label{two_infproducts}
+	Suppose that $\cC$ has tensor products of size $< \kappa$.
+Let $J = J_1 \sqcup J_2$ be a disjoint union with $|J| < \kappa$, and $(X_i)_{i \in J}$ a family of objects in $\cC$.
 Suppose that the infinite tensor products $X_{J_1}$ and $X_{J_2}$ exist.
@@
 	\]
-	is an infinite tensor product $X_J$ with respect to the finite marginalizations morphisms given by, for $F \subseteq J$,
+	is an infinite tensor product $X_J$ with respect to the finite marginalizations morphisms given by, for every finite $F \subseteq J$,
 	\[
 		\begin{tikzcd}[column sep=huge]
-			X_{J_1} \otimes X_{J_2} \ar{r}{\pi_{F\cap J_1} \otimes \pi_{F\cap J_2}} & X_{F \cap J_1} \otimes X_{F \cap J_2}
+			\rho_F \: : \: X_{J_1} \otimes X_{J_2} \ar{r}{\pi_{F\cap J_1} \otimes \pi_{F\cap J_2}} & X_{F \cap J_1} \otimes X_{F \cap J_2}.
 		\end{tikzcd}
@@
 \begin{proof}
-    It is clear that the $\rho_F$ are deterministic, and that they form a limit diagram in $\cC_{\rm det}$.
-    Hence the induced map into the actual limit in $\cC_{\rm det}$ is an isomorphism.
+	For fixed finite $F_1 \subseteq J_1$, the morphisms
+	\[
+		\id \otimes \pi_{F_2} \: : \: X_{F_1} \otimes X_{J_2} \longrightarrow X_{F_1} \otimes X_{F_2}
+	\]
+	exhibit $X_{F_1} \otimes X_{J_2}$ as the cofiltered limit of the $X_{F_1} \otimes X_{F_2}$ by the preservation assumption. Similarly, the morphisms
+	\[
+		\pi_{F_1} \otimes \id \: : \: X_{J_1} \otimes X_{J_2} \longrightarrow X_{F_1} \otimes X_{J_2}
+	\]
+	exhibit $X_{J_1} \otimes X_{J_2}$ as the cofiltered limit of the $X_{F_1} \otimes X_{J_2}$.
+The claim follows as a limit of limits is a limit, and it is easy to see that the diagram shapes much up: the poset of finite subsets of $J_1 \sqcup J_2$ is the product of the posets of finite subsets of $J_1$ and $J_2$.
 \end{proof}
+
+More generally, we may consider infinite tensor products of infinite tensor products, $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$, where now $(J_k)_{k \in K}$ is a family of sets and $(X_{k,i})$ a doubly indexed family of objects.
+One may think that this doubly infinite tensor product should be isomorphic to the single-step infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
+And indeed, if for every finite $F \subseteq \prod_{k \in K} J_k$ we choose any finite $G \subseteq K$ such that $(k,i) \in F$ implies $k \in G$, then we have morphisms
+\begin{equation}
+	\label{double_infproduct}
+	\begin{tikzcd}[column sep=huge]
+		\rho_F \: : \: \bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i} \ar{r}{\pi_G} & \bigotimes_{k \in G} \bigotimes_{i \in J_k} X_{k,i} \ar{r}{\bigotimes_{k \in G} \pi_{F \cap J_k}} & \bigotimes_{k \in G, \: i \in F \cap J_k} X_{k,i}
+	\end{tikzcd}
+\end{equation}
+where the object on the right can also be written as $\bigotimes_{(k,i) \in F} X_{k,i}$.
+It is straightforward to see that this $\rho_F$ does not depend on the particular choice of $G$.
+We now show that these $\rho_F$'s are finite marginalization morphisms which make the doubly infinite tensor product $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$ into the single infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
+
+\begin{lemma}
+	Suppose that $\cC$ has tensor products of size $< \kappa$, and let $(J_k)_{k \in K}$ be a family of sets with $|K| < \kappa$ and $|J_k| < \kappa$, and $(X_{k,i})_{i \in J_k, k \in K}$ a doubly indexed family of objects.
+Then the above $\rho_F$ exhibit the infinite tensor product of infinite tensor products $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$ as the infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
+\end{lemma}
+\begin{proof}
+	By repeated application of \Cref{two_infproducts}, the second half of~\Cref{double_infproduct} exhibits $\bigotimes_{k \in G} \bigotimes_{i \in J_k} X_{k,i}$ as the infinite product of the $X_{k,i}$ for $k \in G$ and $i \in J_k$.
+The claim then follows from a straightforward diagram chase.
+\end{proof}
+
+\section{Infinite tensor products in Markov categories}
+\label{infprod_markov}
+
+If a Markov category $\cC$ has infinite tensor products, then one should expect a compatibility condition between these infinite tensor products and the comonoid structures on the objects.
+% In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
+
+\begin{definition}
+    \label{defn_kolmogorov_ext}
+    Let $\cC$ be a Markov category and $(X_i)_{i \in J}$ a family of objects.
+We say that an infinite product $X_J = \bigotimes_{i \in J} X_i$ is a \emph{Kolmogorov product} if the finite marginalization morphisms $\pi_F : X_J \to X_F$ are deterministic, and the universal property is preserved by every functor $Y \otimes -$.
+
+    We say that $\cC$ \emph{has Kolmogorov products} if every family of objects has a Kolmogorov product.
+For $\kappa$ a regular cardinal, we say that $\cC$ has \emph{Kolmogorov products of size $<\kappa$} if families of size $<\kappa$ have a Kolmogorov product.
+For $\kappa = \aleph_1$, we say that $\cC$ has \emph{countable Kolmogorov products}.
+\end{definition}
+
+In $\BorelStoch$, the infinite tensor products constructed in \Cref{infprods_stoch} are Kolmogorov products.
+In $\CRing_+\op$, the infinite tensor products from \Cref{infprods_cring} are Kolmogorov products as well as long as one equips $\bigotimes_i R_i$ with the tensor product ring structure, since this one is the only one which makes the canonical inclusions $R_i \to \bigotimes_i R_i$ into ring homomorphisms.
+These examples illustrate an important point: in some Markov categories, such as $\CRing_+\op$, not all isomorphisms are deterministic, and there may even be isomorphic objects which have no deterministic isomorphism~\cite[Remark~10.9]{markov_cats}.
+In these categories, whether a given object is an infinite tensor product or not generally depends on the specific choice of that object.
+In particular, there may be infinite tensor products which are not Kolmogorov products.
+For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_i R_i$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
+
+\begin{proposition}
+	Every Kolmogorov product is a categorical product in $\cC_\detc$.	
+\end{proposition}
+
+\begin{proof}
+	For $(X_i)_{i \in J}$ a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$, we first show that if we have a compatible family of deterministic morphisms $g_F : A \to X_F$, then also the induced $g_J : A \to X_J$ is deterministic.
+Drawing the Kolmogorov product $X_J$ as a double wire, we need to prove the determinism equation
+	\[
+		\tikzfig{gJ_det}
+	\]
+	By \Cref{two_infproducts}, the codomain object $X_J \otimes X_J$ is itself an infinite tensor product, and it is therefore enough to prove
+	\[
+		\tikzfig{gJ_det2}
+	\]
+	where we have assumed without loss of generality that the two finite marginalization maps are the same, which we can by replacing the corresponding finite subsets by their union.
+Using the determinism assumption for $\pi_F$ on the right as well as the assumption that $g_F = \pi_F \circ g_J$ is deterministic implies the claim.
+
+	Now since every finite tensor product $X_F$ is a categorical product in $\cC_\detc$, we can use the fact that in every category,
+    	\[
+		\lim_{F \subseteq J \text{ finite}} \: \prod_{i \in F} X_i \: \cong \: \prod_{i \in J} X_i,
+	\]
+	and this is what was to be shown.
+\end{proof}
+
+In particular, this proves that the comonoid structure on a Kolmogorov product is determined uniquely: $\cop{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$, and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
+
+\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
+
+\todo[inline]{T: sounds good to me, can you put it in?}
+
+The notion of Kolmogorov product describes a notion of infinite collection of random variables where all dependence must be encoded in the finite subsets of the variables.
+We capture this in the following definition.
+
+\begin{definition}
+	We say that a morphism $p_J : A \to \bigotimes_{i \in J} X_i$ \emph{displays the conditional independence} $\perp_{i \in J}  X_i \:|\: A$ if each finite marginalization $p_F : A \to \bigotimes_{i \in F}X_i$ displays the conditional independence $\perp_{i \in F} X_i \:|\: A$.
+\end{definition}
 

### 2019-10-27 categorical-zero-one.tex
first iteration done, some more fixes coming up

@@
 	We state and prove the zero--one laws of Kolmogorov and Hewitt--Savage within the setting of \emph{Markov categories}, a category-theoretic approach to the foundations of probability and statistics.
-This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones, but also in other contexts such as categories of closed relations between topological spaces,
-	\improve{T: this abstract states what we can hopefully achieve. To be adjusted}
+This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts.
+For example, applying them to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces are constant.
 \end{abstract}
@@
 
+We introduce two more definitions that we will be using later on.
+
+\begin{definition}[{\cite[Definition~11.30]{markov_cats}}]
+	A Markov category $\cC$ is \emph{causal} if whenever
+	\[
+		\tikzfig{causal1}
+	\]
+	holds for morphisms as indicated, then also
+	\[
+		\tikzfig{causal2}
+	\]
+	\label{causal_defn}
+\end{definition}
+
+It is known that $\Stoch$ is causal~\cite[Example~11.34]{markov_cats}, and therefore so are the subcategories $\BorelStoch$ and $\FinStoch$.
+We do not know whether $\CRing_+\op$ is causal, although we suspect that~\cite[Example~11.31]{markov_cats} can be modified to show that it is not.
+
+The following definition goes back to Cho and Jacobs~\cite[Definition~5.1]{cho_jacobs}, but also appears as~\cite[Definition~13.1]{markov_cats}.
+
+\begin{definition}
+	Given morphisms $p : A \to X$ and $f,g : X \to Y$ in a Markov category, we say that $f$ and $g$ are \emph{$p$-a.s.~equal} if
+	\[
+		\tikzfig{asequal}
+	\]
+	and we also write this more concisely as $f =_{p\as} g$.
+\end{definition}
+
 \section{Infinite tensor products in semicartesian monoidal categories}
 \label{infprod_semicartesian}
-
-\todo[inline]{Let's simplify notation by writing $X_J$ and $X_F$ instead of writing $\bigotimes$ every time, as you've already partly done}
 
@@
 
+\begin{remark}
+	If $\cC$ is positive in the sense of~\cite[Definition~11.22]{markov_cats}, then a morphism $A \to B \otimes C$ is deterministic if and only if both of its marginals are $A \to B$ and $A \to C$ are deterministic~\cite[Corollary~12.15]{markov_cats}.
+In this case, it follows that the finite marginalizations $\pi_F$ are deterministic if and only if all the single-factor marginalizations $\pi_{\{i\}} : X_J \to X_i$ are.
+Thus for an infinite tensor product to be a Kolmogorov product, it is then enough to verify that the $\pi_{\{i\}}$ are deterministic.
+\end{remark}
+
 \begin{proposition}
 	Every Kolmogorov product is a categorical product in $\cC_\detc$.	
+	\label{kolmprod_catdet}
 \end{proposition}
-
 \begin{proof}
@@
 \begin{definition}
-	We say that a morphism $p_J : A \to \bigotimes_{i \in J} X_i$ \emph{displays the conditional independence} $\perp_{i \in J}  X_i \:|\: A$ if each finite marginalization $p_F : A \to \bigotimes_{i \in F}X_i$ displays the conditional independence $\perp_{i \in F} X_i \:|\: A$.
+	We say that a morphism $p_J : A \to \bigotimes_{i \in J} X_i$ \emph{displays the conditional independence} $\perp_{i \in J}  X_i \mid\mid A$ if each finite marginalization $p_F : A \to \bigotimes_{i \in F}X_i$ displays the conditional independence $\perp_{i \in F} X_i \mid\mid A$.
 \end{definition}
@@
 
-\begin{theorem}
-    \label{thm:kolmog}
-    Suppose we are given $p: A \to T \tensor \bigotimes_{i \in J} X_i$ satisfying the following conditions:
-    \begin{enumerate}
-        \item $T$ is a deterministic function of $\bigotimes_{i \in J} X_i$.
-        \item For each finite subset $F \subset J$, the marginal $A \to T \tensor \bigotimes_{i \in F}X_i$ displays the independence of $T$ and $\bigotimes_{i \in F} X_i$.
-    \end{enumerate}
-    Then the marginal $A \to T$ is deterministic as well.
-\end{theorem}
+Throughout this section, $(X_i)_{i \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
 
-This theorem is a consequence of two lemmas.
 \begin{lemma}[The infinite independence lemma]
-    Suppose $p: A \to \bigotimes X_i$ exhibits the independence of $\{X_i\}$.
-    Then for each $j$, the map $A \to X_j \tensor \bigotimes_{i \neq j}X_i$ exhibits the independence $X_j \bot \tensor_{i\neq j} X_i \mid \mid A$.
+	Suppose $p: A \to X_J$ displays the conditional independence $\perp_i X_i \mid\mid A$.
+	Then for every $i \in J$, it also displays the independence $X_j \perp X_{J \setminus \{i\}} \mid\mid A$.
 \end{lemma}
-\begin{proof}[Sketch of proof]
-    To prove this, we must compare two maps $A \to X_j \tensor \bigotimes_{i\neq j} X_i \cong \bigotimes_i X_i$.
-    To show that these maps are equal, it suffices to show that all finite marginalizations of them are equal.
-    But this is an immediate consequence of the assumption.
+\begin{proof}
+	This is nontrivial because the assumption by definition only involves conditional independence of the finite marginalizations. What we need to prove is that
+	\[
+		\tikzfig{infind_lemma_goal}
+	\]
+	As the codomain is exactly the Kolmogorov product $X_J$, it is enough to prove this equation upon composing the second output with the finite marginalizations $\pi_F : X_{J\setminus\{i\}} \to X_F$.
+But this is a consequence of the assumption.
 \end{proof}
@@
 \begin{lemma}[The determinism lemma]
-    Suppose $p: A \to T \tensor X$ is such that $T$ is a deterministic function of $X$, and $p$ exhibits the independence $T \bot X \mid \mid A$.
-    Then the marginal $A \to T$ is deterministic.
+	\label{determinismlemma}
+	Suppose that we have $p: A \to X$ and deterministic $s : X \to T$. If the joint
+	\begin{equation}
+		\label{determinismlemma_joint}
+		\tikzfig{determinismlemma_joint}	
+	\end{equation}
+	displays the conditional independence $X \perp T \mid\mid A$, then the composite $sp: A \to T$ is deterministic.
+\end{lemma}
+This result can be thought of as a partial converse to the condition which characterizes positivity of a Markov category~\cite[Definition~11.22]{markov_cats}.
+\begin{proof}
+	Since the marginals of \Cref{determinismlemma_joint} are exactly $p$ and $sp$, the conditional independence assumption is
+	\[
+		\tikzfig{determinismlemma1}
+	\]
+	Using this equation together with the assumption that $s$ is deterministic, we then compute
+	\[
+		\tikzfig{determinismlemma2}
+	\]
+	which is what was to be shown.
+\end{proof}
+
+Here is our abstract version of Kolmogorov's zero--one law.
+
+\begin{theorem}
+    \label{thm:kolmog}
+    Suppose that $\cC$ is a Markov category, and that $(X_i)_{i \in J}$ is a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
+
+    If morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ are such that for every finite $F \subseteq J$, the joint
+    \[
+	    \tikzfig{kolmog_joint}
+    \]
+    displays the conditional independence $X_F \perp T \mid\mid A$, then the composite $sp : A \to T$ is deterministic as well.
+\end{theorem}
+Note that this result applies even in the case where $J$ is finite, in which case it amounts to \Cref{determinismlemma}.
+\begin{proof}
+	Assuming $\ast \not \in J$, let us write $X_\ast := T$, so that $X_J \otimes X_\ast$ is the Kolmogorov product of the family $(X_i)_{i \in J \,\sqcup\,\{\ast\}}$.
+It is clear from the definitions and the assumption that the morphism
+    \[
+	\tikzfig{kolmog_joint2}	    
+    \]
+    displays the conditional independence $\perp_{i \in J\,\sqcup\,\{\ast\}} X_i \mid\mid A$.
+    By the infinite independence lemma, this means that it also displays the conditional independence $X_\ast \perp X_J \mid\mid A$.
+    Now the determinism lemma implies exactly what we want, that the composite $sp : A \to T$ is deterministic.
+\end{proof}
+
+We now move on to our treatment of the Hewitt--Savage zero--one law.
+It applies to Kolmogorov products where all factors are copies of the same object.
+So for an object $X$ and the constant family $(X)_{i \in J}$, let us say that the corresponding Kolmogorov product $X_J$ is the \emph{Kolmogorov power} of $X$ by $J$.
+
+A \emph{finite permutation} of the set $J$ is a bijection $\alpha : J \to J$ which fixes all but finitely many elements.
+Suppose that $\alpha : J \to J$ is a finite permutation or more generally any injection.
+Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_J$ in the obvious way: the morphisms
+\[
+	\begin{tikzcd}
+		X_J \ar{r}{\pi_F} & X_F \ar{r}{\cong} & X_{\alpha(F)}
+	\end{tikzcd}
+\]
+where the second morphism matches up the factors of the two finite products involved as prescribed by the bijection $\alpha|_F : F \stackrel{\cong}{\longrightarrow} \alpha(F)$.
+The relevant compatibility condition is straightforward to check.
+Moreover, $\hat{\alpha}$ is deterministic by \Cref{kolmprod_catdet}.
+
+\begin{theorem}[Hewitt--Savage for Markov categories]
+    	\label{thm:hewsav}
+	Suppose that $\cC$ is a causal Markov category and that $X_J$ is a Kolmogorov power of an object $X \in \cC$ with respect to an infinite set $J$.
+
+    	Suppose that morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ satisfy the following:
+    	\begin{enumerate}
+		\item $p$ displays the conditional independence $\perp_i X_i \mid\mid A$.
+		\item For every finite permutation $\alpha : J \to J$ we have $\hat{\alpha} p = p$ and $s \hat{\alpha} = s$. 
+    	\end{enumerate}
+	Then the composite $sp : A \to T$ is deterministic.
+\end{theorem}
+
+In contrast to \Cref{thm:kolmog}, we now have two additional relevant assumptions: $\cC$ is causal and $J$ is infinite. We first prove a useful auxiliary observation.
+
+\begin{lemma}
+	\label{aseqlemma}
+	Let $\cC$ be a causal Markov category (\Cref{causal_defn}). Let $p : A \to X$ and $f,g: X \to Y$ be morphisms with $f$ deterministic and such that
+	\[
+		\tikzfig{aseqlemma}
+	\]
+	Then $f =_{p\as} g$.
 \end{lemma}
 \begin{proof}
-The proof is a string diagram chase:
-First, the assumption that $T$ is a deterministic function of $X$ means precisely that we can find $f$ deterministic so that.
-
-%\tikzfig{determinismlemma1}.
-
-Now we can use the independence of $X$ and $T$, and the axioms, to rewrite this as
-
-%\tikzfig{determinismlemma2}
-
-Applying the map $1_T \tensor f$ to the second and fourth diagram now gives an equality
-
-%\tikzfig{determinismlemma3}
-
-Where we have also applied the determinism of $f$.
-This is precisely the statement that $A \to T \tensor X \to X \labelto{f} T$ is deterministic.
-
-Lastly, we use the equality
-
-%\tikzfig{determinismlemma4}
-
-To see that the marginal $A \to T \tensor X \to T$ is deterministic as desired.
-
+    Consider the morphism
+    \[
+	    \tikzfig{aseqlemma1}
+    \]
+    Applying the assumed equation together with determinism of $f$ shows that marginalizing over the first output gives the same morphism $A \to Y \otimes Y$ as marginalizing over the second output.
+Therefore, applying the causality property of \Cref{causal_defn} with $h_1$ and $h_2$ the two marginalizations, we can conclude the equality
+    \[
+	\tikzfig{aseqlemma2}
+    \]
+    Marginalizing this further over the middle output and truncating the redundant pieces proves the desired equation.
 \end{proof}
 
-\begin{proof}[Proof of the theorem]
-    It's clear from the definition that $A \to T \tensor \bigotimes X_i$ exhibits the independence of $\{T, X_1, \dots\}$.
-    By the infinite independence lemma, this means that it also exhibits the independence $T \bot \bigotimes X_i \mid \mid A$.
-    Now the determinism lemma implies exactly what we want, that the marginal $A \to T$ is deterministic.
+\begin{proof}[Proof of \Cref{thm:hewsav}]
+	Letting a finite permutation $\sigma : J \to J$ act on the $X_J$ part of the joint of $X_J$ and $T$ gives
+	\begin{equation}
+		\label{strong_invariance}
+		\tikzfig{hewsav1}
+	\end{equation}
+	so that the joint is invariant. Here, the first and last equation hold by the invariance assumption, and the second because $\hat{\alpha}$ is deterministic.
+
+	We next show that this equation still holds if $\alpha$ is merely an injection.
+By the universal property of $X_J \otimes T$ as the infinite tensor product of the family $(X_i)_{i \in J}$ together with $T$, it is enough to prove \Cref{strong_invariance} upon marginalization by $\pi_F \otimes \id$ for all finite $F \subseteq J$.
+Since we can find a finite permutation $\alpha' : J \to J$ such that $\alpha'|_F = \alpha|_F$, the claim follows from the finite permutation case.
+
+	Consider the morphism given by composing \eqref{strong_invariance} with $s$ on the first output.
+Since these are the same for all injections $\alpha$, \Cref{aseqlemma} tells us that the morphisms $s \hat{\alpha}$ are all $p$-a.s.~equal to $s$, for every injection $\alpha : J \to J$.
+
+	Now let $J = J_1 \,\sqcup\, J_2$ be a decomposition of $J$ into two disjoint subsets having the cardinality of $J$; here is where it is relevant that $J$ is infinite.
+Let $\tau_1, \tau_2: J \to J$ be injections with images $J_1$ and $J_2$, respectively.
+Then we claim that
+	\[
+		\tikzfig{hewsav2}
+	\]
+	By \Cref{two_infproducts}, it is enough to prove this upon postcomposing with two finite marginalizations $\pi_{F_1}$ and $\pi_{F_2}$.
+But then using the fact that $\tau_1$ and $\tau_2$ have disjoint image, this follows from the independence assumption, which has
+	\[
+		\tikzfig{hewsav3}
+	\]
+	as a special case.
+
+	Putting things together, we can now compute
+	\[
+		\tikzfig{hewsav4}
+	\]
+	which is what was to be shown.
 \end{proof}
 
-\begin{corollary}[Kolmogorov zero to one law]
-    Suppose $\Omega$ is a measure space with a probability measure $P$, $\{f_i: \Omega \to X_i\}$ is a collection of independent random variables,
-    and $T \subset \Omega$ is a subset in the $\sigma$-algebra generated by the $f_i$, such that $1_T$ is independent of any finite subset of the $f_i$.
+\section{Examples}
+
+We now show how our results specialize to the standard Kolmogorov and Hewitt--Savage zero--one laws in the case of standard Borel spaces.
+Further down we give another application to continuous maps between topological spaces.
+
+\begin{corollary}[Kolmogorov zero--one law]
+	Suppose $\Omega$ is a standard Borel space with a probability measure $P$ and that $\left(f_i: \Omega \to X_i\right)_{i \in \bN}$ is a sequence of independent random variables taking values in standard Borel spaces $X_i$.
+Suppose that $T \subseteq \Omega$ is in the coarsest $\sigma$-algebra which makes the $f_i$ measurable, and independent of any finite subset of the $f_i$.
     Then $P(T)$ is $0$ or $1$.
@@
 \begin{proof}
-    Consider the composite $I \labelto{P} \Omega \labelto{1_T, \{f_i\}} \{0,1\} \tensor \bigotimes_i X_i$.
-    Then independence of the $f_i$ means precisely that this map exhibits the independence of $\{X_i\}$ given $I$ in the above sense.
-    Moreover, $T(\omega)$ is determined by the values of $f_i(\omega)$, so $T$ factors as a map $\prod_i X_i \to \{0,1\}$, and
-    this map is measurable.
-    Hence we can apply the theorem, and conclude that the map $I \labelto{P} \Omega \labelto{T} \{0,1\}$ is deterministic - but this means it's just a constant map,
-    which precisely means that $T$ is true or false with probability $1$.
+	We want to apply \Cref{thm:kolmog} with $\cC = \BorelStoch$ and $J = \bN$ and $A = I$, the one-element measurable space.
+Then $P : I \to \Omega$.
+We write $f_\bN : \Omega \to X_\bN$ for the induced map to the product.
+In $\Omega$, the coarsest $\sigma$-algebra which makes the $f_i$ measurable coincides with the $\sigma$-algebra consisting of the sets of the form $f_\bN^{-1}(S)$ for measurable $S \subseteq X_J$.
+Hence the assumption implies that there is measurable $S \subseteq X_J$ such that $T = f_\bN^{-1}(S)$.
+Then we apply \Cref{thm:kolmog} with $s : X_J \to \{0,1\}$ the indicator function of $S$, which is a measurable map and therefore can also be regarded as a morphism in $\BorelStoch$.
+We therefore obtain that $sp : I \to \{0,1\}$ is deterministic.
+But since $sp$ corresponds to the probability measure on $\{0,1\}$ with weight $P(f_\bN^{-1}(S)) = P(T)$ on $\{1\}$ and the complementary weight $1 - P(T)$ on $0$, we conclude that indeed $P(T) \in \{0,1\}$.
 \end{proof}
 
-We can also prove a version of the Hewitt-Savage theorem
-\begin{definition}
-    Let $\alpha: J \to J$ be any map.
-    Then it induces a map 
-    \[\hat{\alpha}: \bigotimes_{i\in J}X_i \to \bigotimes_{i \in J}X_{\alpha(i)},\]
-    which we may suggestively write as $(x_i)_{i\in J} \mapsto (x_{\alpha(i)})_{i\in J}$.
+\begin{problem}
+	Is there a Markov category $\cC$ with countable Kolmogorov products such that \Cref{thm:kolmog} specializes to the standard Kolmogorov zero--one law in its general form?
+\end{problem}
 
-    It is clear that this map is always deterministic. Moreover, if $\alpha$ is a bijection, this map is an isomorphism.
-\end{definition}
+\todo[inline]{describe the application of \Cref{thm:hewsav} to $\BorelStoch$}
 
-\begin{theorem}[Hewitt-Savage for Markov categories]
-    \label{thm:hewsav}
-    Let $\cC$ be a causal Markov category with infinite tensor products. Let $A \to \cC$ be a map in $\cC$, $J$ an infinite set, and let $f: \bigotimes_{i \in J}X \to T$ be a deterministic map.
-    Suppose for each finite permutation $\sigma: J \to J$, we have $f \circ \hat{\sigma} = f$ - in other words, $f$ is independent of finite permutations of the inputs.
-    Then the composite $A \to \tensor_J A \to \tensor_J X \to T$ is deterministic.
-\end{theorem}
-Again, we factor part of the proof into a lemma.
-\begin{lemma}
-    Let $\cC$ be a causal markov category, and let $f,g: B \to X$ be maps, $f$ deterministic.
-    Let $p: A \to B$ be any map.
-    Suppose the composites 
-    \[A \to B \to B \tensor B \labelto{f \tensor g} X \tensor X\]
-    and
-    \[A \to B \to B \tensor B \labelto{f \tensor f} X \tensor X\]
-    agree. Then $f = g$ $p$-almost everywhere.
-\end{lemma}
-\begin{proof}[Sketch of sketch of proof]
-    Consider the map
-    $A \labelto{p} B \to B \tensor B \labelto{f \tensor g} X \tensor X \labelto{copy_{X \tensor X}} X \tensor X \tensor X \tensor X$.
-    Whether we marginalize on the first or second factor of $X$, we get equal morphisms, because we may replace the first part of this with
-    $A \to B \labelto{f} B \to X \tensor X \tensor X \tensor X$ by using the assumptions and determinism.
-
-    Then applying causality, with $f = p$, $g= (f \tensor g) \circ copy_B$, $h_1 = (del_X \tensor 1_X)$, $h_2  = (1_X \tensor del_X)$.
-    Marginalizing the resulting (equal) diagrams, one of them is 
-    \[A \to B \to B \tensor B \labelto{f, 1_B} B \tensor B,\]
-    one of them is 
-    \[A \to B \to B \tensor B \labelto{g,1_B} B \tensor B,\]
-    and this is precisely what must hold for them to agree $p$-a.e.
-\end{proof}
-
-\begin{proof}[Proof of theorem]
-    Consider the map
-
-    \[e: A \to \tensor_J A \labelto{\tensor p} (\tensor_J X) \to (\tensor_J X) \tensor (\tensor_J X) \to T \tensor (\tensor_J X)\]
-
-    Denote by $e_\sigma$ the composite of $e$ with $1_T \tensor \hat{\sigma}$
-    Note that if $\sigma$ is a finite permutation, $e_\sigma = e$. To see this, note that we may add a $\hat{\sigma}$ before the $f$ as well, by assumption.
-    Now we can use the determinism of the $\hat{\sigma}$s, and the clear fact that 
-    \[A \to \tensor A \to \tensor B \labelto{\hat{\sigma}} \tensor B = A \to \tensor A \to \tensor B\]
-
-    Now let $\sigma$ instead be an injection. Then for each finite subset $F \subset J$, we can find a finite permutation of $J$, $\sigma_0$, such that $\sigma|_F = \sigma_0|_F$.
-    Then on this marginal, $e_\sigma = e_{\sigma_0} = e$, hence $e_\sigma = e$ in general.
-
-    Let $J = J_0 \sqcup J_1$ be a decomposition of $J$ into two disjoint subsets with the cardinality of $J$ (here we use $J$ infinite).
-    Let $\tau_0, \tau_1: J \to J$ be injections with image $J_0,J_1$ respectively.
-
-    Now consider the map $a_\sigma: A \to T \tensor T$ given by composing $e_\sigma$ with $t$.
-    By the above, they all agree.
-    By the lemma, we see that the maps $\tensor_J X \labelto{\hat{\sigma}} \tensor_J X \to T$ are all $\tensor_J p$ a.e. equal.
-    Applying this to $\tau_0,\tau_1$, we get that the map $A \to T$ must be deterministic.
-\end{proof}
-In the last step, the idea is that precomposing with $\hat{\tau_0}$ and $\hat{\tau_1}$ is essentially picking out two disjoint subsets and using them to determine $T$.
-Since all the variables are independent, these two are clearly independent, but also equal (by the preceding argument). Hence they are deterministic, but they also agree with the original map.
-
-\section{Examples}
-As noted, theorems \cref{thm:kolmog} and \cref{thm:hewsav}, when intepreted in the Markov category $\mathsf{Stoch}$, recover the classical Kolmogorov and Hewitt-Savage zero to one laws.
-\improve{Maybe move those examples to here? Also figure out where to put proof that $Kl(H)$ has infinite tensor product and Kolmogorov extension. (And introduce $H$)}
-
-By intepreting them in other Markov categories, we obtain other nontrivial (although hardly particularly deep) statements:
+By interpreting our results in other Markov categories, we obtain other nontrivial (although hardly particularly deep) statements:
 
@@
 
+\todo[inline]{I agree with the speculation, but it's probably a bit too vague for the paper in its present state, so I've removed it}
+
+\bibliographystyle{plain}
+\bibliography{categorical-zero-one}
+
+\end{document}
+
 \section{Speculation}
@@
 For instance, maybe there is a Markov category with objects the profinite sets, which can be obtained from $\sf{FinStoch}$ by some formal construction (maybe even simply as the pro-category), which admits infinite tensor products, and where one can profitably interpret this theorem.
-
-\bibliographystyle{plain}
-\bibliography{categorical-zero-one}
-
-\end{document}

### 2019-10-27 categorical-zero-one.tex
finished revision

@@
 \section{Introduction}
+
+\todo[inline]{Add some motivation and summary}
 
@@
 \]
-The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $X \otimes Y \to Y$ are correspondingly written as
+The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $\discard{Y} \otimes \id : X \otimes Y \to Y$ are correspondingly written as
 \[
@@
 	\end{equation}
-	which, together with the unique $X \to I$, makes $X$ into a commutative comonoid, and such that
+	which, together with $\discard{X} : X \to I$, makes $X$ into a commutative comonoid, and such that
 	\begin{equation}
@@
 	\end{equation}
+	for all $X, Y \in \cC$.
 	\label{markov_cat}
@@
 
-We introduce two more definitions that we will be using later on.
+We state some more definitions that we will be using later on.
 
@@
 
-The following definition goes back to Cho and Jacobs~\cite[Definition~5.1]{cho_jacobs}, but also appears as~\cite[Definition~13.1]{markov_cats}.
+The following definition goes back to Cho and Jacobs~\cite[Definition~5.1]{cho_jacobs}. A more detailed investigation of its properties can be found in~\cite[Section~13]{markov_cats}.
 
 \begin{definition}
+	\label{defnasequal}
 	Given morphisms $p : A \to X$ and $f,g : X \to Y$ in a Markov category, we say that $f$ and $g$ are \emph{$p$-a.s.~equal} if
@@
 
+We finally introduce a straightforward generalization of~\cite[Defnition~12.12]{markov_cats} from binary conditional independence to $n$-ary conditional independence.
+
+\begin{definition}
+	Given a morphism $p : A \to X_1 \otimes \ldots \otimes X_n$ in a Markov category, we say that $p$ \emph{displays the conditional independence} $X_1 \perp \ldots X_n \mid\mid A$ if the equation
+	\[
+		\tikzfig{cond_ind}
+	\]
+	holds.
+\end{definition}
+
+If $\bigotimes_{j \in F} X_j$ is a finite product without any particular order on the factors\footnote{See e.g.~\cite[Proposition~II.1.5]{DMOS} for how to make sense of tensor products in symmetric monoidal categories without a prescribed order of the factors.}, then we also write $\perp_{j \in F} X_j \mid\mid A$ to denote the corresponding conditional independence for given $p : A \to \bigotimes_{j \in F} X_j$.
+
 \section{Infinite tensor products in semicartesian monoidal categories}
@@
 In the setting of Markov categories, this means that we need to consider morphisms whose codomain is an ``infinite tensor product'' in a suitable sense.
-We start in this section by considering infinite tensor products in semicartesian symmetric monoidal categories.
+In this section, we start by considering infinite tensor products in semicartesian symmetric monoidal categories.
 
@@
 For any finite subset $F \subseteq J$, we also write $X_F := \bigotimes_{i \in F} X_i$ for simplicity of notation.
-By Kolmogorov's extension theorem, the joint distribution of infinitely many random variables is uniquely determined by the family of distributions of all finite subsets of these variables.
-This motivates our general definition of the infinite tensor product: if $F \subseteq F' \subseteq J$ are two finite subsets, then the fact that $\cC$ is semicartesian monoidal gives us \emph{marginalization morphisms}
+In the spirit of Kolmogorov's extension theorem, we believe that a good definition of joint distribution of infinitely many random variables will be such that such a joint distribution is uniquely determined by the family of its finite marginals.
+This motivates our general definition of the infinite tensor product, which we now introduce.
+If $F \subseteq F' \subseteq J$ are two finite subsets, then the fact that $\cC$ is semicartesian monoidal gives us \emph{marginalization morphisms}
 \[
@@
 	\label{semicartesian_infproduct}
-	Let $(X_i)_{i \in J}$ be a family of objects in $\cC$. Then the \emph{infinite tensor product}
+	Let $(X_j)_{j \in J}$ be a family of objects in $\cC$. An \emph{infinite tensor product}
 	\[
-		X_J \: := \: \bigotimes_{i \in J} X_i
+		X_J \: := \: \bigotimes_{j \in J} X_j
 	\]
-	is the limit of the diagram $F \mapsto X_F$, indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists.
+	is the limit of the diagram $F \mapsto X_F$, indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists and is preserved by the functor $- \otimes Y$ for every object $Y \in \cC$.
 \end{definition}
 
-We will refer to the structure maps $\pi_F : X_J \to X_F$ as \emph{finite marginalizations}. % We also write $\pi_j$ as shorthand for $\pi_{\{j\}}$.
+We will refer to the structure maps $\pi_F : X_J \to X_F$ as \emph{finite marginalizations}. The extra preservation condition will be motivated in \Cref{preserve}.
 
 \begin{remark}
-	If $J$ is finite, then the infinite tensor product exists and coincides with the standard tensor product $\bigotimes_{i \in J} X_i$.
+	If $J$ is finite, then the infinite tensor product exists and coincides with the tensor product $X_J = \bigotimes_{i \in J} X_i$ specified by the monoidal structure.
 In a general Markov category, the relevant cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
+\end{remark}
+
+\begin{remark}
+	\label{preserve}
+	It is natural to require different infinite tensor products to interact well with another.
+If $X_J$ is an infinite tensor product of a family $(X_i)_{i \in J}$ and we are given an additional object $X_\ast$ for $\ast \not \in J$, then one will want the canonical comparison morphism
+	\begin{equation}
+		\label{comparison}
+		X_J \otimes X_\ast \longrightarrow X_{J \,\sqcup\, \{\ast\}}
+	\end{equation}
+	to be an isomorphism, where $X_{J \,\sqcup\, \{\ast\}}$ is the infinite tensor product of the original family with $X_\ast$ thrown in.
+
+	If we do not yet assume that $X_{J \,\sqcup\, \{\ast\}}$ exists, then we can exhibit $X_J \otimes X_\ast$ as the relevant cofiltered limit as follows.
+The object $X_J \otimes X_\ast$ can be equipped finite marginalization morphisms with respect to $F \subseteq J \sqcup \{\ast\}$ given by
+	\[
+		\pi_{F \setminus \{\ast\}} \otimes \id \: : \: X_J \otimes X_\ast \longrightarrow X_{F \setminus \{\ast\}} \otimes X_\ast
+	\]
+	for $\ast \in F$, and just
+	\[
+		\pi_F \otimes \discard{X_\ast} : X_J \otimes X_\ast \longrightarrow X_F 
+	\]
+	in case $\ast \not \in F$.
+It is straightforward to check that these morphisms equip $X_J \otimes X_\ast$ with the right universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
+It is also easy to see that this new cofiltered limit is again preserved by every functor $- \otimes Y$, based on the assumption that, based on the assumption that the defining cofiltered limit of the original infinite tensor product is preserved by $- \otimes (X_\ast \otimes Y)$ as well.
+
+	In other words, the preservation condition in this definition amounts to the requirement that the canonical comparison morphism
+	must be an isomorphism, as one would expect intuitively from a notion of infinite tensor product. 
 \end{remark}
@@
 	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
-Thus in the case where our Markov category is $\CRing_+\op$, we recover the usual folklore definition of an infinite tensor product of rings $\bigotimes_{i \in J} R_i$ in terms of formal sums of elementary tensors, where an elementary tensor is a family of elements $(r_i)_{i \in J}$ such that all but finitely many are equal to the respective unit.
-Note that we do not yet consider the multiplication on $\bigotimes_{i \in J} R_i$, since \Cref{semicartesian_infproduct} is not yet concerned with the comonoid structures on the objects.
+Thus in the case where our Markov category is $\CRing_+\op$, we recover the usual folklore definition of an infinite tensor product of rings $\bigotimes_{j \in J} R_j$ in terms of formal sums of elementary tensors, where an elementary tensor is a family of elements $(r_j)_{j \in J}$ such that all but finitely many are equal to the respective unit.
+The necessary preservation condition is easily seen to hold.
+Note that we do not yet consider the multiplication on $\bigotimes_{j \in J} R_j$, since \Cref{semicartesian_infproduct} is not yet concerned with the comonoid structures on the objects.
 We will get to this in the next section.
 
-	Intuitively, our definition matches up with these algebraic ones under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
+	Intuitively, our definition matches up with the known algebraic ones under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
 \end{example}
@@
 	In those semicartesian monoidal categories $\cC$ that are of interest to us, morphisms $I \to X$ play the role of \emph{probability measures} on $X$.
-Thus applying the universal property with respect to maps out of $I$ amounts to requiring the \emph{Kolmogorov extension theorem} to hold in $\cC$: probability measures on an infinite product $X_J$ are in bijection with consistent families of probability measures on the finite products $X_F$ for $F \subseteq J$.
+Thus applying the defining universal property of an infinite tensor product with respect to maps out of $I$ implements the \emph{Kolmogorov extension theorem} in $\cC$: probability measures on an infinite product $X_J$ are in bijection with consistent families of probability measures on the finite products $X_F$ for $F \subseteq J$.
 \end{remark}
@@
 	However, the situation improves for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem holds~\cite[Theorem~14.35]{klenke}.
-In other words, if $\left( (X_i, \Sigma_i) \right)_{i \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{i \in \bN} X_i$ carrying the product $\sigma$-algebra $\Sigma_\bN$ satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
-In the following, we show that this implies the universal property in general.
+In other words, if $\left( (X_j, \Sigma_j) \right)_{j \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{j \in \bN} X_j$ carrying the product $\sigma$-algebra $\Sigma_\bN$ satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
+We now show that this implies the universal property in general.
 
@@
 
+	Since the resulting comparison morphism \Cref{comparison} is an isomorphism by construction---both sides are given by the corresponding products of measurable spaces---it follows that the required preservation condition of infinite tensor products holds as well.
+
 	In conclusion, $\BorelStoch$ indeed has countable tensor products.
-It is plausible that there is is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
-However, we have so far not been able to find a suitable condition on Markov kernels which would be closed under composition, due to problems of perfect measures under mixtures~\cite{ramachandran}.
+It is plausible that there is is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there also is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
+However, we have so far not been able to find a suitable condition on Markov kernels which would guarantee closure under composition, due to problems with perfect measures not being stable under mixtures~\cite{ramachandran}.
 \end{example}
@@
 	\label{infprods_finstoch}
-	Infinite tensor products never exist in $\FinStoch$, in the following sense: if the family $(X_i)$ is such that no $X_i$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_i X_i$ does not exist.
+	Infinite tensor products never exist in $\FinStoch$, in the following sense: if the family $(X_j)_{j \in J}$ is such that no $X_j$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_j X_j$ does not exist.
 One way to see this is to use the fact that the hom-sets of $\FinStoch$ are convex sets in the space of matrices, and that composition distributes over these convex combinations, making $\FinStoch$ into a category enriched in convex sets.
 Since these hom-sets are finite-dimensional, for every $Y$ and $Z$ there is $n \in \bN$ such that among every $n$ morphism $Y \to Z$, one of them can be written as a convex combination of the others.
-Now suppose that the product $\bigotimes_i X_i$ existed.
-Then by choosing varying elements of each $X_i$, we can construct uncountably many morphisms $1 \to \bigotimes_i X_i$ whose marginalizations $1 \to X_F$ are all deterministic.
+Now suppose that the product $\bigotimes_j X_j$ existed.
+Then by choosing varying elements of each $X_j$, we can construct uncountably many morphisms $1 \to \bigotimes_j X_j$ whose marginalizations $1 \to X_F$ are all deterministic.
 Per the above, one of these hypothetical morphisms can be written as a convex combination of finitely many others.
@@
 
-It is natural to require different infinite tensor products to interact well with another.
-If $X_J$ is an infinite tensor product of a family $(X_i)_{i \in J}$ and we are given an additional object $X_\ast$ for $\ast \not \in J$, then one will want $X_J \otimes X_\ast$ to be the infinite tensor product $X_{J \sqcup \{\ast\}}$ of the original family together with $X_\ast$, with finite marginalization morphisms given by
-\[
-		\pi_{F \setminus \{\ast\}} \otimes \id \: : \: X_J \otimes X_\ast \longrightarrow X_{F \setminus \{\ast\}} \otimes X_\ast
-\]
-for $\ast \in F$, and simply
-\[
-		\pi_F \otimes \discard{X_\ast} : X_J \otimes X_\ast \longrightarrow X_F 
-\]
-in case $\ast \not \in F$.
-It is straightforward to check that these morphisms exhibit $X_J \otimes X_\ast$ as the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
-This motivates the following definition.
-
-\begin{definition}
-	\label{has_infprods}
-	Let $\cC$ be a semicartesian symmetric monoidal category.
-We say that $\cC$ \emph{has infinite tensor products} if for every family of objects $(X_i)_{i \in J}$ with $|J| < \kappa$, the infinite tensor product $X_J$ exists, and its defining cofiltered limit is preserved by every functor $Y \otimes -$.
-
-	For $\kappa$ a regular cardinal, we say that $\cC$ \emph{has tensor products of size $<\kappa$} if these conditions hold as soon as $|J| < \kappa$.
-For $\kappa = \aleph_1$, we also simply say that $\cC$ \emph{has countable tensor products}.
-\end{definition}
-
-\todo[inline]{We could also make the preservation condition part of the definition of infinite tensor product. Thoughts?}
-
-As per the above, the preservation condition in this definition amounts to the requirement that the canonical comparison morphism
-\[
-	X_J \otimes X_\ast \longrightarrow X_{J \sqcup \{\ast\}}
-\]
-must be an isomorphism, as one would expect intuitively from a notion of infinite tensor product.
-The explicit constructions of \Cref{infprods_cring,infprods_stoch} show that $\CRing_+\op$ has infinite tensor products and that $\BorelStoch$ has countable tensor products, respectively.
-
 \begin{lemma}
 	\label{two_infproducts}
-	Suppose that $\cC$ has tensor products of size $< \kappa$.
-Let $J = J_1 \sqcup J_2$ be a disjoint union with $|J| < \kappa$, and $(X_i)_{i \in J}$ a family of objects in $\cC$.
-Suppose that the infinite tensor products $X_{J_1}$ and $X_{J_2}$ exist.
-Then the object
+	Let $J = J_1 \,\sqcup\, J_2$ be a disjoint union and $(X_i)_{i \in J}$ a family of objects in $\cC$. Suppose that the infinite tensor products $X_{J_1}$ and $X_{J_2}$ exist. Then the object
 	\[
@@
 		\begin{tikzcd}[column sep=huge]
-			\rho_F \: : \: X_{J_1} \otimes X_{J_2} \ar{r}{\pi_{F\cap J_1} \otimes \pi_{F\cap J_2}} & X_{F \cap J_1} \otimes X_{F \cap J_2}.
+			\rho_F \: : \: X_{J_1} \otimes X_{J_2} \ar{r}{\pi_{F\cap J_1} \,\otimes\, \pi_{F\cap J_2}} & X_{F \cap J_1} \otimes X_{F \cap J_2}.
 		\end{tikzcd}
@@
 	exhibit $X_{J_1} \otimes X_{J_2}$ as the cofiltered limit of the $X_{F_1} \otimes X_{J_2}$.
-The claim follows as a limit of limits is a limit, and it is easy to see that the diagram shapes much up: the poset of finite subsets of $J_1 \sqcup J_2$ is the product of the posets of finite subsets of $J_1$ and $J_2$.
+The claimed universal property follows since a limit of limits is a limit, and it is easy to see that the diagram shapes match up: the poset of finite subsets of $J_1 \sqcup J_2$ is the product of the posets of finite subsets of $J_1$ and $J_2$.
+The preservation property with respect to applying a tensoring functor $- \otimes Y$ carries along.
 \end{proof}
 
-More generally, we may consider infinite tensor products of infinite tensor products, $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$, where now $(J_k)_{k \in K}$ is a family of sets and $(X_{k,i})$ a doubly indexed family of objects.
-One may think that this doubly infinite tensor product should be isomorphic to the single-step infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
-And indeed, if for every finite $F \subseteq \prod_{k \in K} J_k$ we choose any finite $G \subseteq K$ such that $(k,i) \in F$ implies $k \in G$, then we have morphisms
+More generally, we may consider infinite tensor products of infinite tensor products, $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$, where now $(J_k)_{k \in K}$ is a family of sets and $(X_{k,j})$ a doubly indexed family of objects.
+One may think that this doubly infinite tensor product should be isomorphic to the single-step infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
+And indeed, if for every finite $F \subseteq \prod_{k \in K} J_k$ we choose any finite $G \subseteq K$ such that $(k,j) \in F$ implies $k \in G$, then we have morphisms
 \begin{equation}
 	\label{double_infproduct}
-	\begin{tikzcd}[column sep=huge]
-		\rho_F \: : \: \bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i} \ar{r}{\pi_G} & \bigotimes_{k \in G} \bigotimes_{i \in J_k} X_{k,i} \ar{r}{\bigotimes_{k \in G} \pi_{F \cap J_k}} & \bigotimes_{k \in G, \: i \in F \cap J_k} X_{k,i}
+	\begin{tikzcd}[column sep=1cm]
+		\rho_F \; : \; \bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j} \ar{r}{\pi_G} & \bigotimes_{k \in G} \bigotimes_{j \in J_k} X_{k,j} \ar{rr}{\bigotimes_{k \in G} \pi_{F \cap J_k}} & & \bigotimes_{k \in G, \: j \in F \cap J_k} X_{k,j}
 	\end{tikzcd}
 \end{equation}
-where the object on the right can also be written as $\bigotimes_{(k,i) \in F} X_{k,i}$.
+where the object on the right can also be written as $\bigotimes_{(k,j) \in F} X_{k,j}$.
 It is straightforward to see that this $\rho_F$ does not depend on the particular choice of $G$.
-We now show that these $\rho_F$'s are finite marginalization morphisms which make the doubly infinite tensor product $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$ into the single infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
+We now show that these $\rho_F$'s are finite marginalization morphisms which make the doubly infinite tensor product $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ into the single infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
 
 \begin{lemma}
-	Suppose that $\cC$ has tensor products of size $< \kappa$, and let $(J_k)_{k \in K}$ be a family of sets with $|K| < \kappa$ and $|J_k| < \kappa$, and $(X_{k,i})_{i \in J_k, k \in K}$ a doubly indexed family of objects.
-Then the above $\rho_F$ exhibit the infinite tensor product of infinite tensor products $\bigotimes_{k \in K} \bigotimes_{i \in J_k} X_{k,i}$ as the infinite tensor product $\bigotimes_{k \in K, \: i \in J_k} X_{k,i}$.
+	Suppose that $(J_k)_{k \in K}$ is a family of sets and $(X_{k,j})_{j \in J_k, k \in K}$ a doubly indexed family of objects.
+If all of the infinite tensor products $\bigotimes_{j \in J_k} X_{j,k}$ and $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ exist, then the above morphisms $\rho_F$ exhibit $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ as the infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
 \end{lemma}
 \begin{proof}
-	By repeated application of \Cref{two_infproducts}, the second half of~\Cref{double_infproduct} exhibits $\bigotimes_{k \in G} \bigotimes_{i \in J_k} X_{k,i}$ as the infinite product of the $X_{k,i}$ for $k \in G$ and $i \in J_k$.
-The claim then follows from a straightforward diagram chase.
+	By repeated application of \Cref{two_infproducts}, the second half of~\Cref{double_infproduct} exhibits $\bigotimes_{k \in G} \bigotimes_{j \in J_k} X_{k,j}$ as the infinite tensor product of the $X_{k,j}$ for $k \in G$ and $j \in J_k$.
+The relevant universal property as well as its preservation by $- \otimes Y$ then follow from a straightforward diagram chase.
 \end{proof}
@@
     \label{defn_kolmogorov_ext}
-    Let $\cC$ be a Markov category and $(X_i)_{i \in J}$ a family of objects.
-We say that an infinite product $X_J = \bigotimes_{i \in J} X_i$ is a \emph{Kolmogorov product} if the finite marginalization morphisms $\pi_F : X_J \to X_F$ are deterministic, and the universal property is preserved by every functor $Y \otimes -$.
-
-    We say that $\cC$ \emph{has Kolmogorov products} if every family of objects has a Kolmogorov product.
-For $\kappa$ a regular cardinal, we say that $\cC$ has \emph{Kolmogorov products of size $<\kappa$} if families of size $<\kappa$ have a Kolmogorov product.
-For $\kappa = \aleph_1$, we say that $\cC$ has \emph{countable Kolmogorov products}.
+    Let $\cC$ be a Markov category and $(X_j)_{j \in J}$ a family of objects.
+We say that an infinite tensor product $X_J = \bigotimes_{j \in J} X_j$ is a \emph{Kolmogorov product} if the finite marginalization morphisms $\pi_F : X_J \to X_F$ are deterministic.
 \end{definition}
@@
 In $\BorelStoch$, the infinite tensor products constructed in \Cref{infprods_stoch} are Kolmogorov products.
-In $\CRing_+\op$, the infinite tensor products from \Cref{infprods_cring} are Kolmogorov products as well as long as one equips $\bigotimes_i R_i$ with the tensor product ring structure, since this one is the only one which makes the canonical inclusions $R_i \to \bigotimes_i R_i$ into ring homomorphisms.
-These examples illustrate an important point: in some Markov categories, such as $\CRing_+\op$, not all isomorphisms are deterministic, and there may even be isomorphic objects which have no deterministic isomorphism~\cite[Remark~10.9]{markov_cats}.
-In these categories, whether a given object is an infinite tensor product or not generally depends on the specific choice of that object.
+In $\CRing_+\op$, the infinite tensor products from \Cref{infprods_cring} are Kolmogorov products as well as long as one equips $\bigotimes_j R_j$ with the tensor product ring structure, since this one is the only one which makes the canonical inclusions $R_j \to \bigotimes_j R_j$ into ring homomorphisms.
+These examples illustrate the following important point.
+In some Markov categories, such as $\CRing_+\op$, not all isomorphisms are deterministic, and there may even be isomorphic objects which have no deterministic isomorphism~\cite[Remark~10.9]{markov_cats}.
+In these categories, whether a given infinite tensor product is a Kolmogorov product or not generally depends on the specific choice of that object.
 In particular, there may be infinite tensor products which are not Kolmogorov products.
-For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_i R_i$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
+For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_j R_j$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
 
@@
 	If $\cC$ is positive in the sense of~\cite[Definition~11.22]{markov_cats}, then a morphism $A \to B \otimes C$ is deterministic if and only if both of its marginals are $A \to B$ and $A \to C$ are deterministic~\cite[Corollary~12.15]{markov_cats}.
-In this case, it follows that the finite marginalizations $\pi_F$ are deterministic if and only if all the single-factor marginalizations $\pi_{\{i\}} : X_J \to X_i$ are.
-Thus for an infinite tensor product to be a Kolmogorov product, it is then enough to verify that the $\pi_{\{i\}}$ are deterministic.
+In this case, it follows that the finite marginalizations $\pi_F$ are deterministic if and only if all the single-factor marginalizations $\pi_{\{j\}} : X_J \to X_j$ are.
+Thus for an infinite tensor product to be a Kolmogorov product, it is then enough to verify that the $\pi_{\{j\}}$ are deterministic.
 \end{remark}
@@
 \begin{proposition}
-	Every Kolmogorov product is a categorical product in $\cC_\detc$.	
+	Every Kolmogorov product is a categorical product in the cartesian monoidal subcategory of deterministic morphisms $\cC_\detc$.
 	\label{kolmprod_catdet}
@@
 \begin{proof}
-	For $(X_i)_{i \in J}$ a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$, we first show that if we have a compatible family of deterministic morphisms $g_F : A \to X_F$, then also the induced $g_J : A \to X_J$ is deterministic.
+	For $(X_j)_{j \in J}$ a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$, we first show that if we have a compatible family of deterministic morphisms $g_F : A \to X_F$, then also the induced $g_J : A \to X_J$ is deterministic.
 Drawing the Kolmogorov product $X_J$ as a double wire, we need to prove the determinism equation
@@
 	\]
-	By \Cref{two_infproducts}, the codomain object $X_J \otimes X_J$ is itself an infinite tensor product, and it is therefore enough to prove
+	By \Cref{two_infproducts}, the codomain object $X_J \otimes X_J$ is itself an infinite tensor product, and it is therefore enough to prove that for every finite $F \subseteq J$,
 	\[
@@
     	\[
-		\lim_{F \subseteq J \text{ finite}} \: \prod_{i \in F} X_i \: \cong \: \prod_{i \in J} X_i,
+		\lim_{F \subseteq J \text{ finite}} \: \prod_{j \in F} X_j \: \cong \: \prod_{j \in J} X_j,
 	\]
-	and this is what was to be shown.
+	and the claim follows.
 \end{proof}
 
-In particular, this proves that the comonoid structure on a Kolmogorov product is determined uniquely: $\cop{\bigotimes_i X_i}$ has to be the diagonal map in $\cC_{\rm det}$, and this condition determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
+In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_j X_j}$ has to be the diagonal morphism in $\cC_\detc$, and this condition determines $\bigotimes_j X_j$ up to \emph{deterministic} isomorphism.
 
@@
 
-The notion of Kolmogorov product describes a notion of infinite collection of random variables where all dependence must be encoded in the finite subsets of the variables.
-We capture this in the following definition.
+The concept of Kolmogorov product describes a notion of infinite collection of random variables whose joint distribution is encoded in its finite marginals.
+It is natural to postulate the same for when such an infinite collection is considered to be independent.
 
 \begin{definition}
-	We say that a morphism $p_J : A \to \bigotimes_{i \in J} X_i$ \emph{displays the conditional independence} $\perp_{i \in J}  X_i \mid\mid A$ if each finite marginalization $p_F : A \to \bigotimes_{i \in F}X_i$ displays the conditional independence $\perp_{i \in F} X_i \mid\mid A$.
+	We say that a morphism $p : A \to \bigotimes_{j \in J} X_j$ \emph{displays the conditional independence} $\perp_{j \in J}  X_j \mid\mid A$ if each finite marginalization $p_F : A \to \bigotimes_{j \in F} X_j$ displays the conditional independence $\perp_{j \in F} X_j \mid\mid A$.
 \end{definition}
@@
 
-Throughout this section, $(X_i)_{i \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
+Throughout this section, $(X_j)_{j \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
 
 \begin{lemma}[The infinite independence lemma]
-	Suppose $p: A \to X_J$ displays the conditional independence $\perp_i X_i \mid\mid A$.
-	Then for every $i \in J$, it also displays the independence $X_j \perp X_{J \setminus \{i\}} \mid\mid A$.
+	Suppose $p: A \to X_J$ displays the conditional independence $\perp_j X_j \mid\mid A$.
+	Then for every $j \in J$, it also displays the independence $X_j \perp X_{J \setminus \{j\}} \mid\mid A$.
 \end{lemma}
@@
 	\]
-	As the codomain is exactly the Kolmogorov product $X_J$, it is enough to prove this equation upon composing the second output with the finite marginalizations $\pi_F : X_{J\setminus\{i\}} \to X_F$.
+	As the codomain is exactly the Kolmogorov product $X_J$, it is enough to prove this equation upon composing the second output with the finite marginalizations $\pi_F : X_{J\setminus\{j\}} \to X_F$.
 But this is a consequence of the assumption.
@@
 This result can be thought of as a partial converse to the condition which characterizes positivity of a Markov category~\cite[Definition~11.22]{markov_cats}.
+Here and in the following, our notation ``$s$'' indicates that we think of this morphism as a statistic~\cite[Definition~14.2]{markov_cats}.
 \begin{proof}
@@
 
-\begin{theorem}
+\begin{theorem}[Abstract Kolmogorov zero--one law]
     \label{thm:kolmog}
-    Suppose that $\cC$ is a Markov category, and that $(X_i)_{i \in J}$ is a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
-
+    Suppose that $\cC$ is a Markov category, and that $(X_j)_{j \in J}$ is a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
 If morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ are such that for every finite $F \subseteq J$, the joint
@@
 \begin{proof}
-	Assuming $\ast \not \in J$, let us write $X_\ast := T$, so that $X_J \otimes X_\ast$ is the Kolmogorov product of the family $(X_i)_{i \in J \,\sqcup\,\{\ast\}}$.
+	Assuming $\ast \not \in J$, let us write $X_\ast := T$, so that $X_J \otimes X_\ast$ is the Kolmogorov product of the family $(X_j)_{j \in J \,\sqcup\,\{\ast\}}$.
 It is clear from the definitions and the assumption that the morphism
@@
     \]
-    displays the conditional independence $\perp_{i \in J\,\sqcup\,\{\ast\}} X_i \mid\mid A$.
+    displays the conditional independence $\perp_{j \in J\,\sqcup\,\{\ast\}} X_j \mid\mid A$.
     By the infinite independence lemma, this means that it also displays the conditional independence $X_\ast \perp X_J \mid\mid A$.
-    Now the determinism lemma implies exactly what we want, that the composite $sp : A \to T$ is deterministic.
+    Now the determinism lemma implies exactly what we want, namely that the composite $sp : A \to T$ is deterministic.
 \end{proof}
@@
 It applies to Kolmogorov products where all factors are copies of the same object.
-So for an object $X$ and the constant family $(X)_{i \in J}$, let us say that the corresponding Kolmogorov product $X_J$ is the \emph{Kolmogorov power} of $X$ by $J$.
+So for an object $X$ and the constant family $(X)_{j \in J}$, let us say that the corresponding Kolmogorov product $X_J$ is the \emph{Kolmogorov power} of $X$ by $J$.
 
@@
 Suppose that $\alpha : J \to J$ is a finite permutation or more generally any injection.
-Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_J$ in the obvious way: the morphisms
+Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_J$ by applying the universal property of $X_J$ to the compatible family of composite morphisms
 \[
 	\begin{tikzcd}
-		X_J \ar{r}{\pi_F} & X_F \ar{r}{\cong} & X_{\alpha(F)}
+		X_J \ar{r}{\pi_F} & X_F \ar{r}{\cong} & X_{\alpha(F)},
 	\end{tikzcd}
@@
 
-\begin{theorem}[Hewitt--Savage for Markov categories]
+\begin{theorem}[Abstract Hewitt--Savage zero--one law]
     	\label{thm:hewsav}
-	Suppose that $\cC$ is a causal Markov category and that $X_J$ is a Kolmogorov power of an object $X \in \cC$ with respect to an infinite set $J$.
-
+	Suppose that $\cC$ is a causal Markov category (\Cref{causal_defn}). Let $X_J$ be a Kolmogorov power of an object $X \in \cC$ with respect to an infinite set $J$.
     	Suppose that morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ satisfy the following:
     	\begin{enumerate}
-		\item $p$ displays the conditional independence $\perp_i X_i \mid\mid A$.
-		\item For every finite permutation $\alpha : J \to J$ we have $\hat{\alpha} p = p$ and $s \hat{\alpha} = s$. 
+		\item $p$ displays the conditional independence $\perp_j X_j \mid\mid A$.
+		\item For every finite permutation $\alpha : J \to J$, we have $\hat{\alpha} p = p$ and $s \hat{\alpha} = s$. 
     	\end{enumerate}
@@
 	\label{aseqlemma}
-	Let $\cC$ be a causal Markov category (\Cref{causal_defn}). Let $p : A \to X$ and $f,g: X \to Y$ be morphisms with $f$ deterministic and such that
+	Let $\cC$ be a causal Markov category. Let $p : A \to X$ and $f,g: X \to Y$ be morphisms in $\cC$ with $f$ deterministic and such that
 	\[
@@
 	\]
-	Then $f =_{p\as} g$.
+	Then $f =_{p\as} g$ (\Cref{defnasequal}).
 \end{lemma}
@@
 	We next show that this equation still holds if $\alpha$ is merely an injection.
-By the universal property of $X_J \otimes T$ as the infinite tensor product of the family $(X_i)_{i \in J}$ together with $T$, it is enough to prove \Cref{strong_invariance} upon marginalization by $\pi_F \otimes \id$ for all finite $F \subseteq J$.
+By the universal property of $X_J \otimes T$ as the infinite tensor product of the family $(X_j)_{j \in J}$ together with $T$, it is enough to prove \Cref{strong_invariance} upon marginalization by $\pi_F \otimes \id$ for all finite $F \subseteq J$.
 Since we can find a finite permutation $\alpha' : J \to J$ such that $\alpha'|_F = \alpha|_F$, the claim follows from the finite permutation case.
@@
 \begin{corollary}[Kolmogorov zero--one law]
-	Suppose $\Omega$ is a standard Borel space with a probability measure $P$ and that $\left(f_i: \Omega \to X_i\right)_{i \in \bN}$ is a sequence of independent random variables taking values in standard Borel spaces $X_i$.
-Suppose that $T \subseteq \Omega$ is in the coarsest $\sigma$-algebra which makes the $f_i$ measurable, and independent of any finite subset of the $f_i$.
-    Then $P(T)$ is $0$ or $1$.
+	Suppose $\Omega$ is a standard Borel space with a probability measure $P$ and that $\left(f_j: \Omega \to X_j\right)_{j \in \bN}$ is a sequence of independent random variables taking values in standard Borel spaces $X_j$.
+Suppose that $T \subseteq \Omega$ is in the coarsest $\sigma$-algebra which makes the $f_j$ measurable, and independent of any finite subset of the $f_j$.
+Then $P(T) \in \{0,1\}$.
 \end{corollary}
@@
 
+\todo[inline]{Describe Kleisli cat of the hyperspace monad, or directly whatever precise category of relations the following takes place in}
+
 \begin{corollary}
-    Let $\{X_i\}_{i \in J}$ be a family of topological spaces, $Y$ a Hausdorff space, and let $f: \prod_i X_i \to Y$ be a continuous function
+    Let $(X_j)_{j \in J}$ be a family of topological spaces, $Y$ a Hausdorff space, and let $f: \prod_j X_j \to Y$ be a continuous function
     which is independent of any finite prefix of the input.
@@
 \begin{corollary}
-    Let $X, Y$ be topological spaces, $Y$ Hausdorff, and let $f: \prod_{i\in J} X \to Y$ be a continuous function which is independent of any finite permutation of the input.
+	Let $X$ be a topological space, $Y$ a Hausdorff space, $J$ an infinite set, and let $f: \prod_{j\in J} X \to Y$ be a continuous function which is invariant under any finite permutation of the inputs.
     Then $f$ is constant.
 \end{corollary}
-\begin{proof}
-    The theorems follow from \cref{thm:kolmog} and \cref{thm:hewsav}, applied to the Kleisli category $Kl(H)$ of the hyperspace monad,
-    using the maps $* \to X_i$ and $* \to X$ given by the closed subsets $X_i \subseteq X_i, X \subset X$.
+\begin{proof}[Proof of both]
+	These results follow from \Cref{thm:kolmog,thm:hewsav}, applied to the Kleisli category $\mathrm{Kl}(H)$ of the hyperspace monad $H$,
+	using the morphisms $p : I \to X_J$ corresponding to the trivial closed subset $X_J \subseteq X_J$.
     The conclusion is that the closure of the image, call it $A$, has the following property: $\overline{\{(a,a) \mid a \in A\}} = A \times A$ as subsets of $Y \times Y$.

### 2019-10-28 categorical-zero-one.tex

@@
 	in case $\ast \not \in F$.
-It is straightforward to check that these morphisms equip $X_J \otimes X_\ast$ with the right universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
-It is also easy to see that this new cofiltered limit is again preserved by every functor $- \otimes Y$, based on the assumption that, based on the assumption that the defining cofiltered limit of the original infinite tensor product is preserved by $- \otimes (X_\ast \otimes Y)$ as well.
+It is straightforward to check that these morphisms equip $X_J \otimes X_\ast$ with the right universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
+It is also easy to see that this new cofiltered limit is again preserved by every functor $- \otimes Y$, based on the assumption that the defining cofiltered limit of the original infinite tensor product is preserved by $- \otimes (X_\ast \otimes Y)$ as well.
 
@@
 \begin{example}
+
 	\label{infprods_stoch}
@@
 
-\todo[inline]{Add an example where $\cC_{\rm det}$ has infinite products, but $\cC$ lacks infinite tensor products? Like sets and multivalued functions?}
+\begin{example}
+    \label{setmulti}
+    Let $\SetMulti$ be the category with objects ordinary sets, maps $f: X \to Y$ given by functions (i.e maps in the ordinary category of sets) $f: X \to \cP(Y)\setminus \emptyset$, and composition given by
+    \[f\circ g(x) = \bigcup_{y \in g(x)} f(y)\]
+    for $g: X \to Y, f: Y \to Z$.
+    We think of the morphisms in $\SetMulti$ as \emph{multivalued functions}.
+    See also \cite[Example~2.6]{markov_cats}.
+    The Cartesian product of sets gives it a symmetric monoidal structure, if we set \[(f \tensor g)(x_1,x_2) = f(x_1) \times g(x_2) \subset Y_1 \times Y_2,\] for $f:X_1 \to Y_1, g: X_2 \to Y_2$.
+    This is a semicartesian monoidal structure, and we can give it a Markov category structure by setting
+    $\cop{X}(x) = \{(x,x)\} \subset X \times X$.
+    Then the deterministic morphisms are precisely those sending each point into a singleton set, and there is an obvious isomorphism of categories
+    $\SetMulti_\detc \cong \sf{Set}$.
+    Of course, $\sf{Set}$ actually has all infinite products, but they do not form Kolmogorov products, or even infinite tensor products in $\sf{SetMulti}$.
+    To see this, consider the family $X_n = \{0,1\}$ for $n \in \bN$.
+    A map $* \to \prod_{n\in \bN} \{0,1\} = X_\bN$ is just a subset of this infinite product.
+    Given such a subset $U$, the finite marginals $* \to X_F$ for $F \subset \bN$ are the images of $U$ under the projection map.
+    But these images do not determine $U$. For instance, consider the subset $U$ of those sequences containing at least one $1$.
+    The image in $X_F$ is all of $X_F$ (since any finite sequence of $0$s and $1$s can be extended to one containing a $1$).
+    But $U$ is not all of $X_\bN$.
 
-\todo[inline]{T: sounds good to me, can you put it in?}
+\end{example}
 
@@
 	displays the conditional independence $X \perp T \mid\mid A$, then the composite $sp: A \to T$ is deterministic.
-\end{lemma}
+\end{lemma}\cite
 This result can be thought of as a partial converse to the condition which characterizes positivity of a Markov category~\cite[Definition~11.22]{markov_cats}.

### 2019-10-29 categorical-zero-one.tex
Add hewitt-savage zero-one

@@
 Suppose that $\alpha : J \to J$ is a finite permutation or more generally any injection.
-Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_J$ by applying the universal property of $X_J$ to the compatible family of composite morphisms
+Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_{\alpha(J)}$ by applying the universal property of $X_J$ to the compatible family of composite morphisms
 \[
@@
 where the second morphism matches up the factors of the two finite products involved as prescribed by the bijection $\alpha|_F : F \stackrel{\cong}{\longrightarrow} \alpha(F)$.
-The relevant compatibility condition is straightforward to check.
-Moreover, $\hat{\alpha}$ is deterministic by \Cref{kolmprod_catdet}.
+Here we are using the fact that each finite subset of $\alpha(J)$ has the form $\alpha(F)$ for a unique finite $F \subset J$ (namely the preimage).
+The relevant compatibility condition is straightforward to check. Moreover, $\hat{\alpha}$ is deterministic by \Cref{kolmprod_catdet}.
 
@@
 Hence the assumption implies that there is measurable $S \subseteq X_J$ such that $T = f_\bN^{-1}(S)$.
-Then we apply \Cref{thm:kolmog} with $s : X_J \to \{0,1\}$ the indicator function of $S$, which is a measurable map and therefore can also be regarded as a morphism in $\BorelStoch$.
+Then we apply \Cref{thm:kolmog} with $s : X_J \to \{0,1\}$ the indicator function of $S$, which is a measurable map and therefore can also be regarded as a morphism in $\BorelStoch$, and $p = f_\bN P$.
 We therefore obtain that $sp : I \to \{0,1\}$ is deterministic.
@@
 
-\todo[inline]{describe the application of \Cref{thm:hewsav} to $\BorelStoch$}
+\begin{corollary}[Hewitt-savage zero--one law]
+    Suppose $\Omega$ is a standard Borel space with probability measure $P$, and let $\left(f_j: \Omega \to X\right)_{j\in \bN}$ be a sequence of independent, identically distributed random variables taking values in a standard Borel space $X$.
+    Suppose $S \subset \prod_{j \in \bN} X = X_\bN$ is measurable in the product $\sigma$-algebra, and suppose moreover that, for each finite permutation $\alpha: \bN \to \bN$, $\hat{\alpha}(S) = S$ (in other words, $S$ is invariant under finite permutations of the variables).
+    Then $P(f_\bN\inv(S)) \in \{0,1\}$ - here $f_\bN$ again denotes the induced map $\Omega \to X_\bN.$
+\end{corollary}
+\begin{proof}
+    The proof is similar to the previous proof. This time we want to apply \Cref{thm:hewsav} with $\cC = \BorelStoch$, $J = \bN$, $A = I$.
+    Again, we have $P: I \to \Omega$.
+    As before, we let $s: X_\bN \to \{0,1\}$ be the indicator function of $S$, and we let $p = f_\bN P$.
+    The i.i.d assumption on the $f_j$ implies that $\hat{\alpha}p = p$, and the assumption on $S$ implies $s\hat{\alpha} = s$ for finite permutations $\alpha$.
+    Hence we can apply \Cref{thm:hewsav}. This again implies that the map $sp: I \to \{0,1\}$ is deterministic, which, just as before, means 
+    $P(f_\bN\inv(S))$ is either $0$ or $1$.
+\end{proof}
 

### 2019-10-30 categorical-zero-one.tex
Add stuff about Kl(H)

@@
 	displays the conditional independence $X \perp T \mid\mid A$, then the composite $sp: A \to T$ is deterministic.
-\end{lemma}\cite
+\end{lemma}
 This result can be thought of as a partial converse to the condition which characterizes positivity of a Markov category~\cite[Definition~11.22]{markov_cats}.
@@
 
-By interpreting our results in other Markov categories, we obtain other nontrivial (although hardly particularly deep) statements:
+\todo[inline]{E: Not sure these examples are that great.. it seems like we do an inordinate amount of work to get the infinite tensor products, compared to the results. What do you think?}
 
-\todo[inline]{Describe Kleisli cat of the hyperspace monad, or directly whatever precise category of relations the following takes place in}
+By interpreting these results in different Markov categories, we can obtain other results.
+As a simple example, we can consider the following Markov category:
 
+\begin{definition}
+    Consider the hyperspace monad on $\Top$ defined in \cite[Definition~2.4]{hyperspace}.
+    The Kleisli category associated to this monad is denoted $\Kl(H)$.
+    Using \cite[Corollary~2.53]{hyperspace} and \cite[Proposition~3.1]{markov_cats}, this is a Markov category.
+    Concretely, this category has the following structure:
+    \begin{enumerate}
+        \item The objects are topological spaces.
+        \item A map $f: X \to Y$ consists of a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subset Y \text{ closed} \mid V \cap U \neq \emptyset\}$ for $U \subset Y$ open.
+        \item Composition is defined as in $\SetMulti$, by the closure of the union.
+        \item The monoidal product is the Cartesian product of topological spaces, and $(f \tensor g)(x_1,x_2) = f(x_1) \times g(x_2)$.
+        \item The comultiplication is defined by $\cop{X}(x) = \cl(\{(x,x)\})$
+    \end{enumerate}
+\end{definition}
+\begin{proposition}
+    $\Kl(H)$ has Kolmogorov products of any cardinality, given simply by the ordinary infinite product of topological spaces in the product topology.
+\end{proposition}
+\begin{proof}
+    First we observe that $H(\prod_{j\in J} X_j)$ is the cofiltered limit of the spaces
+    $H(\prod_{j\in F} X_j)$.
+    To see this, note that the marginalizations induce a continuous map
+    \[\alpha: H(\prod_{j\in J} X_j) \to \lim_{F \subset J} H(\prod_{j \in J} X_j)\]
+    This is an injection - given distinct closed subsets $V, W \subset \prod X_j$, and let $x \in V \setminus W$.
+    Then let $U \ni x$ be an open neighborhood of $x$ not intersecting $W$.
+    Since $U$ is open in the product topology, we can find some finite subset $F \subset J$ so that 
+    \[y = (y_j) \in U \Leftrightarrow y_j \in \pi_j(U) \text{ for $j\in F$}\]
+    Then $\pi_F(x) \in \pi_F(U)$, which is disjoint from $\pi_F(W)$. Hence $\alpha(V) \neq \alpha(W)$.
+
+    It is also a surjection - given a family $(V_F) \in \lim H(\prod_{j \in J} X_j)$, simply set
+    \[V = \{x \in \prod_{j\in J} X_j \mid  \pi_F(x) \in V_F \forall F\}\]
+    This is an intersection of closed subsets, hence closed, and it is clearly sent to $(V_F)$.
+
+    Finally, we must verify that it's open.
+    It suffices to show that it carries subbasis open sets $A_U = \{V \subset \prod X_j \text{ closed} \mid V \cap U \neq \emptyset\}$ to open subsets of the limit.
+    Again, given such a $U$, we find a finite $F$ so that
+    \[y = (y_j) \in U \Leftrightarrow y_j \in \pi_j(U) \text{ for $j\in F$}\]
+    then \[\alpha(A_U) = \pi_F\inv(\{V \subset \prod_{j \in F} X_F \text{ closed} \mid V \cap \pi_F(U) \neq \emptyset\})\]
+    and this is open in the limit.
+
+    It follows that $\prod_j X_j$ is an infinite tensor product in $\Kl(H)$ - the preservation condition is easily verified.
+    The Kolmogorov product condition is similarly immediate to verify.
+\end{proof}
 \begin{corollary}
@@
 \begin{proof}[Proof of both]
-	These results follow from \Cref{thm:kolmog,thm:hewsav}, applied to the Kleisli category $\mathrm{Kl}(H)$ of the hyperspace monad $H$,
+	These results follow from \Cref{thm:kolmog,thm:hewsav} appliedto $\Kl(H)$.
 	using the morphisms $p : I \to X_J$ corresponding to the trivial closed subset $X_J \subseteq X_J$.
-    The conclusion is that the closure of the image, call it $A$, has the following property: $\overline{\{(a,a) \mid a \in A\}} = A \times A$ as subsets of $Y \times Y$.
+    The conclusion is that the closure of the image, call it $A$, has the following property: $\cl(\{(a,a) \mid a \in A\}) = A \times A$ as subsets of $Y \times Y$.
     But since the diagonal is closed in $Y$, this clearly implies that $A$ must be a singleton.
 \end{proof}
-
-\todo[inline]{I agree with the speculation, but it's probably a bit too vague for the paper in its present state, so I've removed it}
 

### 2019-10-30 categorical-zero-one.tex
Drafted intro

@@
 
-\todo[inline]{Add some motivation and summary}
+\emph{Markov categories} are an approach to probability and statistics based on category theory, developed by the first author in \cite{markov_cats}, building on much previous work by other authors (see \Cref{background}).
+The basic idea is to axiomatize the structure and properties of ``categories of stochastic processes'' - for instance, the category $\Stoch$ where objects are measurable spaces and morphisms are Markov kernels (hence the name).
+The goal is to state and prove results from probability and statistics in this context.
+This represents a \emph{synthetic} approach to probability, in contrast with the usual measure-theoretic approach (which can be called \emph{analytic}).
+Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
+We can draw an analogy to the Euclidean approach to geometry - defining certain basic relations between the geometric objects at hand, and setting down axioms about them - with the more modern description of geometric objects as (very roughly) certain subsets of $\bR^n$.
 
 This is a treatment of the zero--one laws of Kolmogorov and of Hewitt--Savage in the setting of Markov categories.
+
+Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.
+
+The Hewitt--Savage zero--one law is similar - here the variables are supposed to be independent and indetically distributed, and the event is supposed to be invariant under finite permutations of the variables.
+Again, under these assumptions, the event has probability one or zero.
+
+To formulate these statements in the general context of Markov categories, we need a notion of infinite family of random variables.
+To this end, we define a notion of \emph{infinite tensor product}.
+Given such a tensor product, satisfying a certain condition of compatibility with the structure of the Markov category (\Cref{defn_kolmogorov_ext}), we prove abstract versions of the zero--one laws, \Cref{thm:kolmog} and \Cref{thm:hewsav}.
+
+Last, we apply our results to the case of measurable spaces and Markov kernels, deriving the zero--one laws for random variables in standard Borel spaces (this regularity assumption is needed to make the necessary infinite tensor products exist).
 
@@
 
-\section{Background on Markov categories}
+\section{Background on Markov categories}\label{background}
 

### 2019-11-01 categorical-zero-one.tex
Paolo's example: finitary complete monoids

@@
 $F$ denotes either an arbitrary finite set or more concretely a finite subset of $J$.
+
+\paragraph*{Acknowledgments.} We thank Paolo Perrone for discussions leading to \Cref{poset_case}.
 
@@
 \begin{lemma}
+	\label{infprod_operadic}
 	Suppose that $(J_k)_{k \in K}$ is a family of sets and $(X_{k,j})_{j \in J_k, k \in K}$ a doubly indexed family of objects.
@@
 \end{proof}
+
+\begin{example}[Perrone]
+	\label{poset_case}
+	Suppose that $\cC$ is a partially ordered set, considered as a category with $X \geq Y$ if and only if the morphism $X \to Y$ exists.\footnote{This direction of the ordering is opposite to the usual convention, but necessary for the following to work on the nose.} Then the monoidal structure makes $\cC$ into an ordered commutative monoid, which we write additively, where the functoriality of the monoidal structure amounts to the assumption that addition is monotone,
+	\[
+		X \geq Y \quad\: \Longrightarrow \quad\: X + Z \geq Y + Z.
+	\]
+	Furthermore, the monoidal structure is semicartesian if and only if $X \geq 0$ for every $X$.
+One can then apply \Cref{infprod_operadic} to show that $\cC$ has infinite tensor products if and only if $\cC$ is a \emph{finitary complete monoid} in the sense of Goldstern and Karner~\cite[Section~2.2]{karner}.
+\end{example}
 

### 2019-11-02 categorical-zero-one.tex
Minor fixes and some more comments

@@
 Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
-We can draw an analogy to the Euclidean approach to geometry - defining certain basic relations between the geometric objects at hand, and setting down axioms about them - with the more modern description of geometric objects as (very roughly) certain subsets of $\bR^n$.
+We can draw an analogy to the Euclidean approach to geometry - defining certain basic relations between the geometric objects at hand, and setting down axioms about them - with the more modern description of geometric objects as (very roughly) certain subsets of $\bR^n$.\improve{The explanation of this analogy is a bit wonky}
 
@@
 
-Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.
+Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.\improve{add references for the Kolmogorov and Hewitt--Savage 01 laws}
 
@@
 
-A symmetric monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal. Equivalently, it is a monoidal category equipped with morphisms
+A symmetric monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal.
+Equivalently\todo{Should there be a reference to this equivalence?}, it is a monoidal category equipped with morphisms
 \[
@@
 In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness.
-In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive unital maps $S \to R$, i.e.~the ring homomorphisms.
+In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive\todo{should this be ``multiplicative''?}  unital maps $S \to R$, i.e.~the ring homomorphisms.
 Thus the subcategory of deterministic morphisms is exactly the opposite of the usual category of commutative rings.
@@
 \begin{definition}
-	Given a morphism $p : A \to X_1 \otimes \ldots \otimes X_n$ in a Markov category, we say that $p$ \emph{displays the conditional independence} $X_1 \perp \ldots X_n \mid\mid A$ if the equation
+	Given a morphism $p : A \to X_1 \otimes \ldots \otimes X_n$ in a Markov category, we say that $p$ \emph{displays the conditional independence} $X_1 \perp \ldots \perp X_n \mid\mid A$ if the equation
 	\[
@@
 
-In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_j X_j}$ has to be the diagonal morphism in $\cC_\detc$, and this condition determines $\bigotimes_j X_j$ up to \emph{deterministic} isomorphism.
+In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_j X_j}$ has to be the diagonal morphism in $\cC_\detc$, and \Cref{kolmprod_catdet} determines $\bigotimes_j X_j$ up to \emph{deterministic} isomorphism.
 
@@
     \label{setmulti}
-    Let $\SetMulti$ be the category with objects ordinary sets, maps $f: X \to Y$ given by functions (i.e maps in the ordinary category of sets) $f: X \to \cP(Y)\setminus \emptyset$, and composition given by
+    Let $\SetMulti$ be the category with objects ordinary sets, morphisms $f: X \to Y$ given by functions (i.e maps in the ordinary category of sets) $f: X \to \cP(Y)\setminus \emptyset$, and composition given by
     \[f\circ g(x) = \bigcup_{y \in g(x)} f(y)\]
@@
     We think of the morphisms in $\SetMulti$ as \emph{multivalued functions}.
-    See also \cite[Example~2.6]{markov_cats}.
+    See also \cite[Example~2.6]{markov_cats} for the analogous category of finite sets.
     The Cartesian product of sets gives it a symmetric monoidal structure, if we set \[(f \tensor g)(x_1,x_2) = f(x_1) \times g(x_2) \subset Y_1 \times Y_2,\] for $f:X_1 \to Y_1, g: X_2 \to Y_2$.
@@
     \]
+    \todo[inline]{E: I think here we need the second string going out of $g$ too, to fit with the form of \cref{causal_defn}?
+Although it's not critically important, the argument still works and we just marginalize that away too}.
     Applying the assumed equation together with determinism of $f$ shows that marginalizing over the first output gives the same morphism $A \to Y \otimes Y$ as marginalizing over the second output.
@@
 
-\todo[inline]{E: Not sure these examples are that great.. it seems like we do an inordinate amount of work to get the infinite tensor products, compared to the results. What do you think?}
+\todo[inline]{E: Not sure these examples (about top.
+spaces) are that great..
+it seems like we do an inordinate amount of work to get the infinite tensor products, compared to the results.
+What do you think?}
 
@@
         \item The objects are topological spaces.
-        \item A map $f: X \to Y$ consists of a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subset Y \text{ closed} \mid V \cap U \neq \emptyset\}$ for $U \subset Y$ open.
+        \item A morphism $f: X \to Y$ consists of a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subset Y \text{ closed} \mid V \cap U \neq \emptyset\}$ for $U \subset Y$ open.
         \item Composition is defined as in $\SetMulti$, by the closure of the union.

### 2019-11-04 categorical-zero-one.tex
Add references for the two zero-one laws

@@
 
-Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.\improve{add references for the Kolmogorov and Hewitt--Savage 01 laws}
+Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.
+It goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm} - although the statement appearing there is significantly different from the modern form.
+For a more recent treatment of this theorem, see e.g. \cite[Theorem~2.37]{klemke}
 
-The Hewitt--Savage zero--one law is similar - here the variables are supposed to be independent and indetically distributed, and the event is supposed to be invariant under finite permutations of the variables.
+The Hewitt--Savage zero--one law, due to Hewitt and Savage in \cite[Theorem~11.3]{hewitt_savage} is similar - here the variables are supposed to be independent and indetically distributed, and the event is supposed to be invariant under finite permutations of the variables.
 Again, under these assumptions, the event has probability one or zero.
@@
 In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness.
-In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive\todo{should this be ``multiplicative''?}  unital maps $S \to R$, i.e.~the ring homomorphisms.
+In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by multiplicative unital maps $S \to R$, i.e.~the ring homomorphisms.
 Thus the subcategory of deterministic morphisms is exactly the opposite of the usual category of commutative rings.

### 2019-11-04 categorical-zero-one.tex
typo fix

@@
 Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
-We can draw an analogy to the Euclidean approach to geometry - defining certain basic relations between the geometric objects at hand, and setting down axioms about them - with the more modern description of geometric objects as (very roughly) certain subsets of $\bR^n$.\improve{The explanation of this analogy is a bit wonky}
+We can draw an analogy to the Euclidean approach to geometry - where points, lines and so on are described only in terms of their relationships with one another - with the more modern approach, where geometric objects are defined concretely in terms of more primitive notions (i.e sets, real numbers, etc).
 
@@
 It goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm} - although the statement appearing there is significantly different from the modern form.
-For a more recent treatment of this theorem, see e.g. \cite[Theorem~2.37]{klemke}
+For a more recent treatment of this theorem, see e.g. \cite[Theorem~2.37]{klenke}
 

### 2019-11-14 categorical-zero-one.tex
Remove some superfluous uses of "clearly" &c

@@
     $\cop{X}(x) = \{(x,x)\} \subset X \times X$.
-    Then the deterministic morphisms are precisely those sending each point into a singleton set, and there is an obvious isomorphism of categories
+    Then the deterministic morphisms are precisely those sending each point into a singleton set, and there is an isomorphism of categories
     $\SetMulti_\detc \cong \sf{Set}$.
@@
     \[V = \{x \in \prod_{j\in J} X_j \mid  \pi_F(x) \in V_F \forall F\}\]
-    This is an intersection of closed subsets, hence closed, and it is clearly sent to $(V_F)$.
+    This is an intersection of closed subsets, hence closed, and it is sent to $(V_F)$.
 
@@
     The conclusion is that the closure of the image, call it $A$, has the following property: $\cl(\{(a,a) \mid a \in A\}) = A \times A$ as subsets of $Y \times Y$.
-    But since the diagonal is closed in $Y$, this clearly implies that $A$ must be a singleton.
+    But since the diagonal is closed in $Y$, this implies that $A$ must be a singleton.
 \end{proof}

### 2019-11-23 categorical-zero-one.tex
another revision

--- 2019-11-04 categorical-zero-one.tex
@@
 This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts.
-For example, applying them to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces are constant.
+For example, applying them to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.
 \end{abstract}
@@
 
-\emph{Markov categories} are an approach to probability and statistics based on category theory, developed by the first author in \cite{markov_cats}, building on much previous work by other authors (see \Cref{background}).
-The basic idea is to axiomatize the structure and properties of ``categories of stochastic processes'' - for instance, the category $\Stoch$ where objects are measurable spaces and morphisms are Markov kernels (hence the name).
-The goal is to state and prove results from probability and statistics in this context.
+\emph{Markov categories} are an approach to the foundations of probability and statistics based on category theory, proposed first by Golubtsov~\cite{golubtsov}, rediscovered recently independently by Cho and Jacobs~\cite{cho_jacobs}, and developed extensively by the first author in \cite{markov_cats}.
+The basic observation is that Markov kernels can be composed sequentially and in parallel, making them into a symmetric monoidal category $\Stoch$.
+One can then find axioms which make a symmetric monoidal category behave similarly to the actual category of Markov kernels, and then state and prove results from probability and statistics in this general abstract context.
+
 This represents a \emph{synthetic} approach to probability, in contrast with the usual measure-theoretic approach (which can be called \emph{analytic}).
 Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
-We can draw an analogy to the Euclidean approach to geometry - where points, lines and so on are described only in terms of their relationships with one another - with the more modern approach, where geometric objects are defined concretely in terms of more primitive notions (i.e sets, real numbers, etc).
+We can draw an analogy to the Euclidean approach to geometry: here, points and lines are described only in terms of their relationships with one another; while in the analytic approach often attributed to Descartes, where geometric objects are defined concretely in terms of more primitive notions like sets and real numbers.
 
-This is a treatment of the zero--one laws of Kolmogorov and of Hewitt--Savage in the setting of Markov categories.
+In this paper, we give a treatment of the zero--one laws of Kolmogorov and of Hewitt--Savage in the setting of Markov categories.
+This adds further support to the hypothesis that Markov categories are an adequate setting for the foundations of probability and statistics, adding to the existing treatments of Bayesian updating, almost sure equality, conditional independence, and theorems on sufficient statistics~\cite{cho_jacobs,markov_cats}.
 
-Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables, and an event which is in the $\sigma$-algebra generated by the variables, which is independent of any finite subset of variables, the event has probability one or zero.
-It goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm} - although the statement appearing there is significantly different from the modern form.
+Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables and an event which is in the $\sigma$-algebra generated by the variables but independent of any finite subset of these variables, the event has probability zero or one.
+This theorem goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm}, although the statement appearing there is significantly different from the modern form.
 For a more recent treatment of this theorem, see e.g. \cite[Theorem~2.37]{klenke}
 
-The Hewitt--Savage zero--one law, due to Hewitt and Savage in \cite[Theorem~11.3]{hewitt_savage} is similar - here the variables are supposed to be independent and indetically distributed, and the event is supposed to be invariant under finite permutations of the variables.
-Again, under these assumptions, the event has probability one or zero.
+The Hewitt--Savage zero--one law, due to Hewitt and Savage in \cite[Theorem~11.3]{hewitt_savage}, is similar.
+Here, the variables are assumed to be identically distributed in addition to being independent, and the event is assumed to be invariant under finite permutations of the variables.
+Again, under these assumptions, the event has probability zero or one.
 
-To formulate these statements in the general context of Markov categories, we need a notion of infinite family of random variables.
-To this end, we define a notion of \emph{infinite tensor product}.
-Given such a tensor product, satisfying a certain condition of compatibility with the structure of the Markov category (\Cref{defn_kolmogorov_ext}), we prove abstract versions of the zero--one laws, \Cref{thm:kolmog} and \Cref{thm:hewsav}.
+To formulate these statements in the general context of Markov categories, we need an abstract generalization of the concept of joint distribution of infinitely many random variables.
+To this end, we introduce a notion of \emph{infinite tensor product}, first for semicartesian monoidal categories (\Cref{infprod_semicartesian}) and then for Markov categories (\Cref{infprod_markov}).
+A morphism to such an infinite tensor product is an abstract version of a probability measure on an infinite product of measurable spaces.
+Based on this definition, we then prove abstract versions of the zero--one laws, \Cref{thm:kolmog} and \Cref{thm:hewsav}.
 
-Last, we apply our results to the case of measurable spaces and Markov kernels, deriving the zero--one laws for random variables in standard Borel spaces (this regularity assumption is needed to make the necessary infinite tensor products exist).
+Finally in \Cref{examples}, we apply our results to the category of measurable spaces and Markov kernels $\Stoch$.
+In order to guarantee that countably infinite tensor products exist, we restrict to the full subcategory of standard Borel spaces.
+We thereby rederive the standard zero--one laws for random variables in standard Borel spaces from our abstract theorems.
+We also instantiate our theorems in the Kleisli category of the lower Vietoris monad, which gives criteria for when a continuous map out of infinite product of topological spaces into a Hausdorff space is constant (\Cref{vietoris_kolmogorov} and \Cref{vietoris_hewitt_savage}).
 
@@
 $J$ is a set used for indexing products of objects; the definitions and results of this paper are nontrivial only when $J$ is infinite.
-$F$ denotes either an arbitrary finite set or more concretely a finite subset of $J$.
+$F$ denotes either an arbitrary finite set, or more concretely a finite subset of $J$.
 
-\paragraph*{Acknowledgments.} We thank Paolo Perrone for discussions leading to \Cref{poset_case}.
+\paragraph*{Acknowledgments.} We thank Paolo Perrone for discussions and \Cref{poset_case}.
 
@@
 A symmetric monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal.
-Equivalently\todo{Should there be a reference to this equivalence?}, it is a monoidal category equipped with morphisms
-\[
+Equivalently~\cite[Theorem~3.5]{GLS}, it is a symmetric monoidal category equipped with morphisms
+\begin{equation}
+	\label{projections}
 	X \otimes Y \longrightarrow X, \qquad X \otimes Y \longrightarrow Y,
-\]
+\end{equation}
 which are natural in $X$ and $Y$ and coincide with the monoidal structure isomorphisms whenever $X = I$ or $Y = I$. Here are the main examples that we will be considering.
@@
 	\label{finstoch}
-	$\FinStoch$ is the category of finite sets with \emph{stochastic matrices}, which means that $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
+	$\FinStoch$ is the category of finite sets with \emph{stochastic matrices}, which means that a morphism $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
 Stochastic matrices compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
-We consider $\FinStoch$ as a symmetric monoidal category with respect to the cartesian product of sets on objects, and as one would expect the Kronecker product of stochastic matrices on morphisms.
+We consider $\FinStoch$ as a symmetric monoidal category with respect to the cartesian product of sets on objects and the Kronecker product of stochastic matrices on morphisms; the monoidal structure isomorphisms are the obvious ones coming from the full embedding $\FinSet \subseteq \FinStoch$.
 \end{example}
@@
 We sketch the definition here and refer to~\cite[Section~4]{markov_cats} and references therein for the details.
-A \emph{Markov kernel} $(X,\Sigma_X) \to (Y,\Sigma_Y)$ is a function
+A \emph{Markov kernel} $(X,\Sigma_X) \to (Y,\Sigma_Y)$ is a map
 	\[
@@
 The monoidal unit $I$ is given by any one-element set with its unique $\sigma$-algebra.
-As a special case, morphisms $I \to (X,\Sigma_X)$ can be identified with probability measures $\sigma_X \to [0,1]$.
+As a special case, morphisms $I \to (X,\Sigma_X)$ can be identified with probability measures $\Sigma_X \to [0,1]$.
 
-	There is a well-known subclass of particularly well-behaved measurable spaces, the \emph{standard Borel spaces} or equivalently Polish spaces equipped with their Borel $\sigma$-algebras.
+	There is a well-known subclass of particularly well-behaved measurable spaces, the \emph{standard Borel spaces}, or equivalently Polish spaces equipped with their Borel $\sigma$-algebras.
 We write $\BorelStoch \subseteq \Stoch$ for the full subcategory of standard Borel spaces with Markov kernels.
@@
 
-Returning to the general theory, in string diagrams the unique morphism $\discard{X} : X \to I$ for an object $X \in \cC$ is denoted by
+Returning to the general theory, in terms of string diagrams the unique morphism $\discard{X} : X \to I$ for an object $X \in \cC$ is denoted by
 \[
@@
 \]
-The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $\discard{Y} \otimes \id : X \otimes Y \to Y$ are correspondingly written as
+The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $\discard{Y} \otimes \id : X \otimes Y \to Y$, which are the ones from~\eqref{projections}, are correspondingly written as
 \[
@@
 
-Our goal is to use semicartesian monoidal categories such as the above in order to develop aspects of probability theory in categorical terms.
-As it turns out, doing so requires a bit more structure, in a form which has been axiomatized first by Cho and Jacobs~\cite{cho_jacobs} as \emph{affine CD-categories}, although similar definitions occur in earlier work of Golubtsov~\cite{golubtsov}.
+Our goal is to use semicartesian monoidal categories in order to develop aspects of probability theory in categorical terms, in such a way that instantiating this theory in $\Stoch$ or $\BorelStoch$ recovers the standard theory.
+As it turns out, doing so requires a bit more structure, in a form which has been axiomatized first by Cho and Jacobs~\cite{cho_jacobs} as \emph{affine CD-categories}, although very similar definitions occur in earlier work of Golubtsov~\cite{golubtsov}.
 We here follow the terminology of our own~\cite[Definition~2.1]{markov_cats}.
@@
 \begin{definition}
-	A \emph{Markov category} $\cC$ is a semicartesian symmetric monoidal category where every object $X \in \cC$ is equipped with a morphism
+	A \emph{Markov category} $\cC$ is a semicartesian symmetric monoidal category where every object $X \in \cC$ is equipped with a distinguished morphism
 	\begin{equation}
@@
 
-A closely related definition was also used in earlier work of Golubtsov~\cite{golubtsov}, who had proposed a closely related definition, and Cho and Jacobs~\cite{cho_jacobs}, where an equivalent definition was used under the term \emph{affine CD-category}.
-
 We think of the comultiplication~\Cref{comultiplication} as a copying operation.
-The coassociativity and counitality conditions guarantee that copying with any number of output wires is well-defined, and we draw it likewise as a single black dot with any number of outgoing wires, as in
+The coassociativity and counitality conditions guarantee that copying with any number of output wires is well-defined, and we draw it likewise as a single black dot with any number of outgoing wires, like this:
 \[
@@
 
-As per~\cite[Remark~10.12]{markov_cats}, the deterministic morphisms form a symmetric monoidal cartesian subcategory $\cC_\detc \subseteq \cC$ which contains all structure morphisms of $\cC$, including the comultiplications themselves.
-The fact that all morphisms are comonoid homomorphisms implies that $\cC_\detc$ is cartesian monoidal.
+As per~\cite[Remark~10.12]{markov_cats}, the deterministic morphisms form a symmetric monoidal subcategory $\cC_\detc \subseteq \cC$ which contains all structure morphisms of $\cC$, including the comultiplications themselves.
+The fact that all morphisms are comonoid homomorphisms implies that $\cC_\detc$ is actually cartesian monoidal.
 
 In $\FinStoch$, the deterministic morphisms $X \to Y$ are exactly the $\{0,1\}$-valued stochastic matrices.
-Since these can be identified with honest functions $X \to Y$, we conclude that $\FinStoch_\detc$ is equivalent to the category of finite sets.
+Since these can be identified with honest functions $X \to Y$, we conclude that $\FinStoch_\detc$ is equivalent to $\FinSet$.
 In $\Stoch$, the deterministic morphisms $f : X \to Y$ are exactly those Markov kernels for which $f(S|x) \in \{0,1\}$ for every $S \in \Sigma_Y$ and $x \in X$.
-In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness.
-In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by multiplicative unital maps $S \to R$, i.e.~the ring homomorphisms.
+In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness; in $\BorelStoch$, the deterministic morphisms can be identified with the measurable functions.
+In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive unital maps $S \to R$ which are in addition multiplicative, i.e.~the ring homomorphisms.
 Thus the subcategory of deterministic morphisms is exactly the opposite of the usual category of commutative rings.
@@
 
-If $\bigotimes_{j \in F} X_j$ is a finite product without any particular order on the factors\footnote{See e.g.~\cite[Proposition~II.1.5]{DMOS} for how to make sense of tensor products in symmetric monoidal categories without a prescribed order of the factors.}, then we also write $\perp_{j \in F} X_j \mid\mid A$ to denote the corresponding conditional independence for given $p : A \to \bigotimes_{j \in F} X_j$.
+Conditional independence does not depend on the order of the tensor factors: if $p$ displays the conditional independence $X_1 \perp \ldots \perp X_n \mid\mid A$, then composing $p$ with any permutation $\sigma$ of the tensor factors $X_1,\ldots,X_n$ gives a morphism $A \to X_{\sigma(1)} \otimes \ldots \otimes X_{\sigma(n)}$ which displays the conditional independence $X_{\sigma(1)} \perp \ldots \perp X_{\sigma(n)} \mid\mid A$.
+Therefore if $\bigotimes_{j \in F} X_j$ is a finite product without any particular order on the factors\footnote{See e.g.~\cite[Proposition~II.1.5]{DMOS} for how to make sense of tensor products in symmetric monoidal categories without a prescribed order of the factors.}, then for $p : A \to \bigotimes_{j \in F} X_j$ there is no ambiguity about whether $p$ displays conditional independence or not, and we also write $\perp_{j \in F} X_j \mid\mid A$ in case that it does.
 
-\section{Infinite tensor products in semicartesian monoidal categories}
+\section{Infinite tensor products in semicartesian symmetric monoidal categories}
 \label{infprod_semicartesian}
@@
 	\label{semicartesian_infproduct}
-	Let $(X_j)_{j \in J}$ be a family of objects in $\cC$. An \emph{infinite tensor product}
+	Let $(X_i)_{i \in J}$ be a family of objects in $\cC$. An \emph{infinite tensor product}
 	\[
@@
 	\]
-	is the limit of the diagram $F \mapsto X_F$, indexed by the poset of finite subsets $F \subset J$ ordered by reverse inclusion, if this limit exists and is preserved by the functor $- \otimes Y$ for every object $Y \in \cC$.
+	is the limit of the diagram $F \mapsto X_F$, indexed by the poset of finite subsets $F \subseteq J$ ordered by reverse inclusion, if this limit exists and is preserved by the functor $- \otimes Y$ for every object $Y \in \cC$.
 \end{definition}
@@
 	to be an isomorphism, where $X_{J \,\sqcup\, \{\ast\}}$ is the infinite tensor product of the original family with $X_\ast$ thrown in.
+We now show that this is indeed the case thanks to the preservation condition in \Cref{semicartesian_infproduct}, even if $X_{J \,\sqcup\, \{\ast\}}$ does not exist a priori.
 
-	If we do not yet assume that $X_{J \,\sqcup\, \{\ast\}}$ exists, then we can exhibit $X_J \otimes X_\ast$ as the relevant cofiltered limit as follows.
-The object $X_J \otimes X_\ast$ can be equipped finite marginalization morphisms with respect to $F \subseteq J \sqcup \{\ast\}$ given by
+	To do so, we exhibit $X_J \otimes X_\ast$ as the relevant cofiltered limit, which equips it with the defining universal property of $X_{J \,\sqcup\, \{\ast\}}$, as follows.
+The object $X_J \otimes X_\ast$ can be equipped with finite marginalization morphisms with respect to $F \subseteq J \sqcup \{\ast\}$ given by
 	\[
@@
 	in case $\ast \not \in F$.
-It is straightforward to check that these morphisms equip $X_J \otimes X_\ast$ with the right universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
+It is straightforward to check that these morphisms indeed make $X_J \otimes X_\ast$ carry the universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
 It is also easy to see that this new cofiltered limit is again preserved by every functor $- \otimes Y$, based on the assumption that the defining cofiltered limit of the original infinite tensor product is preserved by $- \otimes (X_\ast \otimes Y)$ as well.
 
-	In other words, the preservation condition in this definition amounts to the requirement that the canonical comparison morphism
-	must be an isomorphism, as one would expect intuitively from a notion of infinite tensor product. 
+	In summary, the preservation condition in this definition amounts to the requirement that the canonical comparison morphism~\eqref{comparison} must be an isomorphism, as one would expect intuitively from a good notion of infinite tensor product.
 \end{remark}
@@
 	\label{infprods_cring}
-	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}.
-Thus in the case where our Markov category is $\CRing_+\op$, we recover the usual folklore definition of an infinite tensor product of rings $\bigotimes_{j \in J} R_j$ in terms of formal sums of elementary tensors, where an elementary tensor is a family of elements $(r_j)_{j \in J}$ such that all but finitely many are equal to the respective unit.
+	The dual definition of infinite tensor products of algebraic structures as \emph{filtered colimits} of finite tensor products is well-known in the literature, e.g.~in the case of C*-algebras~\cite[p.~315]{blackadar}, although we do not know whether the preservation condition has been made explicit before.
+For example in the case where our category is $\CRing_+\op$, we recover the usual folklore definition of an infinite tensor product of rings $\bigotimes_{i \in J} R_i$ in terms of formal sums of elementary tensors, where an elementary tensor is a family of elements $(r_i)_{i \in J}$ such that all but finitely many are equal to the respective unit.
 The necessary preservation condition is easily seen to hold.
-Note that we do not yet consider the multiplication on $\bigotimes_{j \in J} R_j$, since \Cref{semicartesian_infproduct} is not yet concerned with the comonoid structures on the objects.
+Note that we do not yet consider the multiplication on $\bigotimes_{i \in J} R_i$, since \Cref{semicartesian_infproduct} is not yet concerned with the comonoid structures on the objects.
 We will get to this in the next section.
 
-	Intuitively, our definition matches up with the known algebraic ones under the categorical duality of algebra and geometry, where our definition is on the geometrical side of the duality.
+	Intuitively, our definition matches up with the known algebraic ones under the categorical duality of algebra and geometry, where our \Cref{semicartesian_infproduct} is on the geometrical side of the duality.
 \end{example}
@@
 Thus applying the defining universal property of an infinite tensor product with respect to maps out of $I$ implements the \emph{Kolmogorov extension theorem} in $\cC$: probability measures on an infinite product $X_J$ are in bijection with consistent families of probability measures on the finite products $X_F$ for $F \subseteq J$.
+The spirit of \Cref{semicartesian_infproduct} is thus such that it turns the Kolmogorov extension theorem into a definition.
 \end{remark}
@@
 Since the Kolmogorov extension theorem does not hold for general (even merely countable) products of measurable spaces~\cite{AJ}, this is not the case without further additional assumptions on the measurable spaces involved.
-Thus we do not know whether $\Stoch$ has infinite tensor products, although we suspect that it does not; but even if it does, they are in general not the ones that one would like to have for the purposes of probability theory.
+Thus we do not know whether $\Stoch$ has infinite tensor products, although we suspect that it does not; but even if it does, they are in general not the ones that one will care about for the purposes of probability theory.
 
-	However, the situation improves for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem holds~\cite[Theorem~14.35]{klenke}.
-In other words, if $\left( (X_j, \Sigma_j) \right)_{j \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{j \in \bN} X_j$ carrying the product $\sigma$-algebra $\Sigma_\bN$ satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
-We now show that this implies the universal property in general.
+	However, the situation improves for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem indeed holds~\cite[Theorem~14.35]{klenke}.
+In other words, if $\left( (X_j, \Sigma_j) \right)_{j \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{j \in \bN} X_j$, carrying the product $\sigma$-algebra $\Sigma_\bN$, satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
+We now prove that this implies the universal property in general.
 
-	Suppose that
+	Thus suppose that
 	\[
@@
 	is a family of Markov kernels satisfying the compatibility condition $\pi_{F',F} \circ g_{F'} = g_F$ for all finite $F \subseteq F' \subseteq J$.
-Then for every $a \in A$, the probability measures $g_F(-|a) : \Sigma_F \to [0,1]$ are a compatible family to which the Kolmogorov extension theorem in the form~\cite[Theorem~14.35]{klenke} applies, and we obtain a unique probability measure $g_J(-|a) : \Sigma_J \to [0,1]$ which has the $g_F(-|a)$ as its finite marginals.
+Then for every $a \in A$, the probability measures $g_F(-|a) : \Sigma_F \to [0,1]$ are a compatible family to which the Kolmogorov extension theorem in the form of~\cite[Theorem~14.35]{klenke} applies, and we obtain a unique probability measure $g_J(-|a) : \Sigma_J \to [0,1]$ which has the original $g_F(-|a)$ as its finite marginals.
 It remains to be shown that for every $S \in \Sigma_J$, the map $a \mapsto g_J(S|a)$ is measurable.
@@
 	\label{infprods_finstoch}
-	Infinite tensor products never exist in $\FinStoch$, in the following sense: if the family $(X_j)_{j \in J}$ is such that no $X_j$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_j X_j$ does not exist.
-One way to see this is to use the fact that the hom-sets of $\FinStoch$ are convex sets in the space of matrices, and that composition distributes over these convex combinations, making $\FinStoch$ into a category enriched in convex sets.
-Since these hom-sets are finite-dimensional, for every $Y$ and $Z$ there is $n \in \bN$ such that among every $n$ morphism $Y \to Z$, one of them can be written as a convex combination of the others.
-Now suppose that the product $\bigotimes_j X_j$ existed.
-Then by choosing varying elements of each $X_j$, we can construct uncountably many morphisms $1 \to \bigotimes_j X_j$ whose marginalizations $1 \to X_F$ are all deterministic.
+	Infinite tensor products never exist in $\FinStoch$, in the following sense: if the family $(X_i)_{i \in J}$ is such that no $X_i$ is empty and infinitely many of them contain at least two elements, then $\bigotimes_i X_i$ does not exist.
+One way to see this is to use the fact that the hom-sets of $\FinStoch$ are convex subsets of the vector space of matrices, and that composition distributes over these convex combinations, making $\FinStoch$ into a category enriched in convex sets.\footnote{See also \href{https://golem.ph.utexas.edu/category/2010/09/what_is_this_category_enriched.html}{golem.ph.utexas.edu/category/2010/09/what\_is\_this\_category\_enriched.html} for discussion of this enrichment.} Since these hom-sets are finite-dimensional, for every $Y$ and $Z$ there is $n \in \bN$ such that among every $n$ morphisms $Y \to Z$, one of them can be written as a convex combination of the others.
+Now suppose that the product $\bigotimes_i X_i$ existed.
+Then by choosing varying elements of each $X_j$, we could construct uncountably many morphisms $1 \to \bigotimes_i X_i$ whose marginalizations $1 \to X_F$ are all deterministic.
 Per the above, one of these hypothetical morphisms can be written as a convex combination of finitely many others.
-By choosing $F \subseteq J$ suitably, we can achieve that the finite marginalizations $1 \to X_F$ are all distinct.
-Since they are deterministic by construction, and no deterministic morphism in $\FinStoch$ can be written as a convex combination of other deterministic morphisms, we have arrived at a contradiction.
+By choosing $F \subseteq J$ suitably, we can achieve that the finite marginalizations $1 \to X_F$ of the finitely many morphisms involved in this convex combination are all distinct.
+Since these morphisms $1 \to X_F$ are deterministic by construction, and no deterministic morphism in $\FinStoch$ can be written as a convex combination of other deterministic morphisms, we have arrived at a contradiction.
+Thus $\bigotimes_i X_i$ does not exist.
 \end{example}
+
+\begin{example}[Paolo Perrone, personal communication]
+	\label{poset_case}
+	Suppose that $\cC$ is a partially ordered set, considered as a category with $X \geq Y$ if and only if the morphism $X \to Y$ exists.\footnote{This direction of the ordering is opposite to the usual convention, but necessary for the following to work on the nose.} Then the monoidal structure makes $\cC$ into a preordered commutative monoid, which we write additively.
+Here, the functoriality of the monoidal structure amounts to the assumption that addition is monotone,
+	\[
+		X \geq Y \quad\: \Longrightarrow \quad\: X + Z \geq Y + Z.
+	\]
+	Furthermore, the monoidal structure is semicartesian if and only if $X \geq 0$ for every $X$.
+One can then apply \Cref{infprod_operadic} to show that $\cC$ has infinite tensor products if and only if $\cC$ is a \emph{finitary complete monoid} in the sense of Goldstern and Karner~\cite[Section~2.2]{karner}, and these infinite tensor products then correspond to infinite sums $\sum_{i \in J} X_i$ in the monoid.
+\end{example}
+
+We return to the general theory.
 
@@
 	\]
-	exhibit $X_{F_1} \otimes X_{J_2}$ as the cofiltered limit of the $X_{F_1} \otimes X_{F_2}$ by the preservation assumption. Similarly, the morphisms
+	exhibit $X_{F_1} \otimes X_{J_2}$ as the cofiltered limit of the $X_{F_1} \otimes X_{F_2}$ by the preservation assumption. Similarly for varying $F_1$, the morphisms
 	\[
@@
 The claimed universal property follows since a limit of limits is a limit, and it is easy to see that the diagram shapes match up: the poset of finite subsets of $J_1 \sqcup J_2$ is the product of the posets of finite subsets of $J_1$ and $J_2$.
-The preservation property with respect to applying a tensoring functor $- \otimes Y$ carries along.
+The preservation property with respect to applying a tensoring functor $- \otimes Y$ carries along both of the above limits individually.
 \end{proof}
@@
 where the object on the right can also be written as $\bigotimes_{(k,j) \in F} X_{k,j}$.
-It is straightforward to see that this $\rho_F$ does not depend on the particular choice of $G$.
+It is straightforward to see that this $\rho_F$ does not depend on the particular choice of $G$ (up to monoidal structure isomorphisms).
 We now show that these $\rho_F$'s are finite marginalization morphisms which make the doubly infinite tensor product $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ into the single infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
@@
 	Suppose that $(J_k)_{k \in K}$ is a family of sets and $(X_{k,j})_{j \in J_k, k \in K}$ a doubly indexed family of objects.
-If all of the infinite tensor products $\bigotimes_{j \in J_k} X_{j,k}$ and $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ exist, then the above morphisms $\rho_F$ exhibit $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ as the infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
+If all of the infinite tensor products $\bigotimes_{j \in J_k} X_{j,k}$ and $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ exist, then the morphisms~\eqref{double_infproduct} exhibit $\bigotimes_{k \in K} \bigotimes_{j \in J_k} X_{k,j}$ as the infinite tensor product $\bigotimes_{k \in K, \: j \in J_k} X_{k,j}$.
 \end{lemma}
@@
 	By repeated application of \Cref{two_infproducts}, the second half of~\Cref{double_infproduct} exhibits $\bigotimes_{k \in G} \bigotimes_{j \in J_k} X_{k,j}$ as the infinite tensor product of the $X_{k,j}$ for $k \in G$ and $j \in J_k$.
-The relevant universal property as well as its preservation by $- \otimes Y$ then follow from a straightforward diagram chase.
+The relevant universal property as well as its preservation by $- \otimes Y$ then follow from another straightforward diagram chase.
 \end{proof}
-
-\begin{example}[Perrone]
-	\label{poset_case}
-	Suppose that $\cC$ is a partially ordered set, considered as a category with $X \geq Y$ if and only if the morphism $X \to Y$ exists.\footnote{This direction of the ordering is opposite to the usual convention, but necessary for the following to work on the nose.} Then the monoidal structure makes $\cC$ into an ordered commutative monoid, which we write additively, where the functoriality of the monoidal structure amounts to the assumption that addition is monotone,
-	\[
-		X \geq Y \quad\: \Longrightarrow \quad\: X + Z \geq Y + Z.
-	\]
-	Furthermore, the monoidal structure is semicartesian if and only if $X \geq 0$ for every $X$.
-One can then apply \Cref{infprod_operadic} to show that $\cC$ has infinite tensor products if and only if $\cC$ is a \emph{finitary complete monoid} in the sense of Goldstern and Karner~\cite[Section~2.2]{karner}.
-\end{example}
 
@@
     \label{defn_kolmogorov_ext}
-    Let $\cC$ be a Markov category and $(X_j)_{j \in J}$ a family of objects.
-We say that an infinite tensor product $X_J = \bigotimes_{j \in J} X_j$ is a \emph{Kolmogorov product} if the finite marginalization morphisms $\pi_F : X_J \to X_F$ are deterministic.
+    Let $\cC$ be a Markov category and $(X_i)_{i \in J}$ a family of objects.
+We say that an infinite tensor product $X_J = \bigotimes_{i \in J} X_i$ is a \emph{Kolmogorov product} if the finite marginalization morphisms $\pi_F : X_J \to X_F$ are deterministic.
 \end{definition}
@@
 In $\BorelStoch$, the infinite tensor products constructed in \Cref{infprods_stoch} are Kolmogorov products.
-In $\CRing_+\op$, the infinite tensor products from \Cref{infprods_cring} are Kolmogorov products as well as long as one equips $\bigotimes_j R_j$ with the tensor product ring structure, since this one is the only one which makes the canonical inclusions $R_j \to \bigotimes_j R_j$ into ring homomorphisms.
+In $\CRing_+\op$, the infinite tensor products from \Cref{infprods_cring} are Kolmogorov products as well, provided that one equips $\bigotimes_i R_i$ with the tensor product ring structure, since this one is the only one which makes the canonical inclusions $R_j \to \bigotimes_i R_i$ into ring homomorphisms.
 These examples illustrate the following important point.
@@
 In particular, there may be infinite tensor products which are not Kolmogorov products.
-For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_j R_j$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
+For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_i R_i$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
 
 \begin{remark}
-	If $\cC$ is positive in the sense of~\cite[Definition~11.22]{markov_cats}, then a morphism $A \to B \otimes C$ is deterministic if and only if both of its marginals are $A \to B$ and $A \to C$ are deterministic~\cite[Corollary~12.15]{markov_cats}.
-In this case, it follows that the finite marginalizations $\pi_F$ are deterministic if and only if all the single-factor marginalizations $\pi_{\{j\}} : X_J \to X_j$ are.
-Thus for an infinite tensor product to be a Kolmogorov product, it is then enough to verify that the $\pi_{\{j\}}$ are deterministic.
+	If the Markov category $\cC$ is positive in the sense of~\cite[Definition~11.22]{markov_cats}, then a morphism $A \to B \otimes C$ is deterministic if and only if both of its marginals $A \to B$ and $A \to C$ are deterministic~\cite[Corollary~12.15]{markov_cats}.
+In this case, it follows that the finite marginalizations $\pi_F$ are deterministic if and only if all the single-factor marginalizations $\pi_{\{i\}} : X_J \to X_i$ are.
+Thus for an infinite tensor product to be a Kolmogorov product, it is then enough to verify that the $\pi_{\{i\}}$ are deterministic.
 \end{remark}
+
+Using the multiplicativity of the comonoid structure of~\eqref{multiplicativity}, we see that \Cref{two_infproducts,infprod_operadic} hold also for Kolmogorov products.
 
@@
 \begin{proof}
-	For $(X_j)_{j \in J}$ a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$, we first show that if we have a compatible family of deterministic morphisms $g_F : A \to X_F$, then also the induced $g_J : A \to X_J$ is deterministic.
+	For $(X_i)_{i \in J}$ a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$, we first show that if we have a compatible family of deterministic morphisms $g_F : A \to X_F$, then also the induced $g_J : A \to X_J$ is deterministic.
 Drawing the Kolmogorov product $X_J$ as a double wire, we need to prove the determinism equation
@@
 	where we have assumed without loss of generality that the two finite marginalization maps are the same, which we can by replacing the corresponding finite subsets by their union.
-Using the determinism assumption for $\pi_F$ on the right as well as the assumption that $g_F = \pi_F \circ g_J$ is deterministic implies the claim.
+Using the determinism assumption for $\pi_F$ on the right, as well as the assumption that $g_F = \pi_F \circ g_J$ is deterministic, implies the claim.
 
@@
 
-In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_j X_j}$ has to be the diagonal morphism in $\cC_\detc$, and \Cref{kolmprod_catdet} determines $\bigotimes_j X_j$ up to \emph{deterministic} isomorphism.
+In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_i X_i}$ has to be the equal to the corresponding diagonal in $\cC_\detc$, and \Cref{kolmprod_catdet} determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
 
@@
     \label{setmulti}
-    Let $\SetMulti$ be the category with objects ordinary sets, morphisms $f: X \to Y$ given by functions (i.e maps in the ordinary category of sets) $f: X \to \cP(Y)\setminus \emptyset$, and composition given by
-    \[f\circ g(x) = \bigcup_{y \in g(x)} f(y)\]
-    for $g: X \to Y, f: Y \to Z$.
-    We think of the morphisms in $\SetMulti$ as \emph{multivalued functions}.
-    See also \cite[Example~2.6]{markov_cats} for the analogous category of finite sets.
-    The Cartesian product of sets gives it a symmetric monoidal structure, if we set \[(f \tensor g)(x_1,x_2) = f(x_1) \times g(x_2) \subset Y_1 \times Y_2,\] for $f:X_1 \to Y_1, g: X_2 \to Y_2$.
-    This is a semicartesian monoidal structure, and we can give it a Markov category structure by setting
-    $\cop{X}(x) = \{(x,x)\} \subset X \times X$.
-    Then the deterministic morphisms are precisely those sending each point into a singleton set, and there is an obvious isomorphism of categories
+    Let $\SetMulti$ be the category with objects ordinary sets, morphisms $f: X \to Y$ given by \emph{multivalued functions}, which are maps $f: X \to \cP(Y)\setminus \emptyset$, with composition of morphisms $f : X \to Y$ and $g : Y \to Z$ given by
+    	\begin{equation}
+		\label{relational_composition}
+		(g\circ f)(x) := \bigcup_{y \in f(x)} g(y).
+	\end{equation}
+    See also \cite[Example~2.6]{markov_cats} for a treatment of the full subcategory $\FinSetMulti$ on finite sets.
+    The Cartesian product of sets gives it a symmetric monoidal structure, if for $f : X_1 \to Y_1$ and $g: X_2 \to Y_2$ we set
+	\[
+	(f \tensor g)(x_1,x_2) := f(x_1) \times g(x_2) \:\subseteq\: Y_1 \times Y_2.
+	\]
+	With the obvious structure isomorphisms inherited from $\Set$, this turns $\SetMulti$ into a semicartesian symmetric monoidal category, and we can give it a Markov category structure by setting
+    $\cop{X}(x) := \{(x,x)\} \subset X \times X$.
+    Then the deterministic morphisms are precisely those sending each point into a singleton set, resulting in an isomorphism of categories
     $\SetMulti_\detc \cong \sf{Set}$.
-    Of course, $\sf{Set}$ actually has all infinite products, but they do not form Kolmogorov products, or even infinite tensor products in $\sf{SetMulti}$.
-    To see this, consider the family $X_n = \{0,1\}$ for $n \in \bN$.
-    A map $* \to \prod_{n\in \bN} \{0,1\} = X_\bN$ is just a subset of this infinite product.
-    Given such a subset $U$, the finite marginals $* \to X_F$ for $F \subset \bN$ are the images of $U$ under the projection map.
+
+    Of course, $\sf{Set}$ has all infinite products. But perhaps surprisingly, these products are not Kolmogorov products, or even infinite tensor products in $\sf{SetMulti}$.
+    \todo[inline]{T: I think we shouldn't use our $X_J$ notation in the following example, precisely because we don't have infinite tensor products}
+    To see this, consider for example the family $(X_n)_{n\in\bN}$ with $X_n = \{0,1\}$ for all $n$. 
+    A map $* \to \prod_{n\in \bN} \{0,1\}$ is just a nonempty subset of this infinite product.
+    Given such a subset $U$, the finite marginals $* \to \prod_{n \in F} \{0,1\}$ for $F \subset \bN$ are the images of $U$ under the projection map.
     But these images do not determine $U$. For instance, consider the subset $U$ of those sequences containing at least one $1$.
-    The image in $X_F$ is all of $X_F$ (since any finite sequence of $0$s and $1$s can be extended to one containing a $1$).
-    But $U$ is not all of $X_\bN$.
+    Its image in every $\prod_{n \in F} \{0,1\}$ is the whole set, since any finite sequence of $0$s and $1$s can be extended to one containing a $1$, but $U$ itself is a proper subset.
+It is clear that this example is quite generic and works for any infinite family of nonempty sets, infinitely many of which contain at least two elements, as in \Cref{infprods_finstoch}.
 
@@
 \begin{definition}
-	We say that a morphism $p : A \to \bigotimes_{j \in J} X_j$ \emph{displays the conditional independence} $\perp_{j \in J}  X_j \mid\mid A$ if each finite marginalization $p_F : A \to \bigotimes_{j \in F} X_j$ displays the conditional independence $\perp_{j \in F} X_j \mid\mid A$.
+	Let $X_J = \bigotimes_{i \in J} X_i$ be a Kolmogorov product in a Markov category.
+We say that a morphism $p : A \to X_J$ \emph{displays the conditional independence} $\perp_{i \in J}  X_i \mid\mid A$ if each finite marginalization $p_F : A \to X_F$ displays the conditional independence $\perp_{i \in F} X_i \mid\mid A$.
 \end{definition}
@@
 
-Throughout this section, $(X_j)_{j \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
+Throughout this section, $(X_i)_{i \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
 
 \begin{lemma}[The infinite independence lemma]
-	Suppose $p: A \to X_J$ displays the conditional independence $\perp_j X_j \mid\mid A$.
-	Then for every $j \in J$, it also displays the independence $X_j \perp X_{J \setminus \{j\}} \mid\mid A$.
+	Suppose $p: A \to X_J$ displays the conditional independence $\perp_i X_i \mid\mid A$.
+	Then for every $i \in J$, it also displays the independence $X_i \perp X_{J \setminus \{i\}} \mid\mid A$.
 \end{lemma}
@@
 	\]
-	As the codomain is exactly the Kolmogorov product $X_J$, it is enough to prove this equation upon composing the second output with the finite marginalizations $\pi_F : X_{J\setminus\{j\}} \to X_F$.
+	As the codomain is exactly the Kolmogorov product $X_J$, it is enough to prove this equation upon composing the second output with the finite marginalizations $\pi_F : X_{J\setminus\{i\}} \to X_F$.
 But this is a consequence of the assumption.
@@
     \label{thm:kolmog}
-    Suppose that $\cC$ is a Markov category, and that $(X_j)_{j \in J}$ is a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
-If morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ are such that for every finite $F \subseteq J$, the joint
+    Suppose that $\cC$ is a Markov category, and that $(X_i)_{i \in J}$ is a family of objects with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
+Suppose that morphisms $p: A \to X_J$ and deterministic $s : X_J \to T$ satisfy the following:
+    \begin{enumerate}
+	    \item $p$ displays the conditional independence $\perp_i X_i \mid\mid A$.
+	    \item For every finite $F \subseteq J$, the joint
     		\[
@@
     		\]
-    displays the conditional independence $X_F \perp T \mid\mid A$, then the composite $sp : A \to T$ is deterministic as well.
+    		displays the conditional independence $X_F \perp T \mid\mid A$.
+    \end{enumerate}
+Then the composite $sp : A \to T$ is deterministic as well.
 \end{theorem}
@@
 \begin{proof}
-	Assuming $\ast \not \in J$, let us write $X_\ast := T$, so that $X_J \otimes X_\ast$ is the Kolmogorov product of the family $(X_j)_{j \in J \,\sqcup\,\{\ast\}}$.
+	Assuming $\ast \not \in J$, let us write $X_\ast := T$, so that $X_J \otimes X_\ast$ is the Kolmogorov product of the family $(X_i)_{i \in J \,\sqcup\,\{\ast\}}$.
 It is clear from the definitions and the assumption that the morphism
@@
     \]
-    displays the conditional independence $\perp_{j \in J\,\sqcup\,\{\ast\}} X_j \mid\mid A$.
+    displays the conditional independence $\perp_{i \in J\,\sqcup\,\{\ast\}} X_i \mid\mid A$.
     By the infinite independence lemma, this means that it also displays the conditional independence $X_\ast \perp X_J \mid\mid A$.
@@
 It applies to Kolmogorov products where all factors are copies of the same object.
-So for an object $X$ and the constant family $(X)_{j \in J}$, let us say that the corresponding Kolmogorov product $X_J$ is the \emph{Kolmogorov power} of $X$ by $J$.
+So for an object $X$ and the constant family $(X)_{i \in J}$, let us say that the corresponding Kolmogorov product $X_J$ is the \emph{Kolmogorov power} of $X$ by $J$, whenever it exists.
 
-A \emph{finite permutation} of the set $J$ is a bijection $\alpha : J \to J$ which fixes all but finitely many elements.
-Suppose that $\alpha : J \to J$ is a finite permutation or more generally any injection.
-Then an application of the universal property of the Kolmogorov power shows that $\alpha$ induces a morphism $\hat{\alpha} : X_J \to X_{\alpha(J)}$ by applying the universal property of $X_J$ to the compatible family of composite morphisms
+A \emph{finite permutation} of the set $J$ is a bijection $\sigma : J \to J$ which fixes all but finitely many elements.
+Suppose that $\sigma : J \to J$ is a finite permutation or more generally any injection.
+Then an application of the universal property of the Kolmogorov power shows that $\sigma$ induces a morphism $\hat{\sigma} : X_J \to X_J$ by applying the universal property of $X_J$ to the compatible family of composite morphisms
 \[
 	\begin{tikzcd}
-		X_J \ar{r}{\pi_F} & X_F \ar{r}{\cong} & X_{\alpha(F)},
+		X_J \ar{r}{\pi_{\sigma(F)}} & X_{\sigma(F)} \ar{r}{\cong} & X_{F},
 	\end{tikzcd}
 \]
-where the second morphism matches up the factors of the two finite products involved as prescribed by the bijection $\alpha|_F : F \stackrel{\cong}{\longrightarrow} \alpha(F)$.
-Here we are using the fact that each finite subset of $\alpha(J)$ has the form $\alpha(F)$ for a unique finite $F \subset J$ (namely the preimage).
-The relevant compatibility condition is straightforward to check. Moreover, $\hat{\alpha}$ is deterministic by \Cref{kolmprod_catdet}.
+where the second morphism matches up the factors of the two finite products involved as prescribed by the bijection $\sigma|_F : F \stackrel{\cong}{\longrightarrow} \sigma(F)$.
+The relevant compatibility condition is straightforward to check.
+Moreover, $\hat{\sigma}$ is deterministic by \Cref{kolmprod_catdet}.
 
@@
     	\begin{enumerate}
-		\item $p$ displays the conditional independence $\perp_j X_j \mid\mid A$.
-		\item For every finite permutation $\alpha : J \to J$, we have $\hat{\alpha} p = p$ and $s \hat{\alpha} = s$. 
+		\item $p$ displays the conditional independence $\perp_{i \in J} X_i \mid\mid A$.
+		\item For every finite permutation $\sigma : J \to J$, we have $\hat{\sigma} p = p$ and $s \hat{\sigma} = s$. 
     	\end{enumerate}
@@
 
-In contrast to \Cref{thm:kolmog}, we now have two additional relevant assumptions: $\cC$ is causal and $J$ is infinite. We first prove a useful auxiliary observation.
+In contrast to \Cref{thm:kolmog}, we now have two relevant assumptions in addition to those on $p$ and $s$, namely that $\cC$ is causal and $J$ is infinite.
+Before getting to the proof, we first make a useful auxiliary observation.
 
@@
     \]
-    \todo[inline]{E: I think here we need the second string going out of $g$ too, to fit with the form of \cref{causal_defn}?
-Although it's not critically important, the argument still works and we just marginalize that away too}.
-    Applying the assumed equation together with determinism of $f$ shows that marginalizing over the first output gives the same morphism $A \to Y \otimes Y$ as marginalizing over the second output.
+    Applying the assumed equation together with determinism of $f$ shows that marginalizing over the first output gives the same morphism $A \to Y \otimes Y \otimes Y$ as marginalizing over the second output.
 Therefore, applying the causality property of \Cref{causal_defn} with $h_1$ and $h_2$ the two marginalizations, we can conclude the equality
@@
     \]
-    Marginalizing this further over the middle output and truncating the redundant pieces proves the desired equation.
+    Marginalizing this further over the second and third outputs and truncating the redundant pieces proves the desired equation.
 \end{proof}
@@
 	\end{equation}
-	so that the joint is invariant. Here, the first and last equation hold by the invariance assumption, and the second because $\hat{\alpha}$ is deterministic.
+	so that the joint given by the right-hand side is invariant. Here, the first and last equation hold by the invariance assumption, and the second because $\hat{\sigma}$ is deterministic.
 
-	We next show that this equation still holds if $\alpha$ is merely an injection.
-By the universal property of $X_J \otimes T$ as the infinite tensor product of the family $(X_j)_{j \in J}$ together with $T$, it is enough to prove \Cref{strong_invariance} upon marginalization by $\pi_F \otimes \id$ for all finite $F \subseteq J$.
-Since we can find a finite permutation $\alpha' : J \to J$ such that $\alpha'|_F = \alpha|_F$, the claim follows from the finite permutation case.
+	We next argue that this equation still holds if $\sigma$ is merely an injection.
+By the universal property of $X_J \otimes T$ as the infinite tensor product of the family $(X_i)_{i \in J}$ together with $T$, it is enough to prove \Cref{strong_invariance} upon marginalization by $\pi_F \otimes \id$ for all finite $F \subseteq J$.
+Since we can find a finite permutation $\sigma' : J \to J$ such that $\sigma'|_F = \sigma|_F$ for any given $F$, the claim follows from the finite permutation case.
 
 	Consider the morphism given by composing \eqref{strong_invariance} with $s$ on the first output.
-Since these are the same for all injections $\alpha$, \Cref{aseqlemma} tells us that the morphisms $s \hat{\alpha}$ are all $p$-a.s.~equal to $s$, for every injection $\alpha : J \to J$.
+Since these are the same for all injections $\sigma$, \Cref{aseqlemma} tells us that the morphisms $s \hat{\sigma}$ are all $p$-a.s.~equal to $s$, for every injection $\sigma : J \to J$.
 
-	Now let $J = J_1 \,\sqcup\, J_2$ be a decomposition of $J$ into two disjoint subsets having the cardinality of $J$; here is where it is relevant that $J$ is infinite.
+	Now let $J = J_1 \,\sqcup\, J_2$ be a decomposition of $J$ into two disjoint subsets having the same cardinality as $J$; this is the step which relies on $J$ being infinite.
 Let $\tau_1, \tau_2: J \to J$ be injections with images $J_1$ and $J_2$, respectively.
@@
 \section{Examples}
+\label{examples}
 
 We now show how our results specialize to the standard Kolmogorov and Hewitt--Savage zero--one laws in the case of standard Borel spaces.
-Further down we give another application to continuous maps between topological spaces.
+Further down we will give another application to continuous maps between topological spaces.
 
 \begin{corollary}[Kolmogorov zero--one law]
-	Suppose $\Omega$ is a standard Borel space with a probability measure $P$ and that $\left(f_j: \Omega \to X_j\right)_{j \in \bN}$ is a sequence of independent random variables taking values in standard Borel spaces $X_j$.
-Suppose that $T \subseteq \Omega$ is in the coarsest $\sigma$-algebra which makes the $f_j$ measurable, and independent of any finite subset of the $f_j$.
+	Suppose $\Omega$ is a standard Borel space with a probability measure $P$ and that $\left(f_i: \Omega \to X_i\right)_{i \in \bN}$ is a sequence of independent random variables taking values in standard Borel spaces $X_i$.
+Suppose that $T \subseteq \Omega$ is in the coarsest $\sigma$-algebra which makes the $f_i$ measurable, and independent of any finite subset of the $f_i$.
 Then $P(T) \in \{0,1\}$.
@@
 Then $P : I \to \Omega$.
-We write $f_\bN : \Omega \to X_\bN$ for the induced map to the product.
+We write $f_\bN : \Omega \to X_\bN$ for the induced map to the product measurable space.
 In $\Omega$, the coarsest $\sigma$-algebra which makes the $f_i$ measurable coincides with the $\sigma$-algebra consisting of the sets of the form $f_\bN^{-1}(S)$ for measurable $S \subseteq X_J$.
 Hence the assumption implies that there is measurable $S \subseteq X_J$ such that $T = f_\bN^{-1}(S)$.
-Then we apply \Cref{thm:kolmog} with $s : X_J \to \{0,1\}$ the indicator function of $S$, which is a measurable map and therefore can also be regarded as a morphism in $\BorelStoch$, and $p = f_\bN P$.
+Then we apply \Cref{thm:kolmog} with $s : X_J \to \{0,1\}$ the indicator function of $S$, which is a measurable map and therefore can also be regarded as a morphism in $\BorelStoch$, and with $p = f_\bN P$.
 We therefore obtain that $sp : I \to \{0,1\}$ is deterministic.
@@
 \begin{problem}
-	Is there a Markov category $\cC$ with countable Kolmogorov products such that \Cref{thm:kolmog} specializes to the standard Kolmogorov zero--one law in its general form?
+	Is there a Markov category $\cC$ with countable Kolmogorov products such that \Cref{thm:kolmog} specializes to the standard Kolmogorov zero--one law in its general form applicable to all measurable spaces?
 \end{problem}
@@
 \begin{corollary}[Hewitt-savage zero--one law]
-    Suppose $\Omega$ is a standard Borel space with probability measure $P$, and let $\left(f_j: \Omega \to X\right)_{j\in \bN}$ be a sequence of independent, identically distributed random variables taking values in a standard Borel space $X$.
-    Suppose $S \subset \prod_{j \in \bN} X = X_\bN$ is measurable in the product $\sigma$-algebra, and suppose moreover that, for each finite permutation $\alpha: \bN \to \bN$, $\hat{\alpha}(S) = S$ (in other words, $S$ is invariant under finite permutations of the variables).
-    Then $P(f_\bN\inv(S)) \in \{0,1\}$ - here $f_\bN$ again denotes the induced map $\Omega \to X_\bN.$
+    Suppose $\Omega$ is a standard Borel space with probability measure $P$, and let $\left(f_i: \Omega \to X\right)_{i\in \bN}$ be a sequence of independent, identically distributed random variables taking values in a standard Borel space $X$.
+    Suppose $S \subseteq \prod_{i \in \bN} X = X_\bN$ is measurable in the product $\sigma$-algebra, and suppose moreover that, for each finite permutation $\sigma: \bN \to \bN$, we have $\hat{\sigma}(S) = S$ (in other words, $S$ is invariant under finite permutations of the variables).
+    Then $P(f_\bN\inv(S)) \in \{0,1\}$, where $f_\bN$ again denotes the induced map $\Omega \to X_\bN$.
 \end{corollary}
@@
     As before, we let $s: X_\bN \to \{0,1\}$ be the indicator function of $S$, and we let $p = f_\bN P$.
-    The i.i.d assumption on the $f_j$ implies that $\hat{\alpha}p = p$, and the assumption on $S$ implies $s\hat{\alpha} = s$ for finite permutations $\alpha$.
-    Hence we can apply \Cref{thm:hewsav}. This again implies that the map $sp: I \to \{0,1\}$ is deterministic, which, just as before, means 
-    $P(f_\bN\inv(S))$ is either $0$ or $1$.
+    The i.i.d.~assumption on the $f_j$ implies that $\hat{\sigma}p = p$, and the assumption on $S$ implies $s\hat{\sigma} = s$ for finite permutations $\sigma$.
+    Hence we can apply \Cref{thm:hewsav}. This again shows that the map $sp: I \to \{0,1\}$ is deterministic, which, just as before, means $P(f_\bN\inv(S)) \in \{0,1\}$.
 \end{proof}
@@
 By interpreting these results in different Markov categories, we can obtain other results.
-As a simple example, we can consider the following Markov category:
+In particular, the following example is of a similar flavour as $\SetMulti$, but improves on its lack of infinite tensor products (\Cref{setmulti}).
 
-\begin{definition}
-    Consider the hyperspace monad on $\Top$ defined in \cite[Definition~2.4]{hyperspace}.
-    The Kleisli category associated to this monad is denoted $\Kl(H)$.
-    Using \cite[Corollary~2.53]{hyperspace} and \cite[Proposition~3.1]{markov_cats}, this is a Markov category.
+With $\Top$ the category of topological spaces and continuous maps, we consider the \emph{lower Vietoris monad} or \emph{hyperspace monad} $H$ on $\Top$, introduced by Schalk for $T_0$ spaces~\cite{schalk} and investigated generally in~\cite[Section~2]{hyperspace}.
+Let $\Kl(H)$ be its Kleisli category.
+Using the symmetric monoidal structure of $H$ guaranteed by~\cite[Corollary~2.53]{hyperspace}, the general construction of Markov categories from symmetric monoidal monads of \cite[Proposition~3.1]{markov_cats} turns $\Kl(H)$ into a Markov category.
 Concretely, this category has the following structure:
@@
         \item The objects are topological spaces.
-        \item A morphism $f: X \to Y$ consists of a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subset Y \text{ closed} \mid V \cap U \neq \emptyset\}$ for $U \subset Y$ open.
-        \item Composition is defined as in $\SetMulti$, by the closure of the union.
-        \item The monoidal product is the Cartesian product of topological spaces, and $(f \tensor g)(x_1,x_2) = f(x_1) \times g(x_2)$.
+	\item A morphism $f: X \to Y$ is a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subseteq Y \text{ closed} \mid V \cap U \neq \emptyset\}$, where $U \subseteq Y$ ranges over all opens.
+	\item Composition is defined as in $\SetMulti$ via~\eqref{relational_composition}, but taking the closure of the union in addition.
+        \item The monoidal product is the Cartesian product of topological spaces, and on morphisms
+		\[
+			(f \tensor g)(x_1,x_2) := f(x_1) \times g(x_2),
+		\]
+		exactly as in $\SetMulti$.
         \item The comultiplication is defined by $\cop{X}(x) = \cl(\{(x,x)\})$
     \end{enumerate}
-\end{definition}
 \begin{proposition}
-    $\Kl(H)$ has Kolmogorov products of any cardinality, given simply by the ordinary infinite product of topological spaces in the product topology.
+    $\Kl(H)$ has Kolmogorov products of any cardinality, given by the usual infinite product of topological spaces with the product topology.
 \end{proposition}
@@
     First we observe that $H(\prod_{j\in J} X_j)$ is the cofiltered limit of the spaces
-    $H(\prod_{j\in F} X_j)$.
+    $H(\prod_{j\in F} X_j)$ for $F \subseteq J$ finite.
     To see this, note that the marginalizations induce a continuous map
-    \[\alpha: H(\prod_{j\in J} X_j) \to \lim_{F \subset J} H(\prod_{j \in J} X_j)\]
-    This is an injection - given distinct closed subsets $V, W \subset \prod X_j$, and let $x \in V \setminus W$.
-    Then let $U \ni x$ be an open neighborhood of $x$ not intersecting $W$.
-    Since $U$ is open in the product topology, we can find some finite subset $F \subset J$ so that 
-    \[y = (y_j) \in U \Leftrightarrow y_j \in \pi_j(U) \text{ for $j\in F$}\]
-    Then $\pi_F(x) \in \pi_F(U)$, which is disjoint from $\pi_F(W)$. Hence $\alpha(V) \neq \alpha(W)$.
+    	\[
+		\alpha \: : \: H\!\left(\prod_{i\in J} X_i\right) \longrightarrow \lim_{F \subseteq J} \, H\!\left(\prod_{i \in J} X_i\right)
+	\]
+	We show that this is an injection.
+Thus we start with distinct closed subsets $C, D \subseteq \prod X_i$.
+We assume without loss of generality that $C \not\subseteq D$, and choose $x \in C \setminus D$.
+    Then let $U \ni x$ be an open neighborhood of $x$ not intersecting $D$.
+    Since $U$ is open in the product topology, we can assume that there is some finite subset $F \subset J$ so that 
+    	\[
+		y = (y_i) \in U \quad\Longleftrightarrow\quad y_i \in \pi_i(U) \:\;\forall i\in F.
+	\]
+    Then $\pi_F(x) \in \pi_F(U)$, which is disjoint from $\pi_F(D)$. Hence $\alpha(C) \neq \alpha(D)$.
 
-    It is also a surjection - given a family $(V_F) \in \lim H(\prod_{j \in J} X_j)$, simply set
-    \[V = \{x \in \prod_{j\in J} X_j \mid  \pi_F(x) \in V_F \forall F\}\]
-    This is an intersection of closed subsets, hence closed, and it is clearly sent to $(V_F)$.
+    We show that $\alpha$ is also surjective. Given a family $(C_F) \in \lim_F H\!\left(\prod_{i \in F} X_i\right)$, simply set
+	\[
+		C = \left\{x \in \prod_{j\in J} X_j \:\Bigg|\: \pi_F(x) \in C_F \:\: \forall F\right\}
+	\]
+	This is an intersection of closed subsets, hence closed, and the finite marginalizations clearly send it to the given family $(C_F)$.
 
-    Finally, we must verify that it's open.
-    It suffices to show that it carries subbasis open sets $A_U = \{V \subset \prod X_j \text{ closed} \mid V \cap U \neq \emptyset\}$ to open subsets of the limit.
-    Again, given such a $U$, we find a finite $F$ so that
-    \[y = (y_j) \in U \Leftrightarrow y_j \in \pi_j(U) \text{ for $j\in F$}\]
-    then \[\alpha(A_U) = \pi_F\inv(\{V \subset \prod_{j \in F} X_F \text{ closed} \mid V \cap \pi_F(U) \neq \emptyset\})\]
-    and this is open in the limit.
+	Finally, we must verify that $\alpha$ is an open map.
+	It suffices to show that it carries a subbasic open set $\mathrm{Hit}(U) = \{C \subseteq \prod X_i \text{ closed} \mid C \cap U \neq \emptyset\}$ to an open subset of the limit.
+For a given point $C \in \mathrm{Hit}(U)$, it is enough to find an open neighborhood contained in $\mathrm{Hit}(U)$.
+But then by making $U$ smaller if necessary, we can assume without loss of generality that $U$ is a basic open in the product topology, meaning that there is a finite $F$ so that
+	\[
+		y = (y_i) \in U \quad\Longleftrightarrow\quad y_i \in \pi_i(U) \:\; \forall i \in F.
+	\]
+    Then
+	\[
+		\alpha(A_U) = \pi_F\inv\left(\left\{V \subseteq \prod_{j \in F} X_F \text{ closed} \:\Bigg|\: V \cap \pi_F(U) \neq \emptyset\right\}\right),
+	\]
+    which is indeed open in the limit.
 
-    It follows that $\prod_j X_j$ is an infinite tensor product in $\Kl(H)$ - the preservation condition is easily verified.
+    It follows that $\prod_i X_i$ is an infinite tensor product in $\Kl(H)$; the preservation condition is easily verified since adding another factor to this product again gives the infinite product.
 The Kolmogorov product condition is similarly immediate to verify.
 \end{proof}
+
+We can therefore instantiate our \Cref{thm:kolmog,thm:hewsav} in $\Kl(H)$, which gives the following results as special cases.
+
 \begin{corollary}
-    Let $(X_j)_{j \in J}$ be a family of topological spaces, $Y$ a Hausdorff space, and let $f: \prod_j X_j \to Y$ be a continuous function
-    which is independent of any finite prefix of the input.
-    Then the map $f$ is constant.
+    Let $(X_i)_{i \in J}$ be a family of topological spaces, $Y$ a Hausdorff space, and let $f: \prod_i X_i \to Y$ be a continuous function
+    which is independent of any finite subset of the input.
+    Then $f$ is constant.
+    \label{vietoris_kolmogorov}
 \end{corollary}
 \begin{corollary}
-	Let $X$ be a topological space, $Y$ a Hausdorff space, $J$ an infinite set, and let $f: \prod_{j\in J} X \to Y$ be a continuous function which is invariant under any finite permutation of the inputs.
+	Let $X$ be a topological space, $Y$ a Hausdorff space, $J$ an infinite set, and let $f: \prod_{i\in J} X \to Y$ be a continuous function which is invariant under any finite permutation of the inputs.
     Then $f$ is constant.
+    \label{vietoris_hewitt_savage}
 \end{corollary}
 \begin{proof}[Proof of both]
-	These results follow from \Cref{thm:kolmog,thm:hewsav} appliedto $\Kl(H)$.
-	using the morphisms $p : I \to X_J$ corresponding to the trivial closed subset $X_J \subseteq X_J$.
-    The conclusion is that the closure of the image, call it $A$, has the following property: $\cl(\{(a,a) \mid a \in A\}) = A \times A$ as subsets of $Y \times Y$.
+	These results follow from \Cref{thm:kolmog,thm:hewsav} applied to $\Kl(H)$,
+	using the morphism $p : I \to X_J$ corresponding to the trivial closed subset $X_J \subseteq X_J$.
+	The conclusion is that the closure of its image, call it $A$, satisfies
+	\[
+		\cl(\{(a,a) \mid a \in A\}) = A \times A
+	\]
+	as subsets of $Y \times Y$.
     But since the diagonal is closed in $Y$, this clearly implies that $A$ must be a singleton.

### 2019-12-03 categorical-zero-one.tex
Push argument for causality of Kl(H)

@@
 \end{proof}
+\begin{proposition}
+    $\Kl(H)$ is causal.
+\end{proposition}
+\begin{proof}
+    We are given spaces $A, X, Y, Z$, and continuous maps $f:A \to HX, g: X \to HY, h_1,h_2: Y \to HZ$.
+    We assume that two maps $X \to H(W \times Z)$ are equal.
+    They are given by
+    \[a \mapsto \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_1(y) \times \{y\}\right),\ x \mapsto \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_2(y) \times \{y\}\right)\]
+    Of course, equality of these maps simply means that the right-hand sides agree for each $x$.
+
+    Let us rewrite and name this set as
+    \[S := \cl\left(\{(z,y) \mid z \in h_1(y), y \in \cup_{x \in f(a)} g(x)\}  \right) = \cl\left(\{(z,y) \mid z \in h_2(y), y \in \cup_{x \in f(a)} g(x)\}  \right) \]
+
+    The desired conclusion is that the sets
+    \[\cl\left(\bigcup_{x \in f(a), y \in g(x)} h_1(y) \times \{y\} \times \{x\}\right),\ \cl\left(\bigcup_{x \in f(a), y \in g(x)} h_2(y) \times \{y\} \times \{x\}\right)\]
+    agree. Let us rewrite them as
+    \[\cl\left(\{(z,y,x) \mid z \in h_1(y), y\in g(x), x\in f(a)\}\right),\ \cl\left(\{(z,y,x) \mid z \in h_2(y), y\in g(x), x\in f(a)\}\right)\]
+
+    To show this identity, it suffices to show that 
+    \[\{(z,y,x) \mid z \in h_1(y), y\in g(x), x\in f(a)\} \subseteq \cl\left(\{(z,y,x) \mid z \in h_2(y), y\in g(x), x\in f(a)\}\right)\]
+    (and the converse inclusion).
+
+    Let us take a point $(z_0,y_0,x_0)$ left-hand set, and consider an open neighborhood $U_1 \times U_2 \times U_3$, for open subsets of $Z,Y,X$ respectively.
+    Our goal is to construct $(z,y,x) \in U_1\times U_2 \times U_3$ so that $x \in f(a), y \in g(x), z \in h_2(y)$.
+
+    The assumptions on $(z_0,y_0,x_0)$ implies that the point $(z_0,y_0)$ is in $S$.
+    Hence by the other expression of $S$, we can find a point $x$ so that $x \in f(a), y_0 \in g(x) \cap U_2, z_0 \in h_2(y_0) \cap U_1$.
+    The issue is now to fix this so that $x \in f(a) \cap U_3$.
+
+    Consider the set $\{y \mid h_2(y) \cap U_1 \neq \emptyset\}$.
+    This is an open set which contains our $y_0$ above. Let $U_2'$ be the (nonempty!) intesection of this set with $U_2$.
+    Now consider $\{x \mid g(x) \cap U_2' \neq \emptyset\}$. This is again an open set which cantains $x_0$. Let $U_3'$ be the intersection of this with $U_3$.
+    Now since $x_0 \in f(a)$, any open neighborhood of $x_0$ intersects $f(a)$ (since it's closed).
+    So choose $x_1 \in f(a) \cap U_3', y_1 \in U_2' \cap g(x) \cap U_2',$ and finally $z_1 \in h_2(y) \cap U_1$.
+    (Each possible by the construction of the previous element). By construction we have $(z_1,y_1,x_1) \in U_1 \times U_2 \times U_3$, exactly as desired.
+    The other inclusion follows by a symmetric argument.
+\end{proof}
 

### 2019-12-04 categorical-zero-one.tex
add lemma, fix minor error in proof of causality

@@
 \end{proof}
-\begin{proposition}
+\begin{proposition}\label{prop:klh-causal}
     $\Kl(H)$ is causal.
 \end{proposition}
+The proof of this proposition is fairly technical and not very illuminating. We recommend skipping to \Cref{vietoris_kolmogorov} below on a first reading.
+We will use the notation of \cite{hyperspace} through the proof.
+
+First, we will need a quick lemma.
+\begin{lemma}\label{lem:extraclosure}
+    Let $f: X \to HY$ and $g: Y \to HZ$ be continuous functions
+    Consider the map $HX \to HZ$ given by composing $f$ and $g$ in $\Kl(H)$, yielding a map $X \to HZ$, then lifting this using the monad structure.
+    By definition, this map sends a closed $A \subset X$ to
+    \[\cl \left(\bigcup_{a \in A} \cl\left(\bigcup_{b \in f(a)} g(b)\right)\right)\]
+
+    In fact, this equals \[\cl\left(\bigcup_{a \in A}\bigcup_{b \in f(a)} g(b)\right)\]
+\end{lemma}
+The point of this lemma is that the iterated closures that arise when composing maps in $\Kl(H)$ can be mostly ignored, although we do have to take a closure at the end.
 \begin{proof}
+    Let $\hat{f},\hat{g}$ denote the induced maps $HX \to HY, HY \to HZ$.
+    Since both of the sets we are comparing are closed, it suffices to show that they intersect the same collection of open sets.
+    We use the notation $\braket{U,V}$ from \cite{hyperspace}, which is defined for two subsets of the same space to be $1$ if they intersect and $0$ otherwise.\footnote{we generalize slightly and use this notation even when $V$ is not closed, although $U$ is still always open.}
+
+    Now we calculate, for a given open $U \subset Z$
+    \[\braket{U , \hat{g}(\hat{f}(A))} = \braket{U , \cl(\cup_{y \in \hat{f}(A)}g(y))} = \braket{ U, \cup_{y \in \hat{f}(A)}g(y)}\]
+    Here we first insert the definition of $\hat{g}$, then use the fact that $U$ is open.
+
+    Now the statement that this union intersects $U$ means just that at least one of the sets in the union does.
+    So we get
+    \[=\braket{g\inv(\Hit(U)) , \hat{f}(A)}\]
+    Note that $g\inv(\Hit(U))$ is still an open set, by continuity.
+    Applying these arguments again, we find
+    \[=\braket{f\inv(\Hit(g\inv(\Hit(U)))) , A} = \braket{\Hit(g\inv(\Hit(U))) , f(A)}\]
+    where $f(A) \subset HY$ is simply the direct image of $A$.
+    The statement that $f(A)$ intersects $\Hit(g\inv(\Hit(U)))$ means that for at least one $a\in A$, $f(a)$ is in $\Hit(g\inv(\Hit(U)))$, i.e it intersects $g\inv(\Hit(U))$.
+    So we can pass to
+    \[= \braket{g\inv(\Hit(U)) , \cup_{x \in A} f(x)}\]
+    And by the same argument, to
+    \[= \braket{U , \cup_{x \in A}\cup_{y\in f(x)}g(x)} = \braket{U , \cl \cup_{x \in A}\cup_{y\in f(x)}g(x)}\]
+    which is exactly what we wanted.
+\end{proof}
+
+\begin{proof}[Proof of \Cref{prop:klh-causal}]
     We are given spaces $A, X, Y, Z$, and continuous maps $f:A \to HX, g: X \to HY, h_1,h_2: Y \to HZ$.
@@
     Of course, equality of these maps simply means that the right-hand sides agree for each $x$.
+    Here we have implictly used \Cref{lem:extraclosure} to get rid of extra closures.
 
@@
     \[\cl\left(\{(z,y,x) \mid z \in h_1(y), y\in g(x), x\in f(a)\}\right),\ \cl\left(\{(z,y,x) \mid z \in h_2(y), y\in g(x), x\in f(a)\}\right)\]
+    (Where we have again used \Cref{lem:extraclosure}).
 
@@
 
-    Let us take a point $(z_0,y_0,x_0)$ left-hand set, and consider an open neighborhood $U_1 \times U_2 \times U_3$, for open subsets of $Z,Y,X$ respectively.
+    Let us take a point $(z_0,y_0,x_0)$ in the left-hand set, and consider an open neighborhood $U_1 \times U_2 \times U_3$, for open subsets of $Z,Y,X$ respectively.
     Our goal is to construct $(z,y,x) \in U_1\times U_2 \times U_3$ so that $x \in f(a), y \in g(x), z \in h_2(y)$.
@@
     The assumptions on $(z_0,y_0,x_0)$ implies that the point $(z_0,y_0)$ is in $S$.
-    Hence by the other expression of $S$, we can find a point $x$ so that $x \in f(a), y_0 \in g(x) \cap U_2, z_0 \in h_2(y_0) \cap U_1$.
+    Hence by the other expression of $S$, we can find points $x_1,y_1,z_1$ so that $x_1 \in f(a), y_1 \in g(x) \cap U_2, z_1 \in h_2(y_1) \cap U_1$.
     The issue is now to fix this so that $x \in f(a) \cap U_3$.
@@
     Consider the set $\{y \mid h_2(y) \cap U_1 \neq \emptyset\}$.
-    This is an open set which contains our $y_0$ above. Let $U_2'$ be the (nonempty!) intesection of this set with $U_2$.
-    Now consider $\{x \mid g(x) \cap U_2' \neq \emptyset\}$. This is again an open set which cantains $x_0$. Let $U_3'$ be the intersection of this with $U_3$.
-    Now since $x_0 \in f(a)$, any open neighborhood of $x_0$ intersects $f(a)$ (since it's closed).
-    So choose $x_1 \in f(a) \cap U_3', y_1 \in U_2' \cap g(x) \cap U_2',$ and finally $z_1 \in h_2(y) \cap U_1$.
-    (Each possible by the construction of the previous element). By construction we have $(z_1,y_1,x_1) \in U_1 \times U_2 \times U_3$, exactly as desired.
+    This is an open set which contains our $y_1$ above. Let $U_2'$ be the (nonempty!) intesection of this set with $U_2$.
+    Now consider $\{x \mid g(x) \cap U_2' \neq \emptyset\}$. This is again an open set which contains $x_1$. Let $U_3'$ be the intersection of this with $U_3$.
+    Now since $x_1 \in f(a)$, any open neighborhood of $x_1$ intersects $f(a)$ (since it's closed).
+    So choose $x_2 \in f(a) \cap U_3', y_2 \in U_2' \cap g(x_2) \cap U_2',$ and finally $z_2 \in h_2(y_2) \cap U_1$.
+    (Each possible by the construction of the previous element). By construction we have $(z_2,y_2,x_2) \in U_1 \times U_2 \times U_3$, exactly as desired.
     The other inclusion follows by a symmetric argument.

### 2019-12-04 categorical-zero-one.tex
take out todo remark about spaces
removed wrong proof, added counterexample

--- 2019-11-23 categorical-zero-one.tex
@@
 
-\todo[inline]{E: Not sure these examples (about top.
-spaces) are that great..
-it seems like we do an inordinate amount of work to get the infinite tensor products, compared to the results.
-What do you think?}
-
 By interpreting these results in different Markov categories, we can obtain other results.
@@
 
-We can therefore instantiate our \Cref{thm:kolmog,thm:hewsav} in $\Kl(H)$, which gives the following results as special cases.
+We can therefore instantiate our \Cref{thm:kolmog} in $\Kl(H)$, which gives the following result as a special case.
 
@@
 \end{corollary}
-\begin{corollary}
-	Let $X$ be a topological space, $Y$ a Hausdorff space, $J$ an infinite set, and let $f: \prod_{i\in J} X \to Y$ be a continuous function which is invariant under any finite permutation of the inputs.
-    Then $f$ is constant.
-    \label{vietoris_hewitt_savage}
-\end{corollary}
-\begin{proof}[Proof of both]
-	These results follow from \Cref{thm:kolmog,thm:hewsav} applied to $\Kl(H)$,
+\begin{proof}
+	These results follow from \Cref{thm:kolmog} applied to $\Kl(H)$,
     using the morphism $p : I \to X_J$ corresponding to the trivial closed subset $X_J \subseteq X_J$.
@@
 \end{proof}
+
+However, we cannot instantiate the Hewitt-Savage 0-1 law, because $\Kl(H)$ is not in fact causal, as the following example shows.
+\begin{example}
+    Let $A = \{*\}, X = Y = Z = [0,1]$.
+    Let $f: A \to HX$ send $*$ to $X$, and define
+\begin{equation}
+g(x) =  \begin{cases} [0,1/2] & x < \frac{1}{3}\\ \{1/2\} & \frac{1}{3} < x < \frac{2}{3}\\ [1/2,1] & x > \frac{1}{2}\end{cases}
+\end{equation}
+\begin{equation}
+h_1(y) = [0,1]
+\end{equation}
+\begin{equation}
+h_2(y) = \begin{cases}[0,1] & y \neq \frac{1}{2}\\ \{0\} &  y = \frac{1}{2}\end{cases}\end{equation}
+
+One can verify that these are indeed continuous maps.
+To check the hypothesis of the statement of causality, we must verify that two maps $A \to Y \times Z$ agree - these are just closed subsets of $[0,1]^2$
+From the definition of the composition, we see that any point $(y,z)$ with $y \in g(x)$ for some $x$ and $z \in h_1(y)$ must lie in the set corresponding to $h_1$,
+and similarly for $h_2$.
+Hence the set corresponding to $h_1$ contains all points, while the set corresponding to $h_2$ contains all points with $y \neq 1/2$.
+But the closure of $\{(y,z) \mid y \neq 1/2}$ in $[0,1]^2$ is everything, so both sets must equal the whole space.
+
+Hence the hypothesis is satisfied.
+But one can verify that the point $(x,y,z) = (1/2,1/2,1)$ is in the subset of $X \times Y \times Z$ corresponding to $h_1$, but not $h_2$.
+\end{example}
 

### 2019-12-04 categorical-zero-one.tex
bugfix
revised example, added open problem

@@
 % draft packages
-\usepackage{todonotes}
-\usepackage{showkeys}
+%\usepackage{todonotes}
+%\usepackage{showkeys}
 
@@
 	holds for morphisms as indicated, then also
-	\[
+	\begin{equation}
+		\label{causal2}
 		\tikzfig{causal2}
-	\]
+	\end{equation}
 	\label{causal_defn}
@@
     Of course, $\sf{Set}$ has all infinite products. But perhaps surprisingly, these products are not Kolmogorov products, or even infinite tensor products in $\sf{SetMulti}$.
-    \todo[inline]{T: I think we shouldn't use our $X_J$ notation in the following example, precisely because we don't have infinite tensor products}
     To see this, consider for example the family $(X_n)_{n\in\bN}$ with $X_n = \{0,1\}$ for all $n$. 
@@
 
-However, we cannot instantiate the Hewitt-Savage 0-1 law, because $\Kl(H)$ is not in fact causal, as the following example shows.
+However, we cannot instantiate the Hewitt-Savage zero--one law in $\Kl(H)$, since this Markov category is in fact not causal, as the following example shows.
+
 \begin{example}
-    Let $A = \{*\}, X = Y = Z = [0,1]$.
+	Let $A = \{*\}$ and $X = Y = Z = [0,1]$ with the usual topology.
     Let $f: A \to HX$ send $*$ to $X$, and define
-\begin{equation}
-g(x) =  \begin{cases} [0,1/2] & x < \frac{1}{3}\\ \{1/2\} & \frac{1}{3} < x < \frac{2}{3}\\ [1/2,1] & x > \frac{1}{2}\end{cases}
-\end{equation}
-\begin{equation}
-h_1(y) = [0,1]
-\end{equation}
-\begin{equation}
-h_2(y) = \begin{cases}[0,1] & y \neq \frac{1}{2}\\ \{0\} &  y = \frac{1}{2}\end{cases}\end{equation}
-
-One can verify that these are indeed continuous maps.
-To check the hypothesis of the statement of causality, we must verify that two maps $A \to Y \times Z$ agree - these are just closed subsets of $[0,1]^2$
+    \[g(x) :=  \begin{cases} [0,1/2] & x < \frac{1}{3}\\ \{1/2\} & \frac{1}{3} < x < \frac{2}{3}\\ [1/2,1] & x > \frac{1}{2}\end{cases}\]
+    \[
+    	h_1(y) := [0,1], \qquad h_2(y) = \begin{cases}[0,1] & y \neq \frac{1}{2}\\ \{0\} &  y = \frac{1}{2}\end{cases}
+    \]
+    Using the definition of the hyperspace topology, it is straightforward to see that these maps are continuous.
+To check the hypothesis of the statement of causality, we must verify that the resulting two maps $A \to Y \times Z$ agree; these are just closed subsets of $[0,1]^2$.
 From the definition of the composition, we see that any point $(y,z)$ with $y \in g(x)$ for some $x$ and $z \in h_1(y)$ must lie in the set corresponding to $h_1$,
@@
 Hence the set corresponding to $h_1$ contains all points, while the set corresponding to $h_2$ contains all points with $y \neq 1/2$.
-But the closure of $\{(y,z) \mid y \neq 1/2}$ in $[0,1]^2$ is everything, so both sets must equal the whole space.
+But the closure of $\{(y,z) \mid y \neq 1/2\}$ in $[0,1]^2$ is the whole space, so that both sets are indeed equal to the whole space.
 
 Hence the hypothesis is satisfied.
-But one can verify that the point $(x,y,z) = (1/2,1/2,1)$ is in the subset of $X \times Y \times Z$ corresponding to $h_1$, but not $h_2$.
+But one can verify that the point $(x,y,z) = (1/2,1/2,1)$ is in the subset of $X \times Y \times Z$ corresponding to the $h_1$ side of \eqref{causal2}, but not so for the $h_2$ side.
 \end{example}
+
+We end with an open problem.
+
+\begin{problem}
+	Find an interesting causal Markov category which has all Kolmogorov products.
+\end{problem}
+
+Strangely enough, the only example that we know of so far are monoidal posets, namely the finitary complete monoids of \Cref{poset_case}.
+For these, the causality axiom holds trivially since any two parallel morphisms are equal.
 

### 2019-12-06 categorical-zero-one.tex
cartesian monoidal cats and Problem 6.7

@@
 
-Strangely enough, the only example that we know of so far are monoidal posets, namely the finitary complete monoids of \Cref{poset_case}.
-For these, the causality axiom holds trivially since any two parallel morphisms are equal.
+Strangely enough, the only examples that we know of so far are of two kinds: first, cartesian monoidal categories (meaning that $\cC = \cC_\det$) with all products; and second, the finitary complete monoids of \Cref{poset_case} which are monoidal posets.
+For the former, the universal property of the monoidal structure implies that the causality axiom holds.
+For the latter, it holds trivially since any two parallel morphisms are equal.
 

### 2019-12-07 categorical-zero-one.tex
minor fixes

--- 2019-12-04 categorical-zero-one.tex
@@
 This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts.
-For example, applying them to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.
+For example, applying the Kolmogorov law to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.
 \end{abstract}
@@
 We thereby rederive the standard zero--one laws for random variables in standard Borel spaces from our abstract theorems.
-We also instantiate our theorems in the Kleisli category of the lower Vietoris monad, which gives criteria for when a continuous map out of infinite product of topological spaces into a Hausdorff space is constant (\Cref{vietoris_kolmogorov} and \Cref{vietoris_hewitt_savage}).
+We also instantiate one of our theorems in the Kleisli category of the lower Vietoris monad, which gives criteria for when a continuous map out of infinite product of topological spaces into a Hausdorff space is constant (\Cref{vietoris_kolmogorov}).
 

### 2020-01-10 categorical-zero-one.tex
typo

@@
 	In conclusion, $\BorelStoch$ indeed has countable tensor products.
-It is plausible that there is is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there also is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
+It is plausible that there is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there also is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
 However, we have so far not been able to find a suitable condition on Markov kernels which would guarantee closure under composition, due to problems with perfect measures not being stable under mixtures~\cite{ramachandran}.

### 2020-05-03 categorical-zero-one.tex
acknowledged Kenta
Some rev1 edits, added list file

@@
 
-\paragraph*{Acknowledgments.} We thank Paolo Perrone for discussions and \Cref{poset_case}.
+\paragraph*{Acknowledgments.} We thank Paolo Perrone for discussions and \Cref{poset_case} as well as Kenta Cho for comments on an earlier version of this paper.
 
@@
 \]
-The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $\discard{Y} \otimes \id : X \otimes Y \to Y$, which are the ones from~\eqref{projections}, are correspondingly written as
+The projection maps $\id \otimes \discard{Y} : X \otimes Y \to X$ and $\discard{X} \otimes \id : X \otimes Y \to Y$, which are the ones from~\eqref{projections}, are correspondingly written as
 \[
@@
 
-It is known that $\Stoch$ is causal~\cite[Example~11.34]{markov_cats}, and therefore so are the subcategories $\BorelStoch$ and $\FinStoch$.
-We do not know whether $\CRing_+\op$ is causal, although we suspect that~\cite[Example~11.31]{markov_cats} can be modified to show that it is not.
+It is known that $\Stoch$ is causal~\cite[Example~11.34]{markov_cats}, and
+therefore so are the subcategories $\BorelStoch$ and $\FinStoch$.
+\todo[inline]{Added as per reviewer's suggestion, but unsure if it's a good
+  inclusion or not.}
+\begin{example}
+$\CRing_{+}^{\op}$ is \emph{not} causal.
+To see this, consider the ring $\mathbb{Z}[\epsilon]/(\epsilon^{2})$.
+Elements have the form $a + b\epsilon$, with $a,b\in\bZ$, and multiplication is
+defined by the convention $\epsilon^{2} = 0$.
+Consider the additive maps given by
+\begin{equation}
+  f(a + b\epsilon) = & b\\
+  g(a + b \epsilon) = & b\\
+  h_{1}(a+ b \epsilon) = & a + b \epsilon\\
+  h_{2}(a + b \epsilon) = & 0
+\end{equation}
+Since $gf = 0$, it's clear that the hypothesis holds, so if $\CRing_{+}^{\op}$
+were causal, we would have the equation
+$g(f(h_{1}(x)y)z) = g(f(h_{2}(x)y)z)$ for all
+$x,y,z \in \bZ[\epsilon]/(\epsilon^{2})$.
+However, this clearly fails if $z = \epsilon$, $y=1$ and $x = \epsilon$.
+\end{example}
 
@@
 	\label{defnasequal}
-	Given morphisms $p : A \to X$ and $f,g : X \to Y$ in a Markov category, we say that $f$ and $g$ are \emph{$p$-a.s.~equal} if
+	Given morphisms $p : A \to X$ and $f,g : X \to Y$ in a Markov category, we
+    say that $f$ and $g$ are \emph{$p$-a.s.~equal} (or $p$-\emph{almost surely}.~equal) if
 	\[
@@
   \end{definition}
+
+  This term comes from measure theory, and should be interpreted as meaning
+  ``for all $a\in A$, if $x \in X$ is sampled according to $p(a)$, the
+  probability that $f(x) \neq g(x)$ is zero''.
 
@@
 
-Using the multiplicativity of the comonoid structure of~\eqref{multiplicativity}, we see that \Cref{two_infproducts,infprod_operadic} hold also for Kolmogorov products.
+Using the multiplicativity of the comonoid structure
+of~\eqref{multiplicativity}, we see that \Cref{two_infproducts,infprod_operadic}
+hold also for Kolmogorov products, in the sense that tensoring together
+Kolmogorov products, or taking Kolmogorov products of Kolmogorov products, results
+again in a Kolmogorov product.
 
@@
 
-In particular, this proves that \Cref{defn_kolmogorov_ext} determines the comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_i X_i}$ has to be the equal to the corresponding diagonal in $\cC_\detc$, and \Cref{kolmprod_catdet} determines $\bigotimes_i X_i$ up to \emph{deterministic} isomorphism.
+In particular, this proves that \Cref{defn_kolmogorov_ext} determines the
+comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_i X_i}$
+has to be the equal to the corresponding diagonal in $\cC_\detc$, and
+\Cref{kolmprod_catdet} determines $\bigotimes_i X_i$ up to \emph{deterministic}
+isomorphism.
 
@@
       \end{equation}
+    $\SetMulti$ could also be described as the Kleisli category of the
+    \emph{nonempty powerset monad}, which sends a set $X$ to $\cP(X) \setminus \emptyset$.
+
     See also \cite[Example~2.6]{markov_cats} for a treatment of the full subcategory $\FinSetMulti$ on finite sets.
@@
 \begin{lemma}[The infinite independence lemma]
+  \label{infindeplemma}
 	Suppose $p: A \to X_J$ displays the conditional independence $\perp_i X_i \mid\mid A$.
@@
     displays the conditional independence $\perp_{i \in J\,\sqcup\,\{\ast\}} X_i \mid\mid A$.
-    By the infinite independence lemma, this means that it also displays the conditional independence $X_\ast \perp X_J \mid\mid A$.
+    By the infinite independence lemma, \cref{infindeplemma}, this means that it also displays the conditional independence $X_\ast \perp X_J \mid\mid A$.
     Now the determinism lemma implies exactly what we want, namely that the composite $sp : A \to T$ is deterministic.
@@
 
+We note that the standard Kolmogorov zero--one law holds for any measurable
+spaces, not just for standard Borel spaces - hence this is a strictly less
+general statement. As discussed in \cref{infprods_stoch}, it seems unlikely that
+the general statement can be proven by applying our machinery to the category
+$\Stoch$ of measurable spaces and Markov kernels. This leads to the following problem:
+
 \begin{problem}
@@
   \end{corollary}
+
 \begin{proof}
@@
     Let $f: A \to HX$ send $*$ to $X$, and define
-    \[g(x) :=  \begin{cases} [0,1/2] & x < \frac{1}{3}\\ \{1/2\} & \frac{1}{3} < x < \frac{2}{3}\\ [1/2,1] & x > \frac{1}{2}\end{cases}\]
+    \[g(x) :=  \begin{cases} [0,1/2] & x < \frac{1}{3}\\ \{1/2\} & \frac{1}{3} \leq x \leq \frac{2}{3}\\ [1/2,1] & x > \frac{1}{3}\end{cases}\]
     \[
@@
 and similarly for $h_2$.
-Hence the set corresponding to $h_1$ contains all points, while the set corresponding to $h_2$ contains all points with $y \neq 1/2$.
+Hence the set corresponding to $h_1$ contains all points, while the set
+corresponding to $h_2$ contains as a subset all points $(y,z)$ with $y\neq 1/2$,
+as well as $(1/2,0)$.
 But the closure of $\{(y,z) \mid y \neq 1/2\}$ in $[0,1]^2$ is the whole space, so that both sets are indeed equal to the whole space.
@@
 
-Strangely enough, the only examples that we know of so far are of two kinds: first, cartesian monoidal categories (meaning that $\cC = \cC_\det$) with all products; and second, the finitary complete monoids of \Cref{poset_case} which are monoidal posets.
+Strangely enough, the only examples that we know of so far are of two kinds: first, cartesian monoidal categories (meaning that $\cC = \cC_{\det}$) with all products; and second, the finitary complete monoids of \Cref{poset_case} which are monoidal posets.
 For the former, the universal property of the monoidal structure implies that the causality axiom holds.

### 2020-05-03 categorical-zero-one.tex
revised also in light of referee 2

@@
 therefore so are the subcategories $\BorelStoch$ and $\FinStoch$.
-\todo[inline]{Added as per reviewer's suggestion, but unsure if it's a good
-  inclusion or not.}
+
 \begin{example}
@@
 Consider the additive maps given by
-\begin{equation}
-  f(a + b\epsilon) = & b\\
-  g(a + b \epsilon) = & b\\
-  h_{1}(a+ b \epsilon) = & a + b \epsilon\\
-  h_{2}(a + b \epsilon) = & 0
-\end{equation}
+\begin{align*}
+	f(a + b\epsilon) = {}& b\\
+	g(a + b \epsilon) = {}& b\\
+	h_{1}(a+ b \epsilon) = {}& a + b \epsilon\\
+	h_{2}(a + b \epsilon) = {}& 0
+\end{align*}
 Since $gf = 0$, it's clear that the hypothesis holds, so if $\CRing_{+}^{\op}$
@@
 However, this clearly fails if $z = \epsilon$, $y=1$ and $x = \epsilon$.
+\todo[inline]{It would be nice to have such an example. But this one doesn't work, since these additive maps are not unit-preserving.}
 \end{example}
@@
 	Given morphisms $p : A \to X$ and $f,g : X \to Y$ in a Markov category, we
-    say that $f$ and $g$ are \emph{$p$-a.s.~equal} (or $p$-\emph{almost surely}.~equal) if
+	say that $f$ and $g$ are \emph{$p$-a.s.~equal} (or $p$-\emph{almost surely equal}) if
 	\[
@@
   This term comes from measure theory, and should be interpreted as meaning
-  ``for all $a\in A$, if $x \in X$ is sampled according to $p(a)$, the
-  probability that $f(x) \neq g(x)$ is zero''.
+  that for all those values of $X$ which can occur as outputs of $p$, feeding these values to $f$ and $g$ as inputs is guaranteed to result in the same distribution; at the same time, the behavior of $f$ and $g$ may be different on those input values which do not occur as outputs of $p$.
+  \todo[inline]{I've rephrased this in order to make sure that we don't create the impression of making a technically precise statement}
 
@@
 Then we claim that
-	\[
+	\begin{equation}
+		\label{hewsav2}
 		\tikzfig{hewsav2}
-	\]
+	\end{equation}
 	By \Cref{two_infproducts}, it is enough to prove this upon postcomposing with two finite marginalizations $\pi_{F_1}$ and $\pi_{F_2}$.
@@
 We note that the standard Kolmogorov zero--one law holds for any measurable
-spaces, not just for standard Borel spaces - hence this is a strictly less
+spaces, not just for standard Borel spaces, and hence this is a strictly less
 general statement. As discussed in \cref{infprods_stoch}, it seems unlikely that
@@
 	\]
-	We show that this is an injection.
+	We prove that this is a homeomorphism, showing first that it is an injection.
 Thus we start with distinct closed subsets $C, D \subseteq \prod X_i$.
@@
     Then let $U \ni x$ be an open neighborhood of $x$ not intersecting $D$.
-    Since $U$ is open in the product topology, we can assume that there is some finite subset $F \subset J$ so that 
-    	\[
-		y = (y_i) \in U \quad\Longleftrightarrow\quad y_i \in \pi_i(U) \:\;\forall i\in F.
-	\]
+    By making $U$ smaller if necessary, we can assume without loss of generality that $U$ is a basic open in the product topology, meaning that there is a finite $F$ so that
+    \begin{equation}
+	    \label{basicU}
+		y = (y_i) \in U \quad\Longleftrightarrow\quad y_i \in \pi_i(U) \:\; \forall i \in F.
+    \end{equation}
     Then $\pi_F(x) \in \pi_F(U)$, which is disjoint from $\pi_F(D)$. Hence $\alpha(C) \neq \alpha(D)$.
@@
 For a given point $C \in \mathrm{Hit}(U)$, it is enough to find an open neighborhood contained in $\mathrm{Hit}(U)$.
-But then by making $U$ smaller if necessary, we can assume without loss of generality that $U$ is a basic open in the product topology, meaning that there is a finite $F$ so that
-	\[
-		y = (y_i) \in U \quad\Longleftrightarrow\quad y_i \in \pi_i(U) \:\; \forall i \in F.
-	\]
+	But then again by choosing smaller $U$ if necessary, so that $C \cap U \neq \emptyset$ still holds, we can assume~\eqref{basicU} without loss of generality.
     Then

### 2020-05-03 categorical-zero-one.tex
numbering in refs to [6]

@@
 
-There is a strictification result~\cite[Theorem~10.16]{markov_cats} which guarantees that $\cC$ can be assumed to be strict monoidal, as we do throughout.
+There is a strictification result~\cite[Theorem~10.17]{markov_cats} which guarantees that $\cC$ can be assumed to be strict monoidal, as we do throughout.
 
@@
 
-As per~\cite[Remark~10.12]{markov_cats}, the deterministic morphisms form a symmetric monoidal subcategory $\cC_\detc \subseteq \cC$ which contains all structure morphisms of $\cC$, including the comultiplications themselves.
+As per~\cite[Remark~10.13]{markov_cats}, the deterministic morphisms form a symmetric monoidal subcategory $\cC_\detc \subseteq \cC$ which contains all structure morphisms of $\cC$, including the comultiplications themselves.
 The fact that all morphisms are comonoid homomorphisms implies that $\cC_\detc$ is actually cartesian monoidal.
@@
 
-\begin{definition}[{\cite[Definition~11.30]{markov_cats}}]
+\begin{definition}[{\cite[Definition~11.31]{markov_cats}}]
 	A Markov category $\cC$ is \emph{causal} if whenever
@@
 
-It is known that $\Stoch$ is causal~\cite[Example~11.34]{markov_cats}, and
+It is known that $\Stoch$ is causal~\cite[Example~11.35]{markov_cats}, and
 therefore so are the subcategories $\BorelStoch$ and $\FinStoch$.
@@
 These examples illustrate the following important point.
-In some Markov categories, such as $\CRing_+\op$, not all isomorphisms are deterministic, and there may even be isomorphic objects which have no deterministic isomorphism~\cite[Remark~10.9]{markov_cats}.
+In some Markov categories, such as $\CRing_+\op$, not all isomorphisms are deterministic, and there may even be isomorphic objects which have no deterministic isomorphism~\cite[Remark~10.10]{markov_cats}.
 In these categories, whether a given infinite tensor product is a Kolmogorov product or not generally depends on the specific choice of that object.

### 2020-05-04 categorical-zero-one.tex
edits, added .txt file

@@
 $\CRing_{+}^{\op}$ is \emph{not} causal.
-To see this, consider the ring $\mathbb{Z}[\epsilon]/(\epsilon^{2})$.
-Elements have the form $a + b\epsilon$, with $a,b\in\bZ$, and multiplication is
-defined by the convention $\epsilon^{2} = 0$.
+To see this, consider the ring $\mathbb{Z}[t]$.
 Consider the additive maps given by
 \begin{align*}
-	f(a + b\epsilon) = {}& b\\
-	g(a + b \epsilon) = {}& b\\
-	h_{1}(a+ b \epsilon) = {}& a + b \epsilon\\
-	h_{2}(a + b \epsilon) = {}& 0
+	f(t^{n}) = {}& \begin{cases}t & n \geq 1 \\ 1 & n= 0\end{cases}\\
+	g(t^{n}) = {}& \begin{cases}t^{n-1} & n \geq 1 \\ 1 & n = 0 \end{cases}\\
+	h_{1}(t^{n}) = {}& t^{n}\\
+	h_{2}(t^{n}) = {}& t^{n+1}
 \end{align*}
-Since $gf = 0$, it's clear that the hypothesis holds, so if $\CRing_{+}^{\op}$
-were causal, we would have the equation
-$g(f(h_{1}(x)y)z) = g(f(h_{2}(x)y)z)$ for all
-$x,y,z \in \bZ[\epsilon]/(\epsilon^{2})$.
-However, this clearly fails if $z = \epsilon$, $y=1$ and $x = \epsilon$.
-\todo[inline]{It would be nice to have such an example. But this one doesn't work, since these additive maps are not unit-preserving.}
+Now $gf(t^{n}) = 1$, $h_{1}(p(t))q(t) = p(t)q(t)$, and
+$h_{2}(p(t))q(t) = tp(t)q(t)$.
+So it's easy to verify that the hypotehis holds.
+If $\CRing_{+}^{\op}$ were causal, we would have
+$g(f(h_{1}(p(t))q(t))r(t)) = g(f(h_{2}(p(t))q(t))r(t))$.
+But this clearly fails for e.g $p(t)=q(t)=r(t) = t$.
+$g(f(h_{1}(1)1)t) = 1$, but $g(f(h_{2}(1)1)t) = t$.
+
+\todo[inline]{It would be nice to have such an example. But this one doesn't
+  work, since these additive maps are not unit-preserving.}
+\todo[inline]{I've adapted this from the similar example in your reference paper.}
 \end{example}

### 2020-05-04 categorical-zero-one.tex
ring example

--- 2020-05-03 categorical-zero-one.tex
@@
 $\CRing_{+}^{\op}$ is \emph{not} causal.
-To see this, consider the ring $\mathbb{Z}[\epsilon]/(\epsilon^{2})$.
-Elements have the form $a + b\epsilon$, with $a,b\in\bZ$, and multiplication is
-defined by the convention $\epsilon^{2} = 0$.
-Consider the additive maps given by
+To see this, consider the ring $\mathbb{Z}[t]$, where the following counterexample similar to~\cite[Example~11.33]{markov_cats} can be formulated.
+Consider the additive maps given as the additive extensions of
 \begin{align*}
-	f(a + b\epsilon) = {}& b\\
-	g(a + b \epsilon) = {}& b\\
-	h_{1}(a+ b \epsilon) = {}& a + b \epsilon\\
-	h_{2}(a + b \epsilon) = {}& 0
+	f(t^{n}) = {}& \begin{cases}t^{n-1} & n \geq 1 \\ 1 & n = 0 \end{cases}\\[3pt]
+	g(t^{n}) = {}& \begin{cases}t & n \geq 1 \\ 1 & n= 0\end{cases}\\[3pt]
+	h_{1}(t^{n}) = {}& t^{n}\\[3pt]
+	h_{2}(t^{n}) = {}& 1
 \end{align*}
-Since $gf = 0$, it's clear that the hypothesis holds, so if $\CRing_{+}^{\op}$
-were causal, we would have the equation
-$g(f(h_{1}(x)y)z) = g(f(h_{2}(x)y)z)$ for all
-$x,y,z \in \bZ[\epsilon]/(\epsilon^{2})$.
-However, this clearly fails if $z = \epsilon$, $y=1$ and $x = \epsilon$.
-\todo[inline]{It would be nice to have such an example. But this one doesn't work, since these additive maps are not unit-preserving.}
+On the basis monomials $t^n$, we have $(fg)(t^n) = 1$, and therefore
+\[
+	(fg)(h_1(t^n)t^m) = 1 = (fg)(h_2(t^n)t^m)
+\]
+for all $n,m \in \mathbb{N}$, so that the hypothesis holds.
+If $\CRing_{+}^{\op}$ were causal, then we would also have
+\[
+	f(g(h_{1}(t^n) t^m) t^\ell) = f(g(h_{2}(t^n) t^m) t^\ell)
+\]
+for all $n,m,\ell \in \mathbb{N}$. But this clearly fails for $n = \ell = 1$ and $m = 0$.
 \end{example}

### 2020-05-09 response_to_referees.tex
first version of response to referee

\documentclass[11pt]{article}
\usepackage{eigilscmds}
\usepackage{tikzit}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{csquotes}
\input{comonoids.tikzdefs}
\input{comonoids.tikzstyles}

% draft packages
%\usepackage{todonotes}
%\usepackage{showkeys}

\author{Tobias Fritz and Eigil Fjeldgren Rischel}
\title{Response to Referees:\\ The zero--one laws of Kolmogorov and Hewitt--Savage\\ in categorical probability}
\date{\today}

\renewcommand{\sf}{\mathsf}
\DeclareMathOperator{\del}{del}
\begin{document}
\maketitle

\begin{abstract}
	We would like to thank both referees for their useful suggestions. There are some items that we would like to respond to, in particular from the first referee's report.
\end{abstract}

\section*{Referee 1}

We have been quite surprised by the length and the amount of detail of this report, and it is exciting that the referee has invested so much work into it. Unfortunately we disagree with the referee on most counts.

\todo[inline]{Comment first on the referee's suggestion to change the emphasis to infinite tensor products}

To illustrate the general incoherence of the referee's report, we start by commenting on the summary report and then moving on the material in the attached PDF.

\begin{enumerate}[label=(\alph*).]
	\item The referee writes:
		\begin{displayquote}
			Your definition of the infinite tensor product is not correct - it does not capture the property characterizing the Kolmogorov extension theorem.  This can be corrected easily enough.
		\end{displayquote}
		This seems to claim that there is an error in our paper.
		\begin{displayquote}	
		However, that correction does require additional material proving that the Kolmogorov extension theorem really is equivalent to the existence of infinite tensor products for the category of standard Borel spaces. The difficulty arises because it is necessary to show that the Kleisi category construction, which is the framework in which  the Kolmogorov extension theorem is given, is a special case of the more general situation in a Markov semicartesian symmetric monoidal category where we have an inclusion of a subcategory (specified by the  deterministic morphisms) into a category which consist of deterministic and nondeterministic mappings.
		\end{displayquote}
		Now the error seems to have become a mere gap. Regardless, there is no such error or gap: the connection with the Kolmogorov extension theorem is explained in Remark 3.5 and Example 3.6. In order to see that this recovers the extension theorem, it is not necessary to construct $\BorelStoch$ as the Kleisli category of the Giry monad (although this is certainly one way to do it); the concrete construction of $\BorelStoch$ in terms of Markov kernels and the Chapman--Kolmogorov formula is perfectly enough, and we have explained why countable tensor products in our sense exist in $\BorelStoch$, and it is obvious that this specializes to the Kolmogorov extension theorem for countable products of standard Borel spaces.

		In fact, the referee already seems to agree with this: the relevant diagram is exactly the referee's one on the second half of p.6 (in the report). The ``new terminology'' that the referee proposes surely does not have any bearing on whether the universal property described by the diagram holds in $\BorelStoch$, right?
\end{enumerate}

On the comments in the PDF:

\begin{enumerate}[resume,label=(\alph*).]
	\item The referee's proposed formulation of Definition 3.1 is along the lines of our Definition 4.1.\footnote{With the only difference between the preservation by the functors $-\otimes Y$, which we get to in the next item.} Both require the Kolmogorov product to the limit of the finite products $\bigotimes_{i \in F} X_i$ in $\cC$ and in $\cC_{\det}$. So it is not clear to us what the referee's point is.

		Perhaps the referee's suggestion is to replace Definition 3.1 by Definition 4.1. We do not want to do this, since the latter only applies in Markov categories, while the former more generally makes sense in semicartesian monoidal categories.
		\begin{displayquote}
			and hence every ``infinite tensor product'' is Kolmogorov.
		\end{displayquote}
		This is true in categories like $\Stoch$ and $\BorelStoch$, but not in general. We had already explained this point after Definition 4.1.
	\item Quoting from p.7,
		\begin{displayquote}
			I did not incorporate the property of preservation of lim $\mathcal{D}$ by the endofunctor
			$-\otimes Y : \cC_{\det} \to \cC_{\det}$ because that condition is a global property in the sense
		that $Y$ is an arbitrary element in your space which may have no relationship
		to your fixed family $(X_j)_{j\in J}$ for which you are trying to find an extension.
		\end{displayquote}
		Assuming that ``space'' means category, we agree that there is no relation between $Y$ and the family $(X_i)$, but we do not see why and how this would be an argument against our preservation condition. As the referee will hopefully have noticed, this preservation condition is an important property which we use throughout the paper.

		Perhaps the referee's point is that this preservation condition never appears in the context of Kolmogorov's extension theorem. This is true, and the reason is simple: it \emph{automatically holds} in $\BorelStoch$, as we have explained in Example 3.6. Hence there is no reason to state it explicitly in the standard probability context.
	\item On p.8, the referee again seems to conclude the incorrectness of a statement from their lack of understanding of our arguments:
		\begin{displayquote}
		(2) Page 17, the last sentence. The statement
			\begin{displayquote}
			Moreover, $\hat{\sigma}$ is deterministic by Proposition 4.3.
			\end{displayquote}
		is not correct.
		\end{displayquote}
		The comment that follows:
			\begin{displayquote}
				then please cite a reference	
			\end{displayquote}
		indeed makes it clear that the referee does not claim to have found a mistake. In fact, the reason that $\hat{\sigma}$ is deterministic is by a trivial application of the universal property of the Kolmogorov product as a limit in $\cC_{\det}$, based precisely on the facts that the referee mentions: both the composite and the $\pi_F$'s are deterministic, and hence the factorization exists uniquely.
	\item Again p.8:
		\begin{displayquote}
			(3) Corollary 6.1. (Kolmogorov zero-one law) Your assumption, which says that
			$T \subseteq \Omega$, is incorrect, because if $T$ is just a subset of $\Omega$, then I can just choose
			it to be any nonmeasurable set of $\Omega$.
		\end{displayquote}
		It is a mystery to us how it is possible to read over half of a sentence, where the relevant measurability assumption is stated in clear and explicit terms.
		\begin{displayquote}
			If you
			meant to say that $T$ is a measurable set in $\Omega$, the whole problem statement is an
			elementary result in measure theory, and certainly not the Kolmogorov zero-one
			law.
		\end{displayquote}
		If $T$ was an \emph{arbitrary} measurable set in $\Omega$, then the statement would clearly be the false. In any case, our statement of the Kolmogorov zero--one law has been and is exactly the classical one, and it is so classical that it should not require a reference.
	\item p.9, item (2): Even if most categorical foundations in algebra and geometry required monoidal closure (which is obviously not the case, take e.g.~abelian categories), we do not see how this would be an argument for monoidal closure in the context of probability theory.
	\item p.9, item (4): Standard usage of the term ``diagram'' in category theory does not have any association with graph homomorphisms. In standard parlance as we use it, ``diagram'' is just any functor from a small category into the category under consideration.\footnote{See e.g.~\href{https://ncatlab.org/nlab/show/diagram\#CategoryShapedDiagramFunctorially}{https://ncatlab.org/nlab/show/diagram\#CategoryShapedDiagramFunctorially}.}
	\item p.11:
		\begin{displayquote}
			\textbf{Theorem 4.1.} The weak limit of the functor $\mathcal{D}' : \mathscr{J} \to \Stoch$ exists. Moreover, the weak limit of the functor $\mathcal{D}'$ is never a limit in $\Stoch$ except for trivial cases.
		\end{displayquote}
		It is not clear to us what ``the weak limit'' means, since weak limits are rarely unique (up to unique iso), and in particular uniqueness does not hold in the case under consideration. We agree that the referee's construction indeed produces a weak limit that is not a limit. But the fact that that particular weak limit is not a limit says nothing about whether the functor has a limit or not.
\end{enumerate}

\section*{Referee 2}

We thank the referee for a number of suggestions which have led to an improvement of the presentation. It is good to know for us that the paper is not so easy to follow at times. While an exposition of string diagrams and Markov categories would perhaps be a bit too much for this paper, we hope that these shortcomings can be addressed in a possible future textbook treatment of the subject.

%\bibliographystyle{plain}
%\bibliography{categorical-zero-one}

\end{document}

### 2020-05-09 categorical-zero-one.tex
mention unitality
first version of response to referee

@@
 Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
-We can draw an analogy to the Euclidean approach to geometry: here, points and lines are described only in terms of their relationships with one another; while in the analytic approach often attributed to Descartes, where geometric objects are defined concretely in terms of more primitive notions like sets and real numbers.
+We can draw an analogy to the Euclidean approach to geometry: here, points and lines are described only in terms of their relationships with one another; while in the analytic approach often attributed to Descartes, geometric objects are defined concretely in terms of more primitive notions like sets and real numbers.
 
@@
 	assigning to every $x \in X$ a probability measure $f(-|x) : \Sigma_Y \to [0,1]$ in such a way that for every $S \in \Sigma_Y$, the function $x \mapsto f(S|x)$ is measurable.
-Intuitively, $f$ assigns to every $x \in X$ a random element of $Y$.
+Intuitively, one can think of $f$ as assigning to every $x \in X$ a random element of $Y$.
 Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the symmetric monoidal structure is defined in terms of the usual product of measurable spaces.
@@
 To see this, consider the ring $\mathbb{Z}[t]$, where the following counterexample similar to~\cite[Example~11.33]{markov_cats} can be formulated.
-Consider the additive maps given as the additive extensions of
+Consider the additive unital maps given as the additive extensions of
 \begin{align*}
@@
 \begin{problem}
-	Is there a Markov category $\cC$ with countable Kolmogorov products such that \Cref{thm:kolmog} specializes to the standard Kolmogorov zero--one law in its general form applicable to all measurable spaces?
+	Is there a Markov category $\cC$ with countable Kolmogorov products such that \Cref{thm:kolmog} specializes to the standard Kolmogorov zero--one law, in its general form applicable to all measurable spaces?
   \end{problem}
@@
 \end{document}
-
-\section{Speculation}
-\todo[inline]{not sure if this section is any good}
-It would good to have a way of using this theorem without assuming that the category in question has these infinite tensor products.
-We can always make sense of the notion of an infinite independent collection of random variables (just a collection of maps $I \to X_i$).
-Of course to talk about an outcome or a function which depends on the outcome of all the $X_i$, we need a map $\prod_i X_i \to T$ of some type.
-But since this map is deterministic, we may want to talk about it without admitting it to our category of Markov kernels.
-
-As an example, the probability theory of finite or countable sets is much simpler than the probability theory of infinite sets, since the whole edifice of $\sigma$-algebras can be done away with.
-This is a reason to prefer $\sf{FinStoch}$ over the full $\sf{Stoch}$.
-In this case, it would be desirable to be able to apply this theorem, given a collection of finite variables $I \to X_i$ and a function $\prod_i X_i \to Y$
-(which may be required to satisfy some condition like continuity in the product topology), without begin required to invent the larger category $\sf{Stoch}$.
-
-For instance, maybe there is a Markov category with objects the profinite sets, which can be obtained from $\sf{FinStoch}$ by some formal construction (maybe even simply as the pro-category), which admits infinite tensor products, and where one can profitably interpret this theorem.

### 2020-05-10 response_to_referees.tex
final response to refs

@@
 We have been quite surprised by the length and the amount of detail of this report, and it is exciting that the referee has invested so much work into it.
-Unfortunately we disagree with the referee on most counts.
+The referee's suggestion of putting more emphasis on our infinite tensor products and Kolmogorov products has been helpful for us, and we have shifted the emphasis a bit.
 
-\todo[inline]{Comment first on the referee's suggestion to change the emphasis to infinite tensor products}
-
-To illustrate the general incoherence of the referee's report, we start by commenting on the summary report and then moving on the material in the attached PDF.
+At the same time, we strongly disagree with the referee on essentially all other counts.
+In particular, the details below will explain that all ``errors'' pointed out in the report are the referee's errors, not ours.
+We start by commenting on the summary report and then move on to the material in the attached PDF.
 
@@
 \begin{enumerate}[resume,label=(\alph*).]
-	\item The referee's proposed formulation of Definition 3.1 is along the lines of our Definition 4.1.\footnote{With the only difference between the preservation by the functors $-\otimes Y$, which we get to in the next item.} Both require the Kolmogorov product to the limit of the finite products $\bigotimes_{i \in F} X_i$ in $\cC$ and in $\cC_{\det}$.
+	\item The referee's proposed new formulation of Definition 3.1 is along the lines of our Definition 4.1.\footnote{With the only difference between the preservation by the functors $-\otimes Y$, which we get to in the next item.} In both definitions, the Kolmogorov product is the limit of the finite products $\bigotimes_{i \in F} X_i$ in both $\cC$ and in $\cC_{\det}$.
 So it is not clear to us what the referee's point is.
@@
 		\end{displayquote}
-		This is true in categories like $\Stoch$ and $\BorelStoch$, but not in general. We had already explained this point after Definition 4.1.
+		This is true in categories like $\Stoch$ and $\BorelStoch$, but not in general.
+We had already explained this point after Definition 4.1.
+In conclusion, the distinction between infinite tensor products (in semicartesian monoidal categories, Section 3) and Kolmogorov products (in Markov categories, Section 4) is important and should not be swept under the rug.
 	\item Quoting from p.7,
@@
 		\end{displayquote}
-		It is a mystery to us how it is possible to read over half of a sentence, where the relevant measurability assumption is stated in clear and explicit terms.
+		It is a mystery to us how it is possible to read over half of a sentence: the relevant measurability assumption was stated in clear and explicit terms directly after $T \subseteq \Omega$.
 		\begin{displayquote}
@@
 		\end{displayquote}
-		If $T$ was an \emph{arbitrary} measurable set in $\Omega$, then the statement would clearly be the false.
+		If $T$ was an \emph{arbitrary} measurable set in $\Omega$, then the statement would quite obviously be false.
 In any case, our statement of the Kolmogorov zero--one law has been and is exactly the classical one, and it is so classical that it should not require a reference.
@@
 		It is not clear to us what ``the weak limit'' means, since weak limits are rarely unique (up to unique iso), and in particular uniqueness does not hold in the case under consideration.
-We agree that the referee's construction indeed produces a weak limit that is not a limit.
+That being said, we agree that the referee's construction indeed produces a weak limit that is not a limit.
 But the fact that that particular weak limit is not a limit says nothing about whether the functor has a limit or not.
@@
 We thank the referee for a number of suggestions which have led to an improvement of the presentation.
-It is good to know for us that the paper is not so easy to follow at times.
+It is good to know for us that the paper is not so easy to follow at times, and we have implemented .
 While an exposition of string diagrams and Markov categories would perhaps be a bit too much for this paper, we hope that these shortcomings can be addressed in a possible future textbook treatment of the subject.

### 2020-05-10 response_to_referees.tex
some revision

@@
 We have been quite surprised by the length and the amount of detail of this report, and it is exciting that the referee has invested so much work into it.
-The referee's suggestion of putting more emphasis on our infinite tensor products and Kolmogorov products has been helpful for us, and we have shifted the emphasis a bit.
+The referee's suggestion of putting more emphasis on our infinite tensor products and Kolmogorov products has been helpful for us, and we have shifted the emphasis a bit in that direction.
 
 At the same time, we strongly disagree with the referee on essentially all other counts.
-In particular, the details below will explain that all ``errors'' pointed out in the report are the referee's errors, not ours.
+In particular, the details below will explain that \textbf{all ``errors'' pointed out in the report are the referee's errors, not ours}.
 We start by commenting on the summary report and then move on to the material in the attached PDF.
@@
 		Assuming that ``space'' means category, we agree that there is no relation between $Y$ and the family $(X_i)$, but we do not see why and how this would be an argument against our preservation condition.
-As the referee will hopefully have noticed, this preservation condition is an important property which we use throughout the paper.
+As the referee will hopefully have noticed, this preservation condition is an important property which we use throughout the paper; in particular, the preservation property is what guarantees the coherence property described in Remark 3.3.
 
@@
 We thank the referee for a number of suggestions which have led to an improvement of the presentation.
-It is good to know for us that the paper is not so easy to follow at times, and we have implemented .
-While an exposition of string diagrams and Markov categories would perhaps be a bit too much for this paper, we hope that these shortcomings can be addressed in a possible future textbook treatment of the subject.
+It is good to know for us that the paper is not so easy to follow at times, and we have invested some work into the exposition with the referee's feedback in mind.
 

### 2020-05-10 categorical-zero-one.tex
some revision

@@
 \author{Tobias Fritz and Eigil Fjeldgren Rischel}
-\title{The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability}
+\title{Infinite products and zero--one laws in categorical probability}
 \date{\today}
@@
 \begin{abstract}
-	We state and prove the zero--one laws of Kolmogorov and Hewitt--Savage within the setting of \emph{Markov categories}, a category-theoretic approach to the foundations of probability and statistics.
+	\emph{Markov categories} are a recent category-theoretic approach to the foundations of probability and statistics.
+Here we develop this approach further by treating infinite products and the Kolmogorov extension theorem.
+This is relevant for all aspects of probability theory in which infinitely many random variables appear at a time.
+These infinite tensor products $\bigotimes_{i \in J} X_i$ come in two versions: a weaker but more general one for families of objects $(X_i)_{i \in J}$ in semicartesian symmetric monoidal categories, and a stronger but more specific one for families of objects in Markov categories.
+
+	As a first application, we state and prove versions of the zero--laws of Kolmogorov and Hewitt--Savage laws for Markov categories.
 This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts.
-For example, applying the Kolmogorov law to the Kleisli category of the hyperspace monad on topological spaces gives criteria for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.
+% For example, applying the Kolmogorov zero--one law to the Kleisli category of the hyperspace monad on topological spaces gives a criterion for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.
+
 \end{abstract}
@@
 
-\emph{Markov categories} are an approach to the foundations of probability and statistics based on category theory, proposed first by Golubtsov~\cite{golubtsov}, rediscovered recently independently by Cho and Jacobs~\cite{cho_jacobs}, and developed extensively by the first author in \cite{markov_cats}.
+\emph{Markov categories} are an approach to the foundations of probability and statistics based on category theory, proposed first by Golubtsov~\cite{golubtsov}, rediscovered recently independently by Cho and Jacobs~\cite{cho_jacobs}, and developed extensively by the first-named author in \cite{markov_cats}.
 The basic observation is that Markov kernels can be composed sequentially and in parallel, making them into a symmetric monoidal category $\Stoch$.
 One can then find axioms which make a symmetric monoidal category behave similarly to the actual category of Markov kernels, and then state and prove results from probability and statistics in this general abstract context.
+Thus Markov categories are abstract versions of the category of Markov kernels, and hence their name.
 
 This represents a \emph{synthetic} approach to probability, in contrast with the usual measure-theoretic approach (which can be called \emph{analytic}).
-Instead of defining \emph{what} the words probability, distribution, random variable, etc, \emph{mean}, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy.
-We can draw an analogy to the Euclidean approach to geometry: here, points and lines are described only in terms of their relationships with one another; while in the analytic approach often attributed to Descartes, geometric objects are defined concretely in terms of more primitive notions like sets and real numbers.
+Instead of defining \emph{what} the words probability, distribution, random variable, etc, mean semantically, we instead state by which operations these objects can be combined and related to each other, and which properties they are supposed to satisfy with respect to each other.
+We can draw an analogy to the Euclidean approach to geometry: in this synthetic approach, points and lines are described only in terms of their relationships with one another.
+This is to be contrasted with the analytic approach often attributed to Descartes, in which geometric objects are defined concretely in terms of more primitive notions like sets and real numbers.
 
-In this paper, we give a treatment of the zero--one laws of Kolmogorov and of Hewitt--Savage in the setting of Markov categories.
+In this paper, we give a treatment of further fundamental and classical results of probability theory within the setting of Markov categories.
 This adds further support to the hypothesis that Markov categories are an adequate setting for the foundations of probability and statistics, adding to the existing treatments of Bayesian updating, almost sure equality, conditional independence, and theorems on sufficient statistics~\cite{cho_jacobs,markov_cats}.
+Concretely, we develop a notion of infinite tensor products in Markov categories and then apply this notion to state and prove two of the standard zero--one laws of probability theory.
 
-Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables and an event which is in the $\sigma$-algebra generated by the variables but independent of any finite subset of these variables, the event has probability zero or one.
-This theorem goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm}, although the statement appearing there is significantly different from the modern form.
-For a more recent treatment of this theorem, see e.g. \cite[Theorem~2.37]{klenke}
+\paragraph*{Summary.}
 
-The Hewitt--Savage zero--one law, due to Hewitt and Savage in \cite[Theorem~11.3]{hewitt_savage}, is similar.
-Here, the variables are assumed to be identically distributed in addition to being independent, and the event is assumed to be invariant under finite permutations of the variables.
+We now present a more detailed overview.
+
+\Cref{background} presents some background by recalling the definition of Markov category, presenting some pertinent examples, and discussing those aspects of the existing theory of Markov categories that will be of relevance for the rest of the paper.
+With the exception of \Cref{cring_not_causal}, there is nothing new in this section.
+
+\Cref{infprod_semicartesian} then proceeds by introducing infinite tensor products in semicartesian symmetric monoidal categories, which are exactly those symmetric monoidal categories in which the monoidal unit object is terminal.
+We consider a number of examples of such categories and discuss whether infinite tensor products exist.
+This already includes examples relevant for probability theory, and in particular $\BorelStoch$, the category of standard Borel spaces and measurable maps\footnote{Or equivalently Polish spaces and measurable maps.}, for which we explain how countably infinite tensor products implement the Kolmogorov extension theorem (for countably many variables); the extension theorem states that the joint distributions of infinitely many random variables are in bijection with compatible families of joint distributions for each finite subset of variables.
+The universal property of our infinite tensor products makes the extension theorem into a definition, generalized from distributions to Markov kernels.
+An important subtlety here is the additional preservation condition in \Cref{semicartesian_infproduct}, where infinite tensor products are introduced: this additional condition guarantees that infinite tensor products have nice compositionality properties, so that e.g.~a tensor product of two infinite tensor products is itself an infinite tensor product (\Cref{two_infproducts}).
+This condition does not come up traditionally in the context of the Kolmogorov extension theorem, the reason being that it automatically holds in the case of $\BorelStoch$ (\Cref{infprods_stoch}).
+
+In the short \Cref{infprod_markov}, we then turn to infinite tensor products in Markov categories, which we call \emph{Kolmogorov products} due to the connection with the Kolmogorov extension theorem.
+In addition to being an infinite tensor product, a Kolmogorov product also needs to respect the additional structure which makes a semicartesian symmetric monoidal category into a Markov category, namely the comultiplications $\cop{X} : X \to X \otimes X$.
+This is implemented by postulating that the product projections should be deterministic morphisms, or equivalently that the infinite product should be an honest categorical product in the cartesian monoidal subcategory of deterministic morphisms (\Cref{kolmprod_catdet}).
+Not surprisingly, the infinite tensor products in $\BorelStoch$, which implement the Kolmogorov extension theorem, are indeed Kolmogorov products.
+
+In \Cref{zeroones}, we state and prove the zero--one laws of Kolmogorov and Hewitt--Savage in their synthetic versions.
+Very roughly, the Kolmogorov zero--one law states that, given an infinite collection of independent random variables and an event which is in the $\sigma$-algebra generated by the variables but independent of any finite subset of them, the event has probability zero or one.
+This theorem goes back to Kolmogorov's foundational monograph \cite{kolmogorovgerm}, although the statement appearing there is significantly different from its modern form.
+For a more recent textbook treatment of this theorem, see e.g.
+\cite[Theorem~2.37]{klenke}
+
+The Hewitt--Savage zero--one law, due to Hewitt and Savage in \cite[Theorem~11.3]{hewitt_savage}, is similar in flavour but technically quite different.
+Here, the infinitely many variables are assumed to be identically distributed in addition to being independent, and the event is assumed to be invariant under finite permutations of the variables.
 Again, under these assumptions, the event has probability zero or one.
 
-To formulate these statements in the general context of Markov categories, we need an abstract generalization of the concept of joint distribution of infinitely many random variables.
-To this end, we introduce a notion of \emph{infinite tensor product}, first for semicartesian monoidal categories (\Cref{infprod_semicartesian}) and then for Markov categories (\Cref{infprod_markov}).
-A morphism to such an infinite tensor product is an abstract version of a probability measure on an infinite product of measurable spaces.
-Based on this definition, we then prove abstract versions of the zero--one laws, \Cref{thm:kolmog} and \Cref{thm:hewsav}.
-
-Finally in \Cref{examples}, we apply our results to the category of measurable spaces and Markov kernels $\Stoch$.
-In order to guarantee that countably infinite tensor products exist, we restrict to the full subcategory of standard Borel spaces.
+Finally in \Cref{examples}, we apply our results to $\BorelStoch$.
 We thereby rederive the standard zero--one laws for random variables in standard Borel spaces from our abstract theorems.
@@
 To simplify notation, we generally omit mention of the structure isomorphisms by assuming that $\cC$ is strict without loss of generality.
-We make frequent use of string diagram notation, and in doing so we omit object labels whenever these are obvious from the context.
+We routinely make use of string diagram notation, and in doing so we omit object labels whenever these are obvious from the context.
+Our string diagrams are to be read from bottom to top.
 
@@
 
+We assume familiarity with symmetric monoidal categories, up to and including string diagram notation and string diagram calculus for composite morphisms in symmetric monoidal categories.
+
 A symmetric monoidal category $\cC$ is \emph{semicartesian} if the monoidal unit $I \in \cC$ is terminal.
-Equivalently~\cite[Theorem~3.5]{GLS}, it is a symmetric monoidal category equipped with morphisms
+Equivalently~\cite[Theorem~3.5]{GLS}, $\cC$ is semicartesian if it comes equipped with morphisms
 \begin{equation}
@@
 \end{equation}
-which are natural in $X$ and $Y$ and coincide with the monoidal structure isomorphisms whenever $X = I$ or $Y = I$. Here are the main examples that we will be considering.
+which are natural in $X$ and $Y$ and coincide with the monoidal structure isomorphisms whenever $X = I$ or $Y = I$.
+In the probability context, these morphisms can be interpreted as marginalizations, or equivalently as discarding the value of the variable $Y$ or $X$.
+
+Here are the main examples of semicartesian symmetric monoidal categories that we will be considering.
 
@@
 	\label{finstoch}
-	$\FinStoch$ is the category of finite sets with \emph{stochastic matrices}, which means that a morphism $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
+	$\FinStoch$ is the category of finite sets with \emph{stochastic matrices} as morphisms.
+This means that for finite sets $X$ and $Y$, a morphism $f : X \to Y$ is a matrix $(f_{xy})_{x \in X,y \in Y}$ of nonnegative real numbers such that $\sum_y f_{xy} = 1$ for every $x$.
 Stochastic matrices compose by matrix multiplication, which in this context is also known as the \emph{Chapman--Kolmogorov equation}.
-We consider $\FinStoch$ as a symmetric monoidal category with respect to the cartesian product of sets on objects and the Kronecker product of stochastic matrices on morphisms; the monoidal structure isomorphisms are the obvious ones coming from the full embedding $\FinSet \subseteq \FinStoch$.
+We consider $\FinStoch$ as a symmetric monoidal category with respect to the cartesian product of sets on objects and the tensor product (Kronecker product) of stochastic matrices on morphisms; the monoidal structure isomorphisms are the obvious ones coming from the embedding $\FinSet \subseteq \FinStoch$.
 \end{example}
@@
 We sketch the definition here and refer to~\cite[Section~4]{markov_cats} and references therein for the details.
-A \emph{Markov kernel} $(X,\Sigma_X) \to (Y,\Sigma_Y)$ is a map
+Given measurable spaces $(X,\Sigma_X)$ and $(Y,\Sigma_Y)$, a \emph{Markov kernel} $(X,\Sigma_X) \to (Y,\Sigma_Y)$ is a map
 	\[
@@
 	assigning to every $x \in X$ a probability measure $f(-|x) : \Sigma_Y \to [0,1]$ in such a way that for every $S \in \Sigma_Y$, the function $x \mapsto f(S|x)$ is measurable.
-Intuitively, one can think of $f$ as assigning to every $x \in X$ a random element of $Y$.
-Composition is again defined by a variant of the Chapman--Kolmogorov equation, and the symmetric monoidal structure is defined in terms of the usual product of measurable spaces.
+Intuitively, one can think of $f$ as assigning to every $x \in X$ a random element of $Y$; or one can think of $f$ as a statistical model, specifying one probability measure $f(-|x)$ for every parameter value $x$.
+
+	Composition of Markov kernels is again defined by a variant of the Chapman--Kolmogorov equation: for $f : (X,\Sigma_X) \to (Y,\Sigma_Y)$ and $g : (Y,\Sigma_Y) \to (Z,\Sigma_Z)$, the composite is given by, for all $x \in X$ and $T \in \Sigma_Z$,
+	\[
+		(gf)(T|x) := \int_{y \in Y} g(T|y) \, f(dy|x),
+	\]
+	where the relevant measurability condition in order for this to define a Markov kernel follows by a standard application of the $\pi$-$\lambda$-theorem; associativity of composition uses Fubini's theorem.
+In this way, we obtain a category $\Stoch$ which is, more or less by definition, isomorphic to the Kleisli category of the Giry monad~\cite{giry}.
+
+	The symmetric monoidal structure on $\Stoch$ is defined in terms of the usual product of measurable spaces, given by the Cartesian product of underlying sets equipped with the product $\sigma$-algebra.
+The tensor product of morphisms $f : (A,\Sigma_A) \to (X,\Sigma_X)$ and $g : (B,\Sigma_B) \to (Y,\Sigma_Y)$ is given by the unique Markov kernel between the product measurable spaces which satisfies
+	\[
+		(f \otimes g)(S \times T|a,b) = f(S|a) \, g(T|b) \qquad \forall a \in A,\: b \in B,\: S \in \Sigma_X,\: T \in \Sigma_Y.
+	\]
 	The monoidal unit $I$ is given by any one-element set with its unique $\sigma$-algebra.
@@
 Since finite products of standard Borel spaces are again standard Borel, $\BorelStoch$ is again semicartesian symmetric monoidal.
+In summary, $\BorelStoch$ is the category of standard Borel spaces as objects with measurable Markov kernels as morphisms.
 \end{example}
@@
 As it turns out, doing so requires a bit more structure, in a form which has been axiomatized first by Cho and Jacobs~\cite{cho_jacobs} as \emph{affine CD-categories}, although very similar definitions occur in earlier work of Golubtsov~\cite{golubtsov}.
-We here follow the terminology of our own~\cite[Definition~2.1]{markov_cats}.
+We here follow the more intuitive terminology of our own~\cite[Definition~2.1]{markov_cats}.
 
@@
 
-There is a strictification result~\cite[Theorem~10.17]{markov_cats} which guarantees that $\cC$ can be assumed to be strict monoidal, as we do throughout.
+There is a strictification result~\cite[Theorem~10.17]{markov_cats} which guarantees that $\cC$ can be assumed to be strict monoidal without messing up the commutative comonoid structures.
+We assume from now on that $\cC$ is strict throughout.
 
@@
 \Cref{finstoch,cring,stoch} are all Markov categories in a canonical way.
-In $\FinStoch$ and $\Stoch$, the comultiplication morphisms are given indeed by copying, i.e.~by those stochastic matrices or Markov kernels which map an $x \in X$ to the Dirac delta measure at $(x,x) \in X \times X$.
+In $\FinStoch$ and $\Stoch$, the comultiplication morphisms are given indeed by copying, i.e.~by those stochastic matrices or Markov kernels which map an element $x \in X$ to the Dirac delta measure at $(x,x) \in X \times X$.
 We refer to~\cite[Example~2.5 and Section~4]{markov_cats} for the technical details.
@@
 \]
+
+The following definition is among the central notions of the theory of Markov categories.
 
@@
 
-In $\FinStoch$, the deterministic morphisms $X \to Y$ are exactly the $\{0,1\}$-valued stochastic matrices.
-Since these can be identified with honest functions $X \to Y$, we conclude that $\FinStoch_\detc$ is equivalent to $\FinSet$.
+In $\FinStoch$, the deterministic morphisms $X \to Y$ are exactly the $\{0,1\}$-valued stochastic matrices, which are indeed those which are deterministic in the sense that they do not involve any randomness.
+Since these stochastic matrices are in obvious bijection with honest functions $X \to Y$, we conclude that $\FinStoch_\detc$ is equivalent to $\FinSet$.
 In $\Stoch$, the deterministic morphisms $f : X \to Y$ are exactly those Markov kernels for which $f(S|x) \in \{0,1\}$ for every $S \in \Sigma_Y$ and $x \in X$.
-In other words, as the term suggests, the deterministic morphisms are those which do not involve any randomness; in $\BorelStoch$, the deterministic morphisms can be identified with the measurable functions.
+In other words, as the term suggests, the deterministic morphisms are again those which do not involve any randomness; in $\BorelStoch$, the deterministic morphisms can be identified with the measurable functions.
 In $\CRing_+\op$, the deterministic morphisms $R \to S$ are precisely those morphisms which are represented by additive unital maps $S \to R$ which are in addition multiplicative, i.e.~the ring homomorphisms.
@@
 
-We state some more definitions that we will be using later on.
+We recall some more definitions that we will be using later on.
 
@@
 
+Intuitively, this condition states that if the choice between $h_1$ and $h_2$ is irrelevant for what happens ``in the future of $g$'', then that choice is likewise irrelevant for what happened ``in the past of $g$''.
 It is known that $\Stoch$ is causal~\cite[Example~11.35]{markov_cats}, and
@@
 \begin{example}
+\label{cring_not_causal}
 $\CRing_{+}^{\op}$ is \emph{not} causal.
@@
   that for all those values of $X$ which can occur as outputs of $p$, feeding these values to $f$ and $g$ as inputs is guaranteed to result in the same distribution; at the same time, the behavior of $f$ and $g$ may be different on those input values which do not occur as outputs of $p$.
-  \todo[inline]{I've rephrased this in order to make sure that we don't create the impression of making a technically precise statement}
 
-We finally introduce a straightforward generalization of~\cite[Defnition~12.12]{markov_cats} from binary conditional independence to $n$-ary conditional independence.
+  We finally introduce a notion of conditional independence, which is a straightforward generalization of~\cite[Defnition~12.12]{markov_cats} from the binary case to the $n$-ary case.
 
@@
 
-Zero--one laws involve infinitely many random variables.
+Many theorems in probability theory involve infinitely many random variables at a time, together with a joint distribution for them.
 In the setting of Markov categories, this means that we need to consider morphisms whose codomain is an ``infinite tensor product'' in a suitable sense.
-In this section, we start by considering infinite tensor products in semicartesian symmetric monoidal categories.
+In this section, we start by considering infinite tensor products in the more general context of semicartesian symmetric monoidal categories.
 
+Recall that the Kolmogorov's extension theorem states that joint distributions of a given (infinite) family of random variables are in bijection with compatible families of distributions of finite subsets of these variables.
+Here, a joint distribution of all of them determines such a compatible family by considering all its marginals on finite subsets.
+This motivates our general definition of infinite tensor products, which we now introduce.
 Suppose that $(X_i)_{i \in J}$ is any family of objects, where the indexing set $J$ is typically infinite.
 For any finite subset $F \subseteq J$, we also write $X_F := \bigotimes_{i \in F} X_i$ for simplicity of notation.
-In the spirit of Kolmogorov's extension theorem, we believe that a good definition of joint distribution of infinitely many random variables will be such that such a joint distribution is uniquely determined by the family of its finite marginals.
-This motivates our general definition of the infinite tensor product, which we now introduce.
 If $F \subseteq F' \subseteq J$ are two finite subsets, then the fact that $\cC$ is semicartesian monoidal gives us \emph{marginalization morphisms}
@@
 	\[
-		X_J \: := \: \bigotimes_{j \in J} X_j
+		X_J \: := \: \bigotimes_{i \in J} X_i
 	\]
@@
 
-We will refer to the structure maps $\pi_F : X_J \to X_F$ as \emph{finite marginalizations}. The extra preservation condition will be motivated in \Cref{preserve}.
+We will refer to the structure maps $\pi_F : X_J \to X_F$ as \emph{finite marginalizations}.
+The extra preservation means more concretely that $X_J \otimes Y$ is likewise the cofiltered limit of the $X_F \otimes Y$ with respect to the maps
+\[
+	\pi_F \otimes \id_Y \: : \: X_J \otimes Y \longrightarrow X_F \otimes Y.
+\]
+We will motivate this preservation condition in \Cref{preserve}.
+
+Of course, an infinite tensor product may or may not exist in $\cC$. \Cref{infprods_finstoch} will present a simple example in which infinite tensor products only exist for \emph{finite} $J$.
 
 \begin{remark}
-	If $J$ is finite, then the infinite tensor product exists and coincides with the tensor product $X_J = \bigotimes_{i \in J} X_i$ specified by the monoidal structure.
-In a general Markov category, the relevant cofiltered limit need not exist for infinite $J$, in which case the infinite tensor product does not exist either (as in \Cref{infprods_finstoch}).
+	If $J$ is finite, then the infinite tensor product always exists and coincides with the tensor product $X_J = \bigotimes_{i \in J} X_i$ specified by the monoidal structure: then the finite product itself is initial in the defining diagram of the limit, and the preservation condition holds automatically for the same reason.
+Thus infinite tensor products $\bigotimes_{i \in J} X_i$ are of interest only for infinite $J$, as the terminology suggests.
+And for finite $J$, the notation is such that $\bigotimes_{i \in J} X_i$ can be interpreted either as specified directly by the monoidal structure, or as an infinite tensor product in the sense of \Cref{semicartesian_infproduct}.
+Since the result is the same (up to unique isomorphism), there is no ambiguity and the notation is consistent.
 \end{remark}
@@
 	It is natural to require different infinite tensor products to interact well with another.
-If $X_J$ is an infinite tensor product of a family $(X_i)_{i \in J}$ and we are given an additional object $X_\ast$ for $\ast \not \in J$, then one will want the canonical comparison morphism
+If $X_J$ is an infinite tensor product of a family $(X_i)_{i \in J}$ and we are given an additional object $X_\ast$ for $\ast \not \in J$, then there is a canonical comparison isomorphism
 	\begin{equation}
@@
 	\end{equation}
-	to be an isomorphism, where $X_{J \,\sqcup\, \{\ast\}}$ is the infinite tensor product of the original family with $X_\ast$ thrown in.
+	induced via the universal property of $X_{J \,\sqcup\, \{\ast\}}$, which is the infinite tensor product of the original family with $X_\ast$ thrown in.
+In order for infinite tensor products to be coherent, one will want this comparison isomorphism to be an isomorphism.
 We now show that this is indeed the case thanks to the preservation condition in \Cref{semicartesian_infproduct}, even if $X_{J \,\sqcup\, \{\ast\}}$ does not exist a priori.
 
-	To do so, we exhibit $X_J \otimes X_\ast$ as the relevant cofiltered limit, which equips it with the defining universal property of $X_{J \,\sqcup\, \{\ast\}}$, as follows.
+	More precisely, we exhibit $X_J \otimes X_\ast$ as the defining cofiltered limit of the infinite tensor product $X_{J \,\sqcup\, \{\ast\}}$ as follows.
 The object $X_J \otimes X_\ast$ can be equipped with finite marginalization morphisms with respect to $F \subseteq J \sqcup \{\ast\}$ given by
@@
 	\]
-	for $\ast \in F$, and just
+	whenever $\ast \in F$, and just by
 	\[
@@
 	\]
-	in case $\ast \not \in F$.
+	in case that $\ast \not \in F$.
 It is straightforward to check that these morphisms indeed make $X_J \otimes X_\ast$ carry the universal property of the infinite tensor product $X_{J \sqcup \{\ast\}}$ if and only if the functor $- \otimes X_\ast$ preserves the defining cofiltered limit of the infinite tensor product $X_J$.
@@
 Since the Kolmogorov extension theorem does not hold for general (even merely countable) products of measurable spaces~\cite{AJ}, this is not the case without further additional assumptions on the measurable spaces involved.
-Thus we do not know whether $\Stoch$ has infinite tensor products, although we suspect that it does not; but even if it does, they are in general not the ones that one will care about for the purposes of probability theory.
+Thus we do not know whether $\Stoch$ has infinite tensor products, although we suspect that it does not; but even in the unlikely case that it does, they are in general not the ones that one will care about for the purposes of probability theory.
 
-	However, the situation improves for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem indeed holds~\cite[Theorem~14.35]{klenke}.
-In other words, if $\left( (X_j, \Sigma_j) \right)_{j \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{j \in \bN} X_j$, carrying the product $\sigma$-algebra $\Sigma_\bN$, satisfies the universal property of an infinite tensor product with respect to maps out of $I$.
-We now prove that this implies the universal property in general.
+	However, the situation is much better for countable products in $\BorelStoch$, for which the Kolmogorov extension theorem indeed holds~\cite[Theorem~14.35]{klenke}.
+In other words, if $\left( (X_i, \Sigma_i) \right)_{i \in \bN}$ is a sequence of standard Borel spaces, then the cartesian product $X_\bN = \prod_{i \in \bN} X_i$, when equipped with the product $\sigma$-algebra $\Sigma_\bN$, satisfies the universal property of an infinite tensor product with respect to maps out of $I$, since the marginalization maps implement a bijection between probability measures on $X_{\bN} = \prod_{i \in \bN} X_i$ and compatible families of probability measures on the finite subproducts $X_F = \prod_{i \in F} X_i$, where the compatibility is with respect to marginalization to smaller subproducts specified by $F' \subseteq F$.
 
+	We now prove that this implies the universal property in general: if $A$ and all the $X_i$ are standard Borel spaces, then Markov kernels $A \to X_J$ are in bijection with compatible families of Markov kernels $A \to X_F$.
+While we just saw that this is the case for $A = I$, we now show that it holds for arbitrary $A$.
 Thus suppose that
@@
 Since the map is measurable by assumption whenever $S$ is a measurable cylinder set, and the cylinder sets form a $\pi$-system, the $\pi$-$\lambda$-theorem implies that $a \mapsto g_J(S|a)$ is measurable for all $S$ in the $\sigma$-algebra generated by the measurable cylinder sets, which is exactly the product $\sigma$-algebra $\Sigma_J$.
+Hence the existence part of the universal property indeed holds; and the uniqueness part is obvious by considering each $a \in A$ separately and applying the Kolmogorov extension theorem.
 
@@
 	In conclusion, $\BorelStoch$ indeed has countable tensor products.
-It is plausible that there is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4}, for which there also is a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
-However, we have so far not been able to find a suitable condition on Markov kernels which would guarantee closure under composition, due to problems with perfect measures not being stable under mixtures~\cite{ramachandran}.
+It is plausible that there is another subcategory of $\Stoch$ strictly larger than $\BorelStoch$ which has all infinite tensor products; for example, one can try to construct such a subcategory by imposing compactness or perfectness conditions~\cite[\S{451}]{fremlin4} on the Markov kernels, since under such assumption one again has a version of the Kolmogorov extension theorem~\cite[Corollary~454G]{fremlin4}.
+However, we have so far not been able to find a definition of ``compact Markov kernel'' or ``perfect Markov kernel'' which would guarantee closure under composition, due to problems with perfect measures not being stable under mixtures~\cite{ramachandran}.
+Hence the problem of finding a subcategory of $\Stoch$ with all infinite tensor products remains open.
 \end{example}
@@
 	\label{poset_case}
-	Suppose that $\cC$ is a partially ordered set, considered as a category with $X \geq Y$ if and only if the morphism $X \to Y$ exists.\footnote{This direction of the ordering is opposite to the usual convention, but necessary for the following to work on the nose.} Then the monoidal structure makes $\cC$ into a preordered commutative monoid, which we write additively.
+	Suppose that $\cC$ is a partially ordered set, considered as a category with $X \geq Y$ if and only if the morphism $X \to Y$ exists.\footnote{This direction of the ordering is opposite to the usual convention, but necessary for the following to work without reversing direction.} Then the monoidal structure makes $\cC$ into a preordered commutative monoid, which we write additively.
 Here, the functoriality of the monoidal structure amounts to the assumption that addition is monotone,
@@
 If a Markov category $\cC$ has infinite tensor products, then one should expect a compatibility condition between these infinite tensor products and the comonoid structures on the objects.
+This is imposed as follows.
 % In the following string diagrams, we draw the object associated to an infinite tensor product as a double wire.
@@
 In particular, there may be infinite tensor products which are not Kolmogorov products.
-For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_i R_i$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit).
+For example in $\CRing_+\op$, we may take the tensor product of abelian groups $\bigotimes_i R_i$ and equip it with a different multiplication than the tensor product of rings one (as long as it has the same unit), and one will then have an infinite tensor product in $\CRing_+\op$ which is not a Kolmogorov product.
 
@@
 comonoid structure on a Kolmogorov product uniquely: $\cop{\bigotimes_i X_i}$
-has to be the equal to the corresponding diagonal in $\cC_\detc$, and
-\Cref{kolmprod_catdet} determines $\bigotimes_i X_i$ up to \emph{deterministic}
+has to be the equal to the corresponding diagonal morphism in $\cC_\detc$, and
+\Cref{kolmprod_catdet} determines $\bigotimes_i X_i$ up to unique \emph{deterministic}
 isomorphism.
@@
     \emph{nonempty powerset monad}, which sends a set $X$ to $\cP(X) \setminus \emptyset$.
+In particular, $\FinSetMulti$ is closely related to $\Rel$, the category of sets and relations, since the latter can equivalently be regarded as the Kleisli category of the powerset monad (where the empty set is allowed).
+Intuitively, $\SetMulti$ is the closest relative of $\Rel$ to which our formalism can be applied.
+    See also \cite[Example~2.6]{markov_cats} for a treatment of the full subcategory $\FinSetMulti$ on finite sets.
 
-    See also \cite[Example~2.6]{markov_cats} for a treatment of the full subcategory $\FinSetMulti$ on finite sets.
-    The Cartesian product of sets gives it a symmetric monoidal structure, if for $f : X_1 \to Y_1$ and $g: X_2 \to Y_2$ we set
+    The Cartesian product of sets equips $\SetMulti$ with a symmetric monoidal structure, if for $f : A \to X$ and $g: B \to Y$ we set
 	\[
-	(f \tensor g)(x_1,x_2) := f(x_1) \times g(x_2) \:\subseteq\: Y_1 \times Y_2.
+	(f \tensor g)(a,b) := f(a) \times g(b) \:\subseteq\: X \times Y.
 	\]
+	The monoidal unit is any one-element set $I$.
 With the obvious structure isomorphisms inherited from $\Set$, this turns $\SetMulti$ into a semicartesian symmetric monoidal category, and we can give it a Markov category structure by setting
@@
     Then the deterministic morphisms are precisely those sending each point into a singleton set, resulting in an isomorphism of categories
-    $\SetMulti_\detc \cong \sf{Set}$.
+    $\SetMulti_\detc \cong \Set$.
 
-    Of course, $\sf{Set}$ has all infinite products. But perhaps surprisingly, these products are not Kolmogorov products, or even infinite tensor products in $\sf{SetMulti}$.
+    Of course, $\Set$ has all infinite products. But perhaps surprisingly, these products are not Kolmogorov products, or even infinite tensor products in $\SetMulti$.
     To see this, consider for example the family $(X_n)_{n\in\bN}$ with $X_n = \{0,1\}$ for all $n$. 
-    A map $* \to \prod_{n\in \bN} \{0,1\}$ is just a nonempty subset of this infinite product.
-    Given such a subset $U$, the finite marginals $* \to \prod_{n \in F} \{0,1\}$ for $F \subset \bN$ are the images of $U$ under the projection map.
+    A map $I \to \prod_{n\in \bN} \{0,1\}$ is just a nonempty subset of this infinite product.
+    Given such a subset $U$, the finite marginals $I \to \prod_{n \in F} \{0,1\}$ for finite $F \subset \bN$ are the images of $U$ under the projection map.
     But these images do not determine $U$. For instance, consider the subset $U$ of those sequences containing at least one $1$.
     Its image in every $\prod_{n \in F} \{0,1\}$ is the whole set, since any finite sequence of $0$s and $1$s can be extended to one containing a $1$, but $U$ itself is a proper subset.
-It is clear that this example is quite generic and works for any infinite family of nonempty sets, infinitely many of which contain at least two elements, as in \Cref{infprods_finstoch}.
+In particular, $U$ has the same compatible family of finite marginalizations as e.g.~the set of those sequences containing at least one $0$, and hence the uniqueness part of the universal property fails.
 
+    It is clear that this counterexample is quite generic and works for any infinite family of nonempty sets, infinitely many of which contain at least two elements, as in \Cref{infprods_finstoch}.
+Thus $\SetMulti$ is very far from having Kolmogorov products.
+A good way to remedy this deficiency is to consider topological spaces instead of sets: as we will see in \Cref{examples}, the Kleisli category of the lower Vietoris monad on $\Top$ does have Kolmogorov products, and it can be thought of as the topological counterpart of $\SetMulti$.
 \end{example}
@@
 \section{The zero--one laws}
+\label{zeroones}
 
+We now make use of the theory developed in the previous sections in order to state and prove synthetic versions of the classical zero--one laws of Kolmogorov and Hewitt--Savage.
 Throughout this section, $(X_i)_{i \in J}$ is a family of objects in a Markov category $\cC$ with Kolmogorov product $X_J$ and finite marginalizations $\pi_F : X_J \to X_F$.
@@
 \begin{proof}
-    The proof is similar to the previous proof. This time we want to apply \Cref{thm:hewsav} with $\cC = \BorelStoch$, $J = \bN$, $A = I$.
+    The proof is similar to the previous proof. This time we want to apply \Cref{thm:hewsav} with $\cC = \BorelStoch$, $J = \bN$ and $A = I$.
     Again, we have $P: I \to \Omega$.
     As before, we let $s: X_\bN \to \{0,1\}$ be the indicator function of $S$, and we let $p = f_\bN P$.
-    The i.i.d.~assumption on the $f_j$ implies that $\hat{\sigma}p = p$, and the assumption on $S$ implies $s\hat{\sigma} = s$ for finite permutations $\sigma$.
+    The i.i.d.~assumption on the $f_i$ implies that $\hat{\sigma}p = p$, and the assumption on $S$ implies $s\hat{\sigma} = s$ for finite permutations $\sigma$.
     Hence we can apply \Cref{thm:hewsav}. This again shows that the map $sp: I \to \{0,1\}$ is deterministic, which, just as before, means $P(f_\bN\inv(S)) \in \{0,1\}$.
@@
         \item The objects are topological spaces.
-	\item A morphism $f: X \to Y$ is a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets, equipped with the topology generated by subbasic opens of the form $\{V \subseteq Y \text{ closed} \mid V \cap U \neq \emptyset\}$, where $U \subseteq Y$ ranges over all opens.
+	\item A morphism $f: X \to Y$ is a continuous function $X \to HY$, where $HY$ denotes the set of closed subsets of the space $Y$, equipped with the topology generated by subbasic opens of the form
+		\[
+			\mathrm{Hit}(U) := \{C \subseteq Y \text{ closed} \mid C \cap U \neq \emptyset\},
+		\]
+		where $U \subseteq Y$ ranges over all opens.
 	\item Composition is defined as in $\SetMulti$ via~\eqref{relational_composition}, but taking the closure of the union in addition.
@@
 		\[
-			(f \tensor g)(x_1,x_2) := f(x_1) \times g(x_2),
+			(f \tensor g)(a,b) := f(a) \times g(b),
 		\]
@@
 \begin{proposition}
+    \label{infprods_klH}
     $\Kl(H)$ has Kolmogorov products of any cardinality, given by the usual infinite product of topological spaces with the product topology.
@@
 \begin{proof}
-    First we observe that $H(\prod_{j\in J} X_j)$ is the cofiltered limit of the spaces
-    $H(\prod_{j\in F} X_j)$ for $F \subseteq J$ finite.
+    First we observe that $H(\prod_{i\in J} X_i)$ is the cofiltered limit of the spaces
+    $H(\prod_{i\in F} X_i)$ for $F \subseteq J$ finite.
     To see this, note that the marginalizations induce a continuous map
@@
 	\[
-		C = \left\{x \in \prod_{j\in J} X_j \:\Bigg|\: \pi_F(x) \in C_F \:\: \forall F\right\}
+		C := \left\{x \in \prod_{j\in J} X_j \:\Bigg|\: \pi_F(x) \in C_F \:\: \forall F\right\}
 	\]
@@
 	\[
-		\alpha(A_U) = \pi_F\inv\left(\left\{V \subseteq \prod_{j \in F} X_F \text{ closed} \:\Bigg|\: V \cap \pi_F(U) \neq \emptyset\right\}\right),
+		\alpha(A_U) = \pi_F\inv\left(\left\{D \subseteq \prod_{j \in F} X_F \text{ closed} \:\Bigg|\: D \cap \pi_F(U) \neq \emptyset\right\}\right),
 	\]
@@
 
-However, we cannot instantiate the Hewitt-Savage zero--one law in $\Kl(H)$, since this Markov category is in fact not causal, as the following example shows.
+However, we cannot instantiate the Hewitt--Savage zero--one law in $\Kl(H)$, since this Markov category is in fact not causal, as the following example shows.
 

### 2020-06-19 categorical-zero-one.tex
Fixed refs
There was an issue with the Giry ref somewhere, although I'm honestly
not sure what. Seems fixed now.
Also fixed abbrev. of the danish journal, as per Dusko's suggestion
Added Cartesian cats as example

@@
 
-	As a first application, we state and prove versions of the zero--laws of Kolmogorov and Hewitt--Savage laws for Markov categories.
+	As a first application, we state and prove versions of the zero--one laws of Kolmogorov and Hewitt--Savage for Markov categories.
 This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts.
@@
 In the probability context, these morphisms can be interpreted as marginalizations, or equivalently as discarding the value of the variable $Y$ or $X$.
+
+\begin{example}
+  Any Cartesian monoidal category is obviously semicartesian. In the probabilistic setting that we are considering, this corresponds to a situation in which there is no randomness
+  (in such a category, all morphisms are deterministic, cf. \cref{determ_def}). Hence it is somewhat uninteresting from our point of view.
+\end{example}
 
@@
 
-\begin{definition}[{\cite[Definition~10.1]{markov_cats}}]
+\begin{definition}[{\cite[Definition~10.1]{markov_cats}}]\label{determ_def}
 	Let $\cC$ be a Markov category. A morphism $f : X \to Y$ in $\cC$ is \emph{deterministic} if it is a comonoid homomorphism,
